### 2017-01-30 paper/DAFx17_tmpl.tex
Added DAFX paper templates and Latex build stuff.

% Template LaTeX file for DAFx-17 papers
%
% To generate the correct references using BibTeX, run
%     latex, bibtex, latex, latex
% modified...
% - from DAFx-00 to DAFx-02 by Florian Keiler, 2002-07-08
% - from DAFx-02 to DAFx-03 by Gianpaolo Evangelista
% - from DAFx-05 to DAFx-06 by Vincent Verfaille, 2006-02-05
% - from DAFx-06 to DAFx-07 by Vincent Verfaille, 2007-01-05
%                          and Sylvain Marchand, 2007-01-31
% - from DAFx-07 to DAFx-08 by Henri Penttinen, 2007-12-12
%                          and Jyri Pakarinen 2008-01-28
% - from DAFx-08 to DAFx-09 by Giorgio Prandi, Fabio Antonacci 2008-10-03
% - from DAFx-09 to DAFx-10 by Hannes Pomberger 2010-02-01
% - from DAFx-10 to DAFx-12 by Jez Wells 2011
% - from DAFx-12 to DAFx-14 by Sascha Disch 2013
% - from DAFx-15 to DAFx-16 by Pavel Rajmic 2015
% - from DAFx-16 to DAFx-17 by Brian Hamilton 2016
%
% Template with hyper-references (links) active after conversion to pdf
% (with the distiller) or if compiled with pdflatex.
%
% 20060205: added package 'hypcap' to correct hyperlinks to figures and tables
%                      use of \papertitle and \paperauthorA, etc for same title in PDF and Metadata
%
% 1) Please compile using latex or pdflatex.
% 2) If using pdflatex, you need your figures in a file format other than eps! e.g. png or jpg is working
% 3) Please use "paperftitle" and "pdfauthor" definitions below

%------------------------------------------------------------------------------------------
%  !  !  !  !  !  !  !  !  !  !  !  ! user defined variables  !  !  !  !  !  !  !  !  !  !  !  !  !  !
% Please use these commands to define title and author(s) of the paper:
\def\papertitle{Templates for DAFx-17, Edinburgh, UK}
\def\paperauthorA{Author One}
\def\paperauthorB{Author Two}
\def\paperauthorC{Author Three}
\def\paperauthorD{Author Four}

% Authors' affiliations have to be set below

%------------------------------------------------------------------------------------------
\documentclass[twoside,a4paper]{article}
\usepackage{dafx_17}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{euscript}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ifpdf}

\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subfig} % or can use subcaption package
\usepackage{color}

\setcounter{page}{1}
\ninept

\usepackage{times}
% Saves a lot of ouptut space in PDF... after conversion with the distiller
% Delete if you cannot get PS fonts working on your system.

% pdf-tex settings: detect automatically if run by latex or pdflatex
\newif\ifpdf
\ifx\pdfoutput\relax
\else
   \ifcase\pdfoutput
      \pdffalse
   \else
      \pdftrue
\fi

\ifpdf % compiling with pdflatex
  \usepackage[pdftex,
    pdftitle={\papertitle},
    pdfauthor={\paperauthorA, \paperauthorB, \paperauthorC, \paperauthorD},
    colorlinks=false, % links are activated as colror boxes instead of color text
    bookmarksnumbered, % use section numbers with bookmarks
    pdfstartview=XYZ % start with zoom=100% instead of full screen; especially useful if working with a big screen :-)
  ]{hyperref}
  \pdfcompresslevel=9
  \usepackage[pdftex]{graphicx}
  \usepackage[figure,table]{hypcap}
\else % compiling with latex
  \usepackage[dvips]{epsfig,graphicx}
  \usepackage[dvips,
    colorlinks=false, % no color links
    bookmarksnumbered, % use section numbers with bookmarks
    pdfstartview=XYZ % start with zoom=100% instead of full screen
  ]{hyperref}
  % hyperrefs are active in the pdf file after conversion
  \usepackage[figure,table]{hypcap}
\fi

\title{\papertitle}

%-------------SINGLE-AUTHOR HEADER STARTS (uncomment below if your paper has a single author)-----------------------
%\affiliation{
%\paperauthorA \,\sthanks{Thanks to the predecessors for the templates}}
%{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
%{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
%}
%-----------------------------------SINGLE-AUTHOR HEADER ENDS------------------------------------------------------

%---------------TWO-AUTHOR HEADER STARTS (uncomment below if your paper has two authors)-----------------------
%\twoaffiliations{
%\paperauthorA \,\sthanks{Thanks to the predecessors for the templates}}
%{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
%{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
%}
%{\paperauthorB \,\sthanks{This work was supported by the XYZ Foundation}}
%{\href{http://dafx16.vutbr.cz}{SPLab} \\ Brno University of Technology \\ Brno, Czech Republic \\ {\tt \href{mailto:dafx16@vutbr.cz}{dafx16@vutbr.cz}}
%}
%-------------------------------------TWO-AUTHOR HEADER ENDS------------------------------------------------------

%---------------THREE-AUTHOR HEADER STARTS (uncomment below if your paper has three authors)-----------------------
%\threeaffiliations{
%\paperauthorA \,\sthanks{This work was supported by the XYZ Foundation}}
%{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
%{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
%}
%{\paperauthorB \,\sthanks{Thanks to the predecessors for the templates}}
%{\href{http://dafx16.vutbr.cz}{SPLab} \\ Brno University of Technology \\ Brno, Czech Republic \\ {\tt \href{mailto:dafx16@vutbr.cz}{dafx16@vutbr.cz}}
%}
%{\paperauthorC \,\sthanks{Illustrious contributor}}
%{\href{http://www.ntnu.edu/dafx15}{Department of Music, Norwegian} \\ University of Science and Technology \\Trondheim, Norway \\ {\tt \href{mailto:dafx15@iet.ntnu.edu}{dafx15@iet.ntnu.edu}}
%}
%-------------------------------------THREE-AUTHOR HEADER ENDS------------------------------------------------------

%----------------FOUR-AUTHOR HEADER STARTS (uncomment below if your paper has four authors)-----------------------
\fouraffiliations{
\paperauthorA \,\sthanks{This work was supported by the XYZ Foundation}}
{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
}
{\paperauthorB \,\sthanks{Thanks to the predecessors for the templates}}
{\href{http://dafx16.vutbr.cz}{SPLab} \\ Brno University of Technology \\ Brno, Czech Republic \\ {\tt \href{mailto:dafx16@vutbr.cz}{dafx16@vutbr.cz}}
}
{\paperauthorC \,\sthanks{Illustrious contributor}}
{\href{http://www.ntnu.edu/dafx15}{Department of Music,} \\ Norwegian University of Science and Technology (NTNU) \\Trondheim, Norway \\ {\tt \href{mailto:dafx15@iet.ntnu.edu}{dafx15@iet.ntnu.edu}}
}
{\paperauthorD \,\sthanks{This guy is a very good fellow}}
{\href{http://dafx14.fau.de}{Fraunhofer IIS,} \\ Friedrich-Alexander University Erlangen\\ Erlangen, Germany\\
{\tt \href{mailto:dafx14@audiolabs-erlangen.de}{dafx14@audiolabs-erlangen.de}}
}
%-------------------------------------FOUR-AUTHOR HEADER ENDS------------------------------------------------------

\begin{document}
% more pdf-tex settings:
\ifpdf % used graphic file format for pdflatex
  \DeclareGraphicsExtensions{.png,.jpg,.pdf}
\else  % used graphic file format for latex
  \DeclareGraphicsExtensions{.eps}
\fi

\maketitle

\begin{abstract}
This is the template file for the proceedings of the 20$^{\text{th}}$ International Conference on Digital Audio Effects (DAFx-17).
This template has been derived from WASPAA'99 templates and aims at producing conference proceedings in electronic form.
The format is essentially the one used for ICASSP conferences.
Please use either this \LaTeX{} or the accompanying Word formats when preparing your submission.
The templates are available in electronic form on
\href{http://dafx17.eca.ed.ac.uk/}{http://dafx17.eca.ed.ac.uk/}.
\end{abstract}

\section{Introduction}
\label{sec:intro}
This template can be found on the conference website.

\subsection{Figures}
\label{ssec:figures}
All figures should be centred on the column (or page, if the figure spans both columns).
Figure captions (in italic) should follow each figure and have the format given in Figure \ref{fft_plot}.
%
Vectorial figures are preferred. For example when using
\texttt{Matlab}, export using either Postscript or PDF format. Also,
in order to provide a better readability, figure text font size
should be at least identical to footnote font size. To do so using
\texttt{Matlab}, use the \texttt{subplot} command before plotting.
If bitmap figures are used, please make sure that the resolution is
enough for print quality. Fig. \ref{ftt_plot2} illustrates an
example of a figure spanning two columns.
%
\begin{figure}[ht]
\centerline{\includegraphics[scale=0.8]{fft_plot2}}
\caption{\label{fft_plot}{\it Sinusoid in time and frequency domain. Short captions are centred, long captions (more than 1 line) are justified.}}
\end{figure}
%
\begin{figure*}[ht]
\center
\includegraphics[width=5in]{TwoColumnSine2}
\caption{\label{ftt_plot2}{\it A figure spanning two columns, as mentioned in Sec. \ref{ssec:figures}. }}
\end{figure*}

\subsection{Tables}
As for figures, all tables should be centered on the column (or page, if the table spans both columns).
Table captions should be in italic, precede each table and have the format given in Table \ref{tab:example}.

\begin{table}[ht]
  \caption{\itshape Basic trigonometric values.}
	\centering
	\begin{tabular}{|c|c|}
		\hline
		$\mathrm{angle}\,(\theta, \mathrm{rad})$ & $\sin \theta$ \\\hline
		$\frac{\pi}{2}$ & $1$ \\
		$\pi$ & $0$ \\
		$\frac{3\pi}{2}$ & $-1$ \\
		$2\pi$ & $0$ \\\hline
	\end{tabular}
	%
	\label{tab:example}
\end{table}

\begin{table*}[ht]
  \caption{{\it Basic trigonometric values, spanning two columns.}}
	\centering
  \begin{tabular}{|c|c|c|c|c|c|c|}\hline
    $\mathrm{angle}\, (\theta, \mathrm{rad})$ & $\sin \theta$ & $\cos \theta $ & $(\sin \theta)/2 $ & $(\cos \theta) /2 $ & $(\sin \theta)/3 $ & $(\cos \theta)/3$    \\\hline
    $\frac{\pi}{2}$ & $1$ & $0$ & $1/2$ & $0$ & $1/3$ & $0$ \\
    $\pi$ & $0$ & $-1$ & $0$ & $-1/2$ & $0$ & $-1/3$\\
    $\frac{3\pi}{2}$ & $-1$ & $0$ & $-1/2$ & $0$ & $-1/3$ & $0$ \\
    $2\pi$ & $0$ & $1$ & $0$ & $1/2$ & $0$ & $1/3$ \\\hline
 \end{tabular}
	%
  \label{tab:example2}
\end{table*}

\subsection{Equations}
Equations should be placed on separate lines and numbered:

\begin{equation}
	X(e^{j\Omega})=\sum_{n=0}^{N-1}x(n)e^{-j\Omega n}
	\label{eq1}
	\end{equation}
	where the sequence $x(n)$ in equation (\ref{eq1}) is a windowed frame:
	\begin{equation}
	x(n)=s(n) w(n)
	\label{eq2}
\end{equation}
%
with a window function $w(n)$.

\subsection{Page Numbers}
Page numbers will be added to the document in the postprocessing stage, so {\em please leave the numbering as is},
that is, the first page will start at page DAFX-1 and the last page, at most, will have to be DAFX-8.

\subsection{References}
The references will be numbered in order of appearance \cite{Mitra:Kaiser:1993:DSP:handbook}, \cite{Haykin:1991:adaptive:filter}, \cite{Moorer:2000:AES:audio:millenium} and \cite{Nackaerts:2001:ICMC}. Please avoid listing references that do not appear in the text (we did the opposite in this template).

\subsubsection{Reference Format}
The reference format is the standard IEEE one. We recommend to use BibTeX to create the reference list.

\section{Conclusions}
This template can be found on the conference website.
For changing the number of author affiliations (1 to 4), uncomment the corresponding regions in the template \texttt{tex} file.
Please, submit full-length papers (max.~8 pages both oral and poster presentations).
Submission is fully electronic and automated through the Conference Web Submission System.
DO NOT send us papers directly by e-mail.

\section{Acknowledgments}
Many thanks to the great number of anonymous reviewers!

%\newpage
\nocite{*}
\bibliographystyle{IEEEbib}
\bibliography{DAFx17_tmpl} % requires file DAFx17_tmpl.bib

\section{Appendix: Margin Check}
This section shows the column margins for the text. \bigskip\newline

Lorem ipsum dolor sit amet, consectetur adipisici elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat. Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.

Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat. Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.

Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis.

At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, At accusam aliquyam diam diam dolore dolores duo eirmod eos erat, et nonumy sed tempor et et invidunt justo labore Stet clita ea et gubergren, kasd magna no rebum. sanctus sea sed takimata ut vero voluptua. est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat.

Consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

Lorem ipsum dolor sit amet, consectetur adipisici elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat. Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.

Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat. Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.

Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis.

At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, At accusam aliquyam diam diam dolore dolores duo eirmod eos erat, et nonumy sed tempor et et invidunt justo labore Stet clita ea et gubergren, kasd magna no rebum. sanctus sea sed takimata ut vero voluptua. est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat.

Consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. 
\end{document}

### 2017-01-30 paper/paper.tex
Added DAFX paper templates and Latex build stuff.

--- 2017-01-30 paper/DAFx17_tmpl.tex
@@
 %     latex, bibtex, latex, latex
-% modified...
-% - from DAFx-00 to DAFx-02 by Florian Keiler, 2002-07-08
-% - from DAFx-02 to DAFx-03 by Gianpaolo Evangelista
-% - from DAFx-05 to DAFx-06 by Vincent Verfaille, 2006-02-05
-% - from DAFx-06 to DAFx-07 by Vincent Verfaille, 2007-01-05
-%                          and Sylvain Marchand, 2007-01-31
-% - from DAFx-07 to DAFx-08 by Henri Penttinen, 2007-12-12
-%                          and Jyri Pakarinen 2008-01-28
-% - from DAFx-08 to DAFx-09 by Giorgio Prandi, Fabio Antonacci 2008-10-03
-% - from DAFx-09 to DAFx-10 by Hannes Pomberger 2010-02-01
-% - from DAFx-10 to DAFx-12 by Jez Wells 2011
-% - from DAFx-12 to DAFx-14 by Sascha Disch 2013
-% - from DAFx-15 to DAFx-16 by Pavel Rajmic 2015
-% - from DAFx-16 to DAFx-17 by Brian Hamilton 2016
-%
-% Template with hyper-references (links) active after conversion to pdf
-% (with the distiller) or if compiled with pdflatex.
-%
-% 20060205: added package 'hypcap' to correct hyperlinks to figures and tables
-%                      use of \papertitle and \paperauthorA, etc for same title in PDF and Metadata
 %
@@
 % Please use these commands to define title and author(s) of the paper:
-\def\papertitle{Templates for DAFx-17, Edinburgh, UK}
-\def\paperauthorA{Author One}
-\def\paperauthorB{Author Two}
-\def\paperauthorC{Author Three}
-\def\paperauthorD{Author Four}
+\def\papertitle{Improved Atoms for the Distribution Derivative Method}
+\def\paperauthorA{Nicholas Esterer}
+\def\paperauthorB{Philippe Depalle}
 
@@
     pdftitle={\papertitle},
-    pdfauthor={\paperauthorA, \paperauthorB, \paperauthorC, \paperauthorD},
+    pdfauthor={\paperauthorA, \paperauthorB},
     colorlinks=false, % links are activated as colror boxes instead of color text
@@
 %---------------TWO-AUTHOR HEADER STARTS (uncomment below if your paper has two authors)-----------------------
-%\twoaffiliations{
-%\paperauthorA \,\sthanks{Thanks to the predecessors for the templates}}
-%{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
-%{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
-%}
-%{\paperauthorB \,\sthanks{This work was supported by the XYZ Foundation}}
-%{\href{http://dafx16.vutbr.cz}{SPLab} \\ Brno University of Technology \\ Brno, Czech Republic \\ {\tt \href{mailto:dafx16@vutbr.cz}{dafx16@vutbr.cz}}
-%}
-%-------------------------------------TWO-AUTHOR HEADER ENDS------------------------------------------------------
-
-%---------------THREE-AUTHOR HEADER STARTS (uncomment below if your paper has three authors)-----------------------
-%\threeaffiliations{
-%\paperauthorA \,\sthanks{This work was supported by the XYZ Foundation}}
-%{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
-%{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
-%}
-%{\paperauthorB \,\sthanks{Thanks to the predecessors for the templates}}
-%{\href{http://dafx16.vutbr.cz}{SPLab} \\ Brno University of Technology \\ Brno, Czech Republic \\ {\tt \href{mailto:dafx16@vutbr.cz}{dafx16@vutbr.cz}}
-%}
-%{\paperauthorC \,\sthanks{Illustrious contributor}}
-%{\href{http://www.ntnu.edu/dafx15}{Department of Music, Norwegian} \\ University of Science and Technology \\Trondheim, Norway \\ {\tt \href{mailto:dafx15@iet.ntnu.edu}{dafx15@iet.ntnu.edu}}
-%}
-%-------------------------------------THREE-AUTHOR HEADER ENDS------------------------------------------------------
-
-%----------------FOUR-AUTHOR HEADER STARTS (uncomment below if your paper has four authors)-----------------------
-\fouraffiliations{
-\paperauthorA \,\sthanks{This work was supported by the XYZ Foundation}}
-{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
-{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
+\twoaffiliations{
+\paperauthorA \,\sthanks{}}
+{\href{http://www.cirmmt.org/}{https://mt.music.mcgill.ca/spcl/home} %
+\\ McGill University %
+\\ Montreal, Quebec, Canada \\
+{\tt \href{mailto:nicholas.esterer@mail.mcgill.ca}{nicholas.esterer@mail.mcgill.ca}}
 }
-{\paperauthorB \,\sthanks{Thanks to the predecessors for the templates}}
-{\href{http://dafx16.vutbr.cz}{SPLab} \\ Brno University of Technology \\ Brno, Czech Republic \\ {\tt \href{mailto:dafx16@vutbr.cz}{dafx16@vutbr.cz}}
+{\paperauthorB \,\sthanks{}}
+{\href{http://www.cirmmt.org/}{https://mt.music.mcgill.ca/spcl/home} %
+\\ McGill University %
+\\ Montreal, Quebec, Canada \\
+{\tt %
+\href{mailto:philippe.depalle@music.mcgill.ca}{philippe.depalle@music.mcgill.ca}}
 }
-{\paperauthorC \,\sthanks{Illustrious contributor}}
-{\href{http://www.ntnu.edu/dafx15}{Department of Music,} \\ Norwegian University of Science and Technology (NTNU) \\Trondheim, Norway \\ {\tt \href{mailto:dafx15@iet.ntnu.edu}{dafx15@iet.ntnu.edu}}
-}
-{\paperauthorD \,\sthanks{This guy is a very good fellow}}
-{\href{http://dafx14.fau.de}{Fraunhofer IIS,} \\ Friedrich-Alexander University Erlangen\\ Erlangen, Germany\\
-{\tt \href{mailto:dafx14@audiolabs-erlangen.de}{dafx14@audiolabs-erlangen.de}}
-}
-%-------------------------------------FOUR-AUTHOR HEADER ENDS------------------------------------------------------
 
@@
 \begin{abstract}
-This is the template file for the proceedings of the 20$^{\text{th}}$ International Conference on Digital Audio Effects (DAFx-17).
-This template has been derived from WASPAA'99 templates and aims at producing conference proceedings in electronic form.
-The format is essentially the one used for ICASSP conferences.
-Please use either this \LaTeX{} or the accompanying Word formats when preparing your submission.
-The templates are available in electronic form on
-\href{http://dafx17.eca.ed.ac.uk/}{http://dafx17.eca.ed.ac.uk/}.
+TODO
 \end{abstract}
@@
 %
-\begin{figure}[ht]
-\centerline{\includegraphics[scale=0.8]{fft_plot2}}
-\caption{\label{fft_plot}{\it Sinusoid in time and frequency domain. Short captions are centred, long captions (more than 1 line) are justified.}}
-\end{figure}
 %
-\begin{figure*}[ht]
-\center
-\includegraphics[width=5in]{TwoColumnSine2}
-\caption{\label{ftt_plot2}{\it A figure spanning two columns, as mentioned in Sec. \ref{ssec:figures}. }}
-\end{figure*}
 
@@
 \subsection{References}
-The references will be numbered in order of appearance \cite{Mitra:Kaiser:1993:DSP:handbook}, \cite{Haykin:1991:adaptive:filter}, \cite{Moorer:2000:AES:audio:millenium} and \cite{Nackaerts:2001:ICMC}.
-Please avoid listing references that do not appear in the text (we did the opposite in this template).
+A test reference \cite{betser2009sinusoidal}.
 
@@
 \bibliographystyle{IEEEbib}
-\bibliography{DAFx17_tmpl} % requires file DAFx17_tmpl.bib
+\bibliography{paper} % requires file DAFx17_tmpl.bib
 

### 2017-01-30 ddm.py

@@ -307,12 +307,16 @@ def p2_1_3_est(x,ch,kma0,w_name='hann',F_s=16000):
     while (b0_ < -np.pi):
         b0_ += 2.*np.pi
     b1_=np.imag(alpha[0][1])*F_s
+    while (b1_ > F_s*np.pi):
+        b1_ -= F_s*np.pi
+    while (b1_ < 0):
+        b1_ += F_s*np.pi
     b2_=np.imag(alpha[0][2])*(F_s**2.)
     a0_err=np.abs(ch.a0-a0_)
     a1_err=np.abs(ch.a1-a1_)
     a2_err=np.abs(ch.a2-a2_)
     # Find minimum distance on circle
     b0_err=min([(ch.b0-b0_)%(2.*np.pi),(b0_-ch.b0)%(2.*np.pi)])
-    b1_err=np.abs(ch.b1-b1_)
+    b1_err=min([(ch.b1-b1_)%(np.pi*F_s),(b1_-ch.b1)%(np.pi*F_s)])
     b2_err=np.abs(ch.b2-b2_)
     return (a0_err,a1_err,a2_err,b0_err,b1_err,b2_err)

### 2017-01-30 ddm_snr_win_comp.py

@@ -115,13 +115,17 @@ for k in errs.keys():
             while (ph0 < ph0_r[0]):
                 ph0_ += 2.*np.pi
             ph1_=np.imag(alpha[0][1])*F_s
+            while (ph1_ > ph1_r[1]):
+                ph1_ -= np.pi*F_s
+            while (ph1_ < ph1_r[0]):
+                ph1_ += np.pi*F_s
             ph2_=np.imag(alpha[0][2])*(F_s**2.)
             a0_err+=np.abs(a0-a0_)
             a1_err+=np.abs(a1-a1_)
             a2_err+=np.abs(a2-a2_)
             # Find minimum distance on circle
             ph0_err+=min([(ph0-ph0_)%(2.*np.pi),(ph0_-ph0)%(2.*np.pi)])
-            ph1_err+=np.abs(min([(ph1-ph1_)%(2.*np.pi),(ph1_-ph1)%(2.*np.pi)]))
+            ph1_err+=min([(ph1-ph1_)%(np.pi*F_s),(ph1_-ph1)%(np.pi*F_s)])
             ph2_err+=np.abs(ph2-ph2_)
             n += 1
 

### 2017-01-30 paper/build_paper.sh

@@ -1,0 +1,12 @@
+#! /bin/bash
+
+# Builds the thesis.tex file complete with bibliography.
+
+# Convert all eps files to pdf
+
+pdflatex paper.tex
+BIBINPUTS=. bibtex paper.aux
+pdflatex paper.tex
+pdflatex paper.tex
+mv paper.pdf Esterer_Nicholas_dafx_2017.pdf
+#dvipdf thesis.dvi

### 2017-02-07 paper/paper.tex
Described motivation for technique
Added power method eigenvalue computation.

@@
 \label{sec:intro}
-This template can be found on the conference website.
+%Additive synthesis using a sum of sinusoids plus noise is a powerful model for
+%representing audio, allowing for the easy implementation of many manipulations
+%such as time-stretching and transposition. In its most basic form, peaks in the
+%short-time spectrum are identified as representing sinusoids and connected based
+%on some criteria. As the phase evolution of the sinusoid is assumed linear over
+%the analysis frame, only the phase and frequency of the sinusoids at these
+%analysis points are used to fit a plausible phase function. Recently, there has
+%been interest in using higher order phase functions as the estimation of their
+%parameters has been made possible by a new set of techniques of only moderate
+%computational complexity using signal derivatives. Theoretically, the estimation
+%of the parameters of a polynomial phase function of arbitrary order make it
+%possible to approximate any analytical phase function to desired precision.
+%Empirically, the use of higher order phase models allow for higher quality
+%manipulations.
+%
+%The technique we will consider in this paper is the Distribution Derivative
+%Method for its convenience: the technique does not require computing derivatives
+%of the signal to be analysed. It does, however, require a
+%$p$ times differentiable analysis window where $p+1$ is the order of the
+%phase polynomial to be estimated.
+%
+%In the few reports on the technique, the window used is the Hann window. This
+%window is many-times differentiable but 
+%
+%Complex polynomial phase models whose estimation is 
+\section{The polynomial phase sinusoid}
+Recently techniques estimating the parameters of polynomial phase sinusoids,
+i.e., signals of the form
+\[
+    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j)
+\]
+have been developed. Many equivalent techniques have been developed for
+estimating the $a_j$ have been developed. In this paper we compare with the
+Distribution Derivative Method (DDM) only, without loss of generality.
+
+\section{The estimation of $a_j$}
+We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
+the theory of distributions (Laurent Schwartz), the DDM
+makes use of ``test
+functions'' or atoms $\psi$. These atoms must be once differentiable with respect to
+$t$ and be non-zero only on a finite interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
+%
+\begin{equation}
+    \label{eq:ddm:inner:prod:def}
+    \left\langle x , \psi \right\rangle = 
+    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
+\]
+%
+and the operator 
+%
+\[
+\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
+\]
+%
+Consider the weighted signal
+%
+\[
+    f(t) = x(t) \overline{\psi}(t)
+\]
+%
+differentiating with respect to $t$ we obtain
+%
+\begin{equation}
+    \label{eq:ddm:weighted:sig:derivative}
+    \frac{df(t)}{dt} = 
+    \frac{dx}{dt}(t)\overline{\psi}(t)
+    + x(t)\frac{d\overline{\psi}}{dt}(t)
+    = \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
+    + x(t)\frac{d\overline{\psi}}{dt}(t)
+\end{equation}
+%
+Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
+$\frac{df(t)}{dt}$ we obtain
+%
+\[
+    \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
+    + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
+\]
+%
+or, using the operator $\mathcal{T}^{\alpha}$,
+%
+\[ 
+    \sum_{j=1}^{Q} j a_j 
+    \left\langle \mathcal{T}^{j-1} x , \overline{\psi} \right\rangle
+    = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
+\]
+%
+
+From this we can see that to estimate the coefficients $a_j$, $ 1 \leq q \leq Q
+$ we simply need $R$ atoms with $R \geq Q$ to solve the linear system of
+equations
+\begin{equation}
+    \label{eq:ddmsyseq}
+    \sum_{j=1}^{Q} j a_j 
+    \left\langle \mathcal{T}^{j-1} x , \overline{\psi}_{r} \right\rangle
+    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
+\end{equation}
+for $1 \leq r \leq R$.
+
+\section{The estimation of the $a_{i,j}$ of $P$ components}
+
+Although this technique can be exteded to describe a single
+sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
+interest to consider a signals featuring a sum of such components, i.e.,
+%
+\[
+    s(t) = \sum_( \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j) )
+\]
+%
+In situations where multiple signal sources are known to exist (e.g., recordings
+of multiple speakers or performers) such a model is plausible.
+
+We examine how this mixture model influences the estimation of the $a_{i,j}$.
+Consider a mixture of $P$ components
+%
+\[
+    s(t) = \sum_{i=1}{P} x_{i}(t)
+\]
+%
+with
+%
+\[
+    x_{i}(t) = \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j)
+\]
+%
+If we define the weighted signal sum
+%
+\[
+    g(t) = \sum_{i=1}{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}{P} f_{i}(t)
+\]
+%
+and substitute $g$ for $f$ in \ref{eq:ddm:weighted:sig:derivative} we obtain
+%
+\[
+    \sum_{i=1}{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
+    0 = 
+    \sum_{i=1}{P}
+    \sum_{j=1}^{Q} j a_{i,j} 
+    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
+     + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle
+\]
+%
+From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
+\right\rangle$ is small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
+can simply estimate the parameters $a_{i^{\ast},j}$ using
+\[
+    \sum_{j=1}^{Q} j a_{i,j} 
+    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r} \right\rangle
+    = -\left\langle x_i, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
+\]
+for $1 \leq r \leq R$.
+
+\section{Designing the \psi_{r}}
+
+In practice, an approximation of \ref{eq:ddm:inner:prod:def} is evaluated using
+the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
+and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
+$T$ the sample period in seconds. In this way, the atoms $\psi_{\omega}(t)$ chosen
+are the products of the elements of the Fourier basis and an appropriately
+chosen window $w$ that is once differentiable and finite, i.e.,
+%
+\[
+    \psi_{\omega}(t) = w(t) \exp(-\sqrt{-1} \omega t)
+\]
+%
+Defining $N = \frac{L_{t}}{T}$ and $\omega = 2
+\pi \frac{r}{N}$, the approximate
+inner product is then
+%
+\[
+    \left\langle x , \psi_{\omega} \right\rangle \approx 
+    \frac{1}{N} \sum_{n=0}{N-1} x(Tn) w(Tn) exp(-2 \pi j r \frac{n}{N}) 
+\]
+%
+i.e., the definition of the DFT.%
+\footnote{%
+    Notice however that this is an approximation of the inner product and should
+    not be interpreted as yielding the Fourier series coefficients of a properly
+    sampled signal $x$ periodic in $\frac{L_{t}}$. This means that other
+    evaluations of the inner product that yield more accurate results are
+    possible. For example, the analytic solution is possible if $x$ is assumed
+    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
+    general analytic).  In this case the samples of $x$ are convolved with the
+    appropriate interpolating sinc functions and the integral of this function's
+    product with $\psi$ is evaluated.
+}%
+
+The DFT is readily interpreted as a bank of bandpass filters centred at
+normalized frequencies $\frac{r}{N}$ and with frequency response described by
+the Fourier transform of modulated $w$. Therefore choosing $\psi$ amounts to a
+filter design problem under the constraints that the impulse response of the
+filter must be differentiable in $t$ and finite.
+
+In all the publications these authors reviewed on the DDM, the window used was
+the Hann window.
+Nuttall has designed windows with greater out-of-band rejection (lower
+side-lobes) than the canonical Hann window which are still differentiable.
 

### 2017-02-07 ddm.py

@@ -1,7 +1,27 @@
 # The distribution derivative method and windows it requires
 
 import numpy as np
+import numpy.linalg as LA
 import matplotlib.pyplot as plt
+
+def eig_pow_method(A,d=1.e-6,maxiters=1000):
+    """
+    Compute the greatest eigenvalue of A and its corresponding eigenvector using
+    the power method. Stops when maxiters reached or difference between last
+    greatest absolute value and current greatest absolute value less than d.
+    """
+    N=A.shape[1]
+    b=np.zeros(N,dtype='complex')
+    b[0]=1.
+    b/=LA.norm(b)
+    lst_max=np.max(np.abs(b))
+    for i in xrange(maxiters):
+        b=np.inner(A,b)
+        b/=LA.norm(b)
+        if np.abs(lst_max - np.max(np.abs(b))) < d:
+            break
+        lst_max=np.max(np.abs(b))
+    return (np.vdot(b,np.inner(A,b)),b)
 
 def w_dw_sum_cos(M,a='hanning',norm=False):
     """
@@ -36,6 +56,12 @@ def w_dw_sum_cos(M,a='hanning',norm=False):
             c=np.r_[0.40897,0.5,0.09103]
         elif (a=='c1-nuttall-4'):
             c=np.r_[0.355768,0.487396,0.144232,0.012604]
+        elif (a=='naive-hamming'):
+            # Called naive because this will not include the derivative of the
+            # rectangular window, which is non-zero at the window edges
+            c=np.r_[0.54,0.46]
+        elif (a=='naive-min-blackman-4'):
+            c=np.r_[0.35875,0.48829,0.14128,0.01168]
     else:
         try:
             _it=iter(a)
@@ -50,7 +76,6 @@ def w_dw_sum_cos(M,a='hanning',norm=False):
     if (norm):
         C=np.sum(w)
     w/=C
-
     dw_=((2.*np.pi/M*c[1:]*np.arange(1,len(c))
             *np.power(-1,1+np.arange(1,len(c))))[:,np.newaxis]
         *np.sin(np.pi*2./M*np.outer(np.arange(1,len(c)),m)))

### 2017-02-07 ddm_snr_win_comp.py

@@ -37,8 +37,8 @@ snrs=np.arange(-2,11)*(10.)
 
 # Errors
 errs=dict()
-keys=['hann','c1-nuttall-4','c1-nuttall-3','c1-blackman-4']
-key_clrs=['b','g','r','m']
+keys=['hann','c1-nuttall-4','c1-nuttall-3','c1-blackman-4','naive-min-blackman-4']
+key_clrs=['b','g','r','m','c']
 for k,c in zip(keys,key_clrs):
     errs[k]=dict()
     # Amplitude part

### 2017-02-07 digital_prolate_window_test.py

@@ -1,0 +1,12 @@
+import ddm
+
+# Length of window
+N=25
+# Relative peak sidelobe height dB
+a=-57.
+# Mainlobe width in cycles/sample
+b=(-.07401*a+1.007)/N
+# Design coefficient for -49 > a
+W=(-3.81e-2*a+3.16e-1)/N
+
+

### 2017-02-07 paper/build_thesis.sh

@@ -1,0 +1,13 @@
+#! /bin/bash
+
+# Builds the thesis.tex file complete with bibliography.
+
+# Convert all eps files to pdf
+
+pdflatex paper.tex
+
+BIBINPUTS=. bibtex paper.aux
+pdflatex paper.tex
+pdflatex paper.tex
+mv paper.pdf Esterer_Nicholas_dafx_2017.pdf
+#dvipdf thesis.dvi

### 2017-02-08 paper/paper.tex
Compare Prolate and Nuttall windows.

@@
     \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
-\]
+\end{equation}
 %
@@
 %
-\begin{equation}
+\begin{multline}
     \label{eq:ddm:weighted:sig:derivative}
@@
     \frac{dx}{dt}(t)\overline{\psi}(t)
-    + x(t)\frac{d\overline{\psi}}{dt}(t)
+    + x(t)\frac{d\overline{\psi}}{dt}(t) \\
     = \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
     + x(t)\frac{d\overline{\psi}}{dt}(t)
-\end{equation}
+\end{multline}
 %
@@
 %
-\[
-    \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
+\begin{multline*}
+    \int_{-\infty}^{\infty}\frac{df(t)}{dt}dt \\
+    = \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
     + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
-\]
+\end{multline*}
 %
@@
 sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
-interest to consider a signals featuring a sum of such components, i.e.,
+interest to consider a signals featuring a sum of $P$ such components, i.e.,
 %
 \[
-    s(t) = \sum_( \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j) )
-\]
-%
-In situations where multiple signal sources are known to exist (e.g., recordings
-of multiple speakers or performers) such a model is plausible.
-
-We examine how this mixture model influences the estimation of the $a_{i,j}$.
-Consider a mixture of $P$ components
-%
-\[
-    s(t) = \sum_{i=1}{P} x_{i}(t)
+    s(t) = \sum_{i=1}^{P} x_{i}(t)
 \]
@@
 %
+In situations where multiple signal sources are known to exist (e.g., recordings
+of multiple speakers or performers) such a model is plausible.
+
+We examine how this mixture model influences the estimation of the $a_{i,j}$.
+Consider a mixture of $P$ components
 If we define the weighted signal sum
@@
 \[
-    g(t) = \sum_{i=1}{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}{P} f_{i}(t)
+    g(t) = \sum_{i=1}^{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}^{P} f_{i}(t)
 \]
@@
 %
-\[
+\begin{multline}
     \sum_{i=1}{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
-    0 = 
-    \sum_{i=1}{P}
+    0
+    \\ = 
+    \sum_{i=1}^{P}
     \sum_{j=1}^{Q} j a_{i,j} 
@@
      + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle
-\]
+\end{multline}
 %
 From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
-\right\rangle$ is small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
+\right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
+is small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
 can simply estimate the parameters $a_{i^{\ast},j}$ using
@@
 
-\section{Designing the \psi_{r}}
+\section{Designing the $\psi_{r}$}
 
@@
     \left\langle x , \psi_{\omega} \right\rangle \approx 
-    \frac{1}{N} \sum_{n=0}{N-1} x(Tn) w(Tn) exp(-2 \pi j r \frac{n}{N}) 
+    \frac{1}{N} \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
 \]
@@
     not be interpreted as yielding the Fourier series coefficients of a properly
-    sampled signal $x$ periodic in $\frac{L_{t}}$. This means that other
+    sampled signal $x$ periodic in $L_{t}$. This means that other
     evaluations of the inner product that yield more accurate results are
@@
 }%
-
 The DFT is readily interpreted as a bank of bandpass filters centred at
@@
 filter design problem under the constraints that the impulse response of the
-filter must be differentiable in $t$ and finite.
+filter must be differentiable in $t$ and finite. To minimize the influence of
+all but one component, granted the components's energy concentrations are
+sufficiently separated in frequency, we desire impulse responses with maximum
+out-of-band rejection or equivalently, windows whose Fourier transform exhibits
+lower side-lobes.
 
@@
 the Hann window.
-Nuttall has designed windows with greater out-of-band rejection (lower
-side-lobes) than the canonical Hann window which are still differentiable.
-
-\subsection{Figures}
-\label{ssec:figures}
-All figures should be centred on the column (or page, if the figure spans both columns).
-Figure captions (in italic) should follow each figure and have the format given in Figure \ref{fft_plot}.
-%
-Vectorial figures are preferred. For example when using
-\texttt{Matlab}, export using either Postscript or PDF format. Also,
-in order to provide a better readability, figure text font size
-should be at least identical to footnote font size. To do so using
-\texttt{Matlab}, use the \texttt{subplot} command before plotting.
-If bitmap figures are used, please make sure that the resolution is
-enough for print quality. Fig. \ref{ftt_plot2} illustrates an
-example of a figure spanning two columns.
-%
-%
-
-\subsection{Tables}
-As for figures, all tables should be centered on the column (or page, if the table spans both columns).
-Table captions should be in italic, precede each table and have the format given in Table \ref{tab:example}.
-
-\begin{table}[ht]
-  \caption{\itshape Basic trigonometric values.}
-	\centering
-	\begin{tabular}{|c|c|}
-		\hline
-		$\mathrm{angle}\,(\theta, \mathrm{rad})$ & $\sin \theta$ \\\hline
-		$\frac{\pi}{2}$ & $1$ \\
-		$\pi$ & $0$ \\
-		$\frac{3\pi}{2}$ & $-1$ \\
-		$2\pi$ & $0$ \\\hline
-	\end{tabular}
-	%
-	\label{tab:example}
-\end{table}
-
-\begin{table*}[ht]
-  \caption{{\it Basic trigonometric values, spanning two columns.}}
-	\centering
-  \begin{tabular}{|c|c|c|c|c|c|c|}\hline
-    $\mathrm{angle}\, (\theta, \mathrm{rad})$ & $\sin \theta$ & $\cos \theta $ & $(\sin \theta)/2 $ & $(\cos \theta) /2 $ & $(\sin \theta)/3 $ & $(\cos \theta)/3$    \\\hline
-    $\frac{\pi}{2}$ & $1$ & $0$ & $1/2$ & $0$ & $1/3$ & $0$ \\
-    $\pi$ & $0$ & $-1$ & $0$ & $-1/2$ & $0$ & $-1/3$\\
-    $\frac{3\pi}{2}$ & $-1$ & $0$ & $-1/2$ & $0$ & $-1/3$ & $0$ \\
-    $2\pi$ & $0$ & $1$ & $0$ & $1/2$ & $0$ & $1/3$ \\\hline
- \end{tabular}
-	%
-  \label{tab:example2}
-\end{table*}
-
-\subsection{Equations}
-Equations should be placed on separate lines and numbered:
-
-\begin{equation}
-	X(e^{j\Omega})=\sum_{n=0}^{N-1}x(n)e^{-j\Omega n}
-	\label{eq1}
-	\end{equation}
-	where the sequence $x(n)$ in equation (\ref{eq1}) is a windowed frame:
-	\begin{equation}
-	x(n)=s(n) w(n)
-	\label{eq2}
-\end{equation}
-%
-with a window function $w(n)$.
-
-\subsection{Page Numbers}
-Page numbers will be added to the document in the postprocessing stage, so {\em please leave the numbering as is},
-that is, the first page will start at page DAFX-1 and the last page, at most, will have to be DAFX-8.
-
-\subsection{References}
-A test reference \cite{betser2009sinusoidal}.
-
-\subsubsection{Reference Format}
-The reference format is the standard IEEE one. We recommend to use BibTeX to create the reference list.
+Nuttall has designed windows with lower
+side-lobes than the canonical Hann window which are still differentiable.
 
 \section{Conclusions}
-This template can be found on the conference website.
-For changing the number of author affiliations (1 to 4), uncomment the corresponding regions in the template \texttt{tex} file.
-Please, submit full-length papers (max.~8 pages both oral and poster presentations).
-Submission is fully electronic and automated through the Conference Web Submission System.
-DO NOT send us papers directly by e-mail.
 
 \section{Acknowledgments}
-Many thanks to the great number of anonymous reviewers!
 
@@
 
-\section{Appendix: Margin Check}
-This section shows the column margins for the text. \bigskip\newline
+\section{Appendix}
 
-Lorem ipsum dolor sit amet, consectetur adipisici elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat.
-Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-
-Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis.
-
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, At accusam aliquyam diam diam dolore dolores duo eirmod eos erat, et nonumy sed tempor et et invidunt justo labore Stet clita ea et gubergren, kasd magna no rebum.
-sanctus sea sed takimata ut vero voluptua.
-est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat.
-
-Consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-Lorem ipsum dolor sit amet, consectetur adipisici elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat.
-Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et accumsan et iusto odio dignissim qui blandit praesent luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
-
-Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum.
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper suscipit lobortis nisl ut aliquip ex ea commodo consequat.
-
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse molestie consequat, vel illum dolore eu feugiat nulla facilisis.
-
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, At accusam aliquyam diam diam dolore dolores duo eirmod eos erat, et nonumy sed tempor et et invidunt justo labore Stet clita ea et gubergren, kasd magna no rebum.
-sanctus sea sed takimata ut vero voluptua.
-est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat.
-
-Consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 \end{document}

### 2017-02-08 digital_prolate_window_test.py

@@ -1,12 +1,26 @@
+import numpy as np
+import numpy.linalg
 import ddm
+import matplotlib.pyplot as plt
 
 # Length of window
 N=25
+#N=513
 # Relative peak sidelobe height dB
 a=-57.
 # Mainlobe width in cycles/sample
 b=(-.07401*a+1.007)/N
 # Design coefficient for -49 > a
 W=(-3.81e-2*a+3.16e-1)/N
-
-
+#W=.8
+i=np.arange(N,dtype='double')
+A=np.diag(np.cos(2*np.pi*W)*(((N-1.)/2.-i)**2.))
+A+=np.diag(0.5*i[1:]*(N-i[1:]),-1)
+A+=np.diag(0.5*i[1:]*(N-i[1:]),1)
+#(l,v)=ddm.eig_pow_method(A)
+(L,V)=np.linalg.eig(A)
+v=V[:,np.argmax(np.abs(L))]
+fig,(ax1,ax2)=plt.subplots(2,1)
+ax1.plot(i,np.real(v))
+ax2.plot(np.arange(512),20.*np.log10(np.abs(np.fft.fft(v[:-1],512))))
+plt.show()

### 2017-02-08 paper/build_thesis.sh

@@ -1,13 +1,0 @@
-#! /bin/bash
-
-# Builds the thesis.tex file complete with bibliography.
-
-# Convert all eps files to pdf
-
-pdflatex paper.tex
-
-BIBINPUTS=. bibtex paper.aux
-pdflatex paper.tex
-pdflatex paper.tex
-mv paper.pdf Esterer_Nicholas_dafx_2017.pdf
-#dvipdf thesis.dvi

### 2017-02-08 search_digital_prolate_window.py

@@ -1,0 +1,59 @@
+import numpy as np
+import numpy.linalg
+import ddm
+import matplotlib.pyplot as plt
+import sigmod as sm
+
+# Length of window
+N=513
+# Length of DFT (controls zero-padding)
+N_F=1024
+#N=513
+# Design coefficients
+# This range found empirically to give peak side-lobes close to desired one
+W=np.arange(.005,.01,0.0001)
+# Ratio of max to peak sidelobe (dB)
+a=np.zeros(len(W))
+# The ratio desired
+a_des=93.32
+#W=.8
+i=np.arange(N,dtype='double')
+
+w_close=None
+a_diff_close=100.
+v_close=None
+v_F_close=None
+for n,W_ in enumerate(W):
+    A=np.diag(np.cos(2*np.pi*W_)*(((N-1.)/2.-i)**2.))
+    A+=np.diag(0.5*i[1:]*(N-i[1:]),-1)
+    A+=np.diag(0.5*i[1:]*(N-i[1:]),1)
+    #(l,v)=ddm.eig_pow_method(A)
+    (L,V)=np.linalg.eig(A)
+    v=V[:,np.argmax(np.abs(L))]
+    v_F=20.*np.log10(np.abs(np.fft.fft(v,N_F)))
+    v_F=np.concatenate((v_F[N_F/2:],v_F[:N_F/2]))
+    (ma,mai)=sm.lextrem(v_F)
+    ma_srt=np.sort(ma.flatten())
+    a[n]=ma_srt[-1]-ma_srt[-2]
+    a_diff=np.abs(a_des-a[n])
+    if (a_diff < a_diff_close):
+        a_diff_close=a_diff
+        w_close=W_
+        v_close=v
+        v_F_close=v_F
+
+print "a_diff_close: %f" % (a_diff_close,)
+print "v_close end point: %g" % (v_close[0],)
+
+fig, (ax1,ax2) = plt.subplots(2,1)
+ax1.plot(W,a)
+ax1.set_title("W versus peak side-lobe height")
+w_nuttall=ddm.w_dw_sum_cos(N-1,a='c1-nuttall-4')[0]
+w_F_nuttall=20.*np.log10(np.abs(np.fft.fft(w_nuttall,N_F)))
+w_F_nuttall=np.concatenate((w_F_nuttall[N_F/2:],w_F_nuttall[:N_F/2]))
[…]

### 2017-02-08 ddm_snr_win_comp.py
Frequency errors correctly calculated now.

@@ -125,6 +125,7 @@ for k in errs.keys():
             a2_err+=np.abs(a2-a2_)
             # Find minimum distance on circle
             ph0_err+=min([(ph0-ph0_)%(2.*np.pi),(ph0_-ph0)%(2.*np.pi)])
+            # Frequency error found on circle too (because of sampling theorem)
             ph1_err+=min([(ph1-ph1_)%(np.pi*F_s),(ph1_-ph1)%(np.pi*F_s)])
             ph2_err+=np.abs(ph2-ph2_)
             n += 1

### 2017-02-09 find_opt_window.py
Trying to find optimal windows
Trying to fit to optimal shape, that is, a window that is zero everywhere except in the first bin.
Either we need to try oversampling or we need to checkout the old Harris method: it doesn't work for more
than 2 cosines in the sum.

@@ -1,0 +1,82 @@
+# Find an optimal window by matching its frequency response with ideal
+import numpy as np
+import cvxopt
+from scipy.linalg import block_diag
+import matplotlib.pyplot as plt
+
+# Window length
+N=512
+
+# Oversampling (for plotting)
+os=4
+
+# "Half" Fourier basis (cosine part only)
+n=np.arange(N)
+k=np.arange(0,N)
+F=np.cos(-2*np.pi*np.outer(k,n)/N)
+
+# Number of cosines to sum
+M=4
+m=np.arange(M)
+# Cosines to sum to get window
+C=np.cos(2*np.pi*np.outer(n,m)/N)*np.power(-1.,np.arange(M))
+
+# P matrix for optimization problem
+P=block_diag(F,np.zeros(C.shape))
+P=np.dot(P.T,P)
+
+# q vector for optimization problem
+q=np.zeros((N+M,1))
+q[0]=1.
+q=-2.*np.dot(P.T,q)
+
+# A constraint matrix for optimization problem
+A=block_diag(-1*np.identity(F.shape[1]),np.ones((1,M)))
+A[:C.shape[0],F.shape[1]:]=C
+# constrain x[0] to be 0
+a_=np.zeros((1,M+N))
+#a_[0]=1.
+a_[0,N:]=C[0,:]
+A=np.concatenate((A,a_),axis=0)
+
+# b vector for optimization problem
+b=np.zeros((C.shape[0]+1,1))
+b[-1]=1.
+# constrain x[0] to be 0
+b=np.concatenate((b,[[0.]]),axis=0)
+
+# G inequality matrix
+G=np.concatenate((np.identity(F.shape[1]),np.zeros((F.shape[1],C.shape[1]))),axis=1)
+G=np.concatenate((G,-G),axis=0)
+
+# h inequality vector
+h=np.concatenate((np.ones(F.shape[1]),np.zeros(F.shape[1])),axis=0)
+
+P=cvxopt.matrix(P)
+q=cvxopt.matrix(q)
+A=cvxopt.matrix(A)
+b=cvxopt.matrix(b)
+G=cvxopt.matrix(G)
+h=cvxopt.matrix(h)
+
+sol=cvxopt.solvers.qp(P,q,G=G,h=h,A=A,b=b)
+
+if sol['status'] == 'optimal':
+    print 'solution found'
+    print 'x='
+    print sol['x'][:N]
+    print 'F*x='
[…]

### 2017-02-09 real_hann_ft.py

@@ -1,0 +1,18 @@
+import ddm
+import numpy as np
+
+N=8
+n=np.arange(N)
+k=np.arange(N)
+
+w=ddm.w_dw_sum_cos(8,'hann')[0]
+f_fft=np.real(np.fft.fft(w))
+
+# vectors of real part only
+C=np.cos(2*np.pi*np.outer(k,n)/N)
+
+f_ct=np.inner(C,w)
+#f_ct/=f_ct[0]
+
+print f_fft
+print f_ct

### 2017-02-10 fft_vs_cos_mat.py
Working on building window that fits mid-points of DFT because this is where the maxima are.

@@ -1,0 +1,26 @@
+# We are interested in Fourier transforming even functions for which the FT is
+# purely real. Therefore should suffice to only use cosine basis functions,
+# right?
+
+import ddm
+import numpy as np
+import matplotlib.pyplot as plt
+
+M = 8
+N = 2*M
+w,dw=ddm.w_dw_sum_cos(M,a='hanning')
+W=np.fft.fft(w,N)
+k=np.arange(N)
+n=np.arange(N)
+F=np.cos(-2*np.pi*np.outer(k,n)/N)
+W_=np.dot(F,np.concatenate((np.zeros((N-M)/2),w,np.zeros((N-M)/2))))
+fig,((ax1,ax2),(ax3,ax4))=plt.subplots(2,2)
+ax1.plot(k,np.abs(W))
+ax1.set_title('DFT')
+ax2.plot(k,np.abs(W_))
+ax2.set_title('Dab cosine')
+ax3.plot(np.concatenate((k[0:1],k[1::2])),np.concatenate((np.abs(W[0:1]),np.abs(W[1::2]))))
+ax3.set_title('DFT, origin and midpoints')
+ax4.set_title('dab cosine, origin and midpoints')
+ax4.plot(np.concatenate((k[0:1],k[1::2])),np.concatenate((np.abs(W_[0:1]),np.abs(W_[1::2]))))
+plt.show()

### 2017-02-10 find_opt_window_midpoints.py

@@ -1,0 +1,91 @@
+# Find an optimal window by matching its frequency response with ideal
+# This matches the mid-points of the lobes of the DFT rather than the troughs
+import numpy as np
+import cvxopt
+from scipy.linalg import block_diag
+import matplotlib.pyplot as plt
+
+# Window length
+N=512
+
+# Oversampling (for plotting)
+os=4
+
+# "Half" Fourier basis (cosine part only)
+n=np.arange(N)
+k=np.arange(0.5,N,1)
+# First bin centred at frequency 0 (DC)
+F=np.cos(-2*np.pi*n/N).reshape((1,N))
+F=np.concatenate((F,np.cos(-2*np.pi*np.outer(k,n)/N)),axis=0)
+
+# Number of cosines to sum
+M=3
+m=np.arange(M)
+# Cosines to sum to get window
+C=np.cos(2*np.pi*np.outer(n,m)/N)*np.power(-1.,np.arange(M))
+
+# P matrix for optimization problem
+P=block_diag(F,np.zeros(C.shape))
+P=np.dot(P.T,P)
+
+# q vector for optimization problem
+q=np.zeros((N+M,1))
+q[0]=1.
+q=-2.*np.dot(P.T,q)
+
+# A constraint matrix for optimization problem
+A=block_diag(-1*np.identity(F.shape[1]),np.ones((1,M)))
+A[:C.shape[0],F.shape[1]:]=C
+# constrain x[0] to be 0
+a_=np.zeros((1,M+N))
+#a_[0]=1.
+a_[0,N:]=C[0,:]
+A=np.concatenate((A,a_),axis=0)
+
+# b vector for optimization problem
+b=np.zeros((C.shape[0]+1,1))
+b[-1]=1.
+# constrain x[0] to be 0
+b=np.concatenate((b,[[0.]]),axis=0)
+
+# G inequality matrix
+G=np.concatenate((np.identity(F.shape[1]),np.zeros((F.shape[1],C.shape[1]))),axis=1)
+G=np.concatenate((G,-G),axis=0)
+
+# h inequality vector
+h=np.concatenate((np.ones(F.shape[1]),np.zeros(F.shape[1])),axis=0)
+
+P=cvxopt.matrix(P)
+q=cvxopt.matrix(q)
+A=cvxopt.matrix(A)
+b=cvxopt.matrix(b)
+G=cvxopt.matrix(G)
+h=cvxopt.matrix(h)
+
[…]

### 2017-02-20 paper/paper.tex
Added the ways of windows
Can synthesize arbitrary prolate spheroidal window using parameter W and length
N.

Can approximate any window by a once-differentiable sum-of-cosines window via
constrained least-squares.

This new window has been incorporated into the measurements. It performs poorly
in noise, probably due to the extremely large main lobe. It performs the best at
obtaining the parameters of two components in mixture (in no noise). Perhaps
using more bins around the maximum will improve estimation in the noisy case. It
would be interesting to see how the estimation accuracy changes a

@@
 
+The family of parametric windows whose construction is based on functions
+proposed by Slepian et al. maximimzing the energy in a given bandwidth can be
+tuned to have extremely low side-lobes, at the expense of main-lobe width.
+Differentiation of these window functions may be possible but is not as
+straight-forward as differentiation of the sum-of-cosine windows. Furthermore,
+the windows do not generally have end-points equal to 0. Motivated by this, and
+the desire to approximate aribtrary windows using sums of cosines leads us to
+the design of high-performance windows (e.g., with extremely low side-lobes) by
+approximation.
+
 \section{Conclusions}
@@
 \bibliographystyle{IEEEbib}
-\bibliography{paper} % requires file DAFx17_tmpl.bib
+%\bibliography{paper} % requires file DAFx17_tmpl.bib
 

### 2017-02-20 approx_psw_cosines.py

@@ -1,0 +1,81 @@
+import ddm
+import sigmod as sm
+import numpy as np
+import matplotlib.pyplot as plt
+import cvxopt
+
+show_plot=False
+
+# Window length
+N=512
+n=np.arange(N)
+
+# Oversampling (for plotting)
+os=4
+
+# Number of cosines to sum
+M=47
+m=np.arange(M)
+# Cosines to sum to get window
+C=np.cos(2*np.pi*np.outer(n,m)/N)*np.power(-1.,np.arange(M))
+
+# Prolate spheroidal window
+W=0.77
+v=ddm.psw_design(N+1,0.77)
+# Make window positive
+if (np.abs(np.min(v)) > np.abs(np.max(v))):
+    v *= -1.
+# Make window maximum equal to 1
+v/=np.max(v)
+
+# Solve for as that approximate v
+# Constraint matrix
+A=np.concatenate((np.ones((1,M)),C[0,:].reshape((1,M))),axis=0)
+b=np.array([[1.],[0.]])
+
+# Prepare matrices to solve constrained least-squares
+P=2.*np.dot(C.T,C)
+q=-2.*np.dot(C.T,v[:-1].reshape(N,1))
+
+A=cvxopt.matrix(A)
+b=cvxopt.matrix(b)
+P=cvxopt.matrix(P)
+q=cvxopt.matrix(q)
+
+a=cvxopt.solvers.qp(P,q,A=A,b=b)['x']
+print 'a coefficients'
+print a
+a=np.array(a).flatten()
+
+# save to file
+np.savetxt('/tmp/prolate_approx_W=0.77_M=%d.txt' % (M,),a)
+
+# The sum-of-cosine window
+w=ddm.w_dw_sum_cos(N,a)[0]
+
+# Magnitude spectra
+N_F=N*os
+v_F=np.fft.fft(v,N_F)
+w_F=np.fft.fft(np.concatenate((w.reshape((1,N)),w[0].reshape((1,1))),axis=1),N_F).flatten()
+v_F=20*np.log10(np.abs(v_F))
+w_F=20*np.log10(np.abs(w_F))
+v_F-=np.max(v_F)
+w_F-=np.max(w_F)
+v_F=np.concatenate((v_F[N_F:],v_F[:N_F]))
+w_F=np.concatenate((w_F[N_F:],w_F[:N_F]))
+bins_F=np.arange(0,N,1./os)
+
+fig1,axs=plt.subplots(2,2)
+axs[0,0].plot(bins_F,v_F)
[…]

### 2017-02-20 comp_offset_chirp_est_err.py

@@ -21,8 +21,8 @@ chirps=ddm.build_offset_chirps(N_chirps=4,
                                W_l_ms=W_l_ms,
                                b1_r=[0.,np.pi*F_s])
 
-wins=['hann','c1-nuttall-4','c1-blackman-4']
-line_stys=['solid','dotted','dashed']
+wins=['hann','c1-nuttall-4','c1-blackman-4','prolate-0.77-approx-47']
+line_stys=['solid','dotted','dashed','dashdot']
 sr_min=-60
 srs=np.arange(sr_min,0,10)
 n_diffs=128

### 2017-02-20 ddm.py

@@ -62,6 +62,56 @@ def w_dw_sum_cos(M,a='hanning',norm=False):
             c=np.r_[0.54,0.46]
         elif (a=='naive-min-blackman-4'):
             c=np.r_[0.35875,0.48829,0.14128,0.01168]
+        elif (a=='prolate-0.77-approx-47'):
+            # Does the number of figures contribute significantly to the
+            # accuracy?
+            c=np.r_[6.815625423533416827e-02,
+                    1.343413407697203465e-01,
+                    1.285968082160944270e-01,
+                    1.195619690697207610e-01,
+                    1.079670679318169152e-01,
+                    9.469240652932217617e-02,
+                    8.065884608008552781e-02,
+                    6.672467071524876281e-02,
+                    5.360436978540508018e-02,
+                    4.181885562354893671e-02,
+                    3.167949690383391192e-02,
+                    2.330191778479831152e-02,
+                    1.664111594502999322e-02,
+                    1.153766107795279119e-02,
+                    7.765363769402260606e-03,
+                    5.073125727673936242e-03,
+                    3.216749477092172276e-03,
+                    1.979436174490603606e-03,
+                    1.181952653281245508e-03,
+                    6.847647303719338633e-04,
+                    3.848668599270928963e-04,
+                    2.098211237310444353e-04,
+                    1.109419375406991352e-04,
+                    5.688331526814708938e-05,
+                    2.827794498282796775e-05,
+                    1.362737098580978749e-05,
+                    6.365042844173701925e-06,
+                    2.880948326056731291e-06,
+                    1.263369519424718326e-06,
+                    5.366584133144254092e-07,
+                    2.207728978301219456e-07,
+                    8.793812084883303941e-08,
+                    3.390713653010824865e-08,
+                    1.265266172182148338e-08,
+                    4.568137255870320335e-09,
+                    1.595319231469439323e-09,
+                    5.387492617615924091e-10,
+                    1.758854467412710503e-10,
+                    5.549388693644718546e-11,
+                    1.691607734986330884e-11,
+                    4.980293127726517115e-12,
+                    1.415506327451228367e-12,
[…]

### 2017-02-20 ddm_snr_win_comp.py

@@ -33,11 +33,11 @@ N_eval=100
 
 
 # SNRs to test
-snrs=np.arange(-2,11)*(10.)
+snrs=np.arange(-2,20)*(10.)
 
 # Errors
 errs=dict()
-keys=['hann','c1-nuttall-4','c1-nuttall-3','c1-blackman-4','naive-min-blackman-4']
+keys=['hann','c1-nuttall-4','c1-nuttall-3','c1-blackman-4','prolate-0.77-approx-47']
 key_clrs=['b','g','r','m','c']
 for k,c in zip(keys,key_clrs):
     errs[k]=dict()

### 2017-02-20 fft_vs_cos_mat.py

@@ -9,15 +9,19 @@ import matplotlib.pyplot as plt
 M = 8
 N = 2*M
 w,dw=ddm.w_dw_sum_cos(M,a='hanning')
-W=np.fft.fft(w,N)
+w_padded=np.concatenate((w,np.zeros(N-M)))
+w_padded=np.concatenate((w_padded[(M/2):],w_padded[:(M/2)]))
+#W=np.fft.fft(np.concatenate((np.zeros((N-M)/2),w,np.zeros((N-M)/2))))
+W=np.fft.fft(w_padded)
 k=np.arange(N)
 n=np.arange(N)
 F=np.cos(-2*np.pi*np.outer(k,n)/N)
-W_=np.dot(F,np.concatenate((np.zeros((N-M)/2),w,np.zeros((N-M)/2))))
+#W_=np.dot(F,np.concatenate((np.zeros((N-M)/2),w,np.zeros((N-M)/2))))
+W_=np.dot(F,w_padded)
 fig,((ax1,ax2),(ax3,ax4))=plt.subplots(2,2)
-ax1.plot(k,np.abs(W))
+ax1.plot(k,np.real(W))
 ax1.set_title('DFT')
-ax2.plot(k,np.abs(W_))
+ax2.plot(k,W_)
 ax2.set_title('Dab cosine')
 ax3.plot(np.concatenate((k[0:1],k[1::2])),np.concatenate((np.abs(W[0:1]),np.abs(W[1::2]))))
 ax3.set_title('DFT, origin and midpoints')

### 2017-02-20 find_opt_window_l_inf_norm.py

@@ -1,0 +1,112 @@
+# This doesn't work...
+
+import numpy as np
+import cvxopt
+from scipy.linalg import block_diag
+import matplotlib.pyplot as plt
+
+# Window length (non-zero part)
+N=512
+
+# Oversampling (for plotting)
+os=4
+
+# L is total length of window including zero-padding
+L=2*N
+
+# "Half" Fourier basis (cosine part only)
+n=np.arange(N)
+l=np.arange(L)
+k=np.arange(1,L,2)
+# First bin centred at frequency 0 (DC)
+k=np.concatenate(([0],k))
+F_=np.cos(-2*np.pi*np.outer(k,l)/L)
+F=F_[:,((L-N)/2):(-(L-N)/2)]
+d=np.zeros((F.shape[0],1))
+d[0]=1.
+
+# Number of cosines to sum
+M=4
+m=np.arange(M)
+# Cosines to sum to get window
+C=np.cos(2*np.pi*np.outer(n,m)/N)*np.power(-1.,np.arange(M))
+
+
+# The bin from which to start checking the sidelobes
+R=0
+
+# We will solve a LP to find a solution
+# See http://cvxopt.org/userguide/coneprog.html#linear-programming for the form
+
+# The c vector of the LP
+c=np.concatenate((np.zeros(N+M),[1]))
+
+# G inequality matrix
+#G=np.zeros((2*(L/2+1-R)+1,N+M+1))
+#G[:(L/2+1-R),:]=np.concatenate((F[R:(L/2+1),:],np.zeros(((L/2+1)-R,M)),np.ones((L/2+1-R,1))),axis=1)
+#G[(L/2+1-R):-1,:]=np.concatenate((-1*F[R:(L/2+1),:],np.zeros(((L/2+1)-R,M)),np.ones((L/2+1-R,1))),axis=1)
+#G[-1,-1]=-1.
+G=np.zeros((2*(N-2*R)+1,N+M+1))
+G[:(N-2*R),:]=np.concatenate((F[R+1:-R,:],np.zeros((N-2*R,M)),np.ones((N-2*R,1))),axis=1)
+G[(N-2*R):-1,:]=np.concatenate((-1*F[R+1:-R,:],np.zeros((N-2*R,M)),np.ones((N-2*R,1))),axis=1)
+G[-1,-1]=-1.
+G=np.concatenate((
+        np.concatenate((np.identity(N),np.zeros((N,M)),np.zeros((N,1))),axis=1),
[…]

### 2017-02-20 find_opt_window_l_inf_norm_oversampling.py

@@ -1,0 +1,125 @@
+# This doesn't work...
+
+import numpy as np
+import cvxopt
+from scipy.linalg import block_diag
+import matplotlib.pyplot as plt
+import ddm
+import sys
+
+# Window length (non-zero part)
+N=512
+
+# Oversampling
+os=16
+
+# L is total length of window including zero-padding
+L=os*N
+
+# "Half" Fourier basis (cosine part only)
+n=np.arange(N)
+l=np.arange(L)
+k=np.arange(L)
+F_=np.cos(-2*np.pi*np.outer(k,l)/L)
+#F=F_[:,((L-N)/2):(-(L-N)/2)]
+F=np.concatenate((F_[:,:(N/2)],F_[:,-(N/2):]),axis=1)
+
+## Show it is correct
+#w_test,dw=ddm.w_dw_sum_cos(N,a='c1-nuttall-4')
+##W_test=np.dot(F,w_test)
+#w_test_padded=np.concatenate((w_test,np.zeros(L-N)))
+#w_test_padded=np.concatenate((w_test_padded[(N/2):],w_test_padded[:(N/2)]))
+##W_test=np.inner(F_,np.concatenate((np.zeros((L-N)/2),w_test,np.zeros((L-N)/2))))
+##W_test=np.dot(F_,w_test_padded)
+#W_test=np.dot(F,np.concatenate((w_test_padded[:(N/2)],w_test_padded[-(N/2):])))
+#plt.plot(k/float(os),20*np.log10(W_test))
+#plt.show()
+
+d=np.zeros((F.shape[0],1))
+d[0]=1.
+
+# Number of cosines to sum
+M=4
+m=np.arange(M)
+# Cosines to sum to get window
+C=np.cos(2*np.pi*np.outer(n,m)/N)*np.power(1.,np.arange(M))
+
+
+# The bin from which to start checking the sidelobes
+R=0
+
+# We will solve a LP to find a solution
+# See http://cvxopt.org/userguide/coneprog.html#linear-programming for the form
+
+# The c vector of the LP
+c=np.concatenate((np.zeros(N+M),[1]))
+
+# G inequality matrix
+#G=np.zeros((2*(L/2+1-R)+1,N+M+1))
[…]

### 2017-02-20 find_opt_window_midpoints.py

@@ -1,25 +1,33 @@
 # Find an optimal window by matching its frequency response with ideal
 # This matches the mid-points of the lobes of the DFT rather than the troughs
+# Because this uses a least-squared error, the solution is not the same as the
+# Blackman-Harris solution (the minimum height of the highest side lobe). To get
+# that, you must use the L-infinity norm.
 import numpy as np
 import cvxopt
 from scipy.linalg import block_diag
 import matplotlib.pyplot as plt
 
-# Window length
+# Window length (non-zero part)
 N=512
 
 # Oversampling (for plotting)
 os=4
 
+# L is total length of window including zero-padding
+L=2*N
+
 # "Half" Fourier basis (cosine part only)
 n=np.arange(N)
-k=np.arange(0.5,N,1)
+l=np.arange(L)
+k=np.arange(1,L,2)
 # First bin centred at frequency 0 (DC)
-F=np.cos(-2*np.pi*n/N).reshape((1,N))
-F=np.concatenate((F,np.cos(-2*np.pi*np.outer(k,n)/N)),axis=0)
+k=np.concatenate(([0],k))
+F_=np.cos(-2*np.pi*np.outer(k,l)/L)
+F=F_[:,((L-N)/2):(-(L-N)/2)]
 
 # Number of cosines to sum
-M=3
+M=4
 m=np.arange(M)
 # Cosines to sum to get window
 C=np.cos(2*np.pi*np.outer(n,m)/N)*np.power(-1.,np.arange(M))
@@ -53,7 +61,8 @@ G=np.concatenate((np.identity(F.shape[1]),np.zeros((F.shape[1],C.shape[1]))),axi
 G=np.concatenate((G,-G),axis=0)
 
 # h inequality vector
-h=np.concatenate((np.ones(F.shape[1]),np.zeros(F.shape[1])),axis=0)
+#h=np.concatenate((np.ones(F.shape[1]),np.zeros(F.shape[1])),axis=0)
+h=np.concatenate((np.ones(F.shape[1]),1*np.ones(F.shape[1])),axis=0)
 
 P=cvxopt.matrix(P)
 q=cvxopt.matrix(q)
@@ -83,7 +92,7 @@ if sol['status'] == 'optimal':
     ax2.set_title('DFT of window %d x oversampled' % (os,))
     f_opt=np.dot(F,np.array(sol['x'][:N]).flatten())
     f_opt_max=np.max(np.abs(f_opt))
[…]

### 2017-02-20 search_min_digital_prolate_window.py

@@ -1,0 +1,59 @@
+import numpy as np
+import numpy.linalg
+import ddm
+import matplotlib.pyplot as plt
+import sigmod as sm
+
+# Length of window
+N=513
+# Length of DFT (controls zero-padding)
+N_F=1024
+#N=513
+# Design coefficients
+# This range found empirically to give peak side-lobes close to desired one
+W=np.arange(.01,.99,.01)
+# Ratio of max to peak sidelobe (dB)
+a=np.zeros(len(W))
+# The ratio desired
+a_des=93.32
+#W=.8
+i=np.arange(N,dtype='double')
+
+w_min=None
+a_min=0
+v_min=None
+v_F_min=None
+for n,W_ in enumerate(W):
+    A=np.diag(np.cos(2*np.pi*W_)*(((N-1.)/2.-i)**2.))
+    A+=np.diag(0.5*i[1:]*(N-i[1:]),-1)
+    A+=np.diag(0.5*i[1:]*(N-i[1:]),1)
+    #(l,v)=ddm.eig_pow_method(A)
+    (L,V)=np.linalg.eig(A)
+    v=V[:,np.argmax(np.abs(L))]
+    v_F=20.*np.log10(np.abs(np.fft.fft(v,N_F)))
+    v_F=np.concatenate((v_F[N_F/2:],v_F[:N_F/2]))
+    (ma,mai)=sm.lextrem(v_F)
+    ma_srt=np.sort(ma.flatten())
+    a[n]=ma_srt[-1]-ma_srt[-2]
+    if (a[n] > a_min):
+        a_min=a[n]
+        w_min=W_
+        v_min=v
+        v_F_min=v_F
+
+print "a_min: %f" % (a_min,)
+print "v_min end point: %g" % (v_min[0],)
+print "w_min: %f" % (w_min,)
+
+fig, (ax1,ax2) = plt.subplots(2,1)
+ax1.plot(W,a)
+ax1.set_title("W versus peak side-lobe height")
+w_nuttall=ddm.w_dw_sum_cos(N-1,a='c1-nuttall-4')[0]
+w_F_nuttall=20.*np.log10(np.abs(np.fft.fft(w_nuttall,N_F)))
+w_F_nuttall=np.concatenate((w_F_nuttall[N_F/2:],w_F_nuttall[:N_F/2]))
+leg_nuttall,=ax2.plot(np.arange(N_F),w_F_nuttall-np.max(w_F_nuttall),c='r',label="Nuttall")
[…]

### 2017-02-20 synth_min_digital_prolate_window.py

@@ -1,0 +1,41 @@
+import numpy as np
+import numpy.linalg
+import ddm
+import matplotlib.pyplot as plt
+import sigmod as sm
+
+# Length of window
+N=513
+# Length of DFT (controls zero-padding)
+N_F=1024
+#N=513
+# Design coefficients
+# This coefficient found to give lowest side lobes
+W=0.77
+v=ddm.psw_design(N,W)
+# If negative, invert (will not affect maginitude reponse)
+if (np.min(v) < -0.1):
+    v*=-1.
+# Make maximum 1.
+v/=np.max(v)
+v_F=20.*np.log10(np.abs(np.fft.fft(v,N_F)))
+v_F=np.concatenate((v_F[N_F/2:],v_F[:N_F/2]))
+w_min=W
+v_min=v
+v_F_min=v_F
+
+print "v_min end point: %g" % (v_min[0],)
+print "w_min: %f" % (w_min,)
+
+fig, (ax1,ax2) = plt.subplots(2,1)
+ax1.plot(np.arange(N),v)
+ax1.set_title("Spheroidal window, time-domain")
+w_nuttall=ddm.w_dw_sum_cos(N-1,a='c1-nuttall-4')[0]
+w_F_nuttall=20.*np.log10(np.abs(np.fft.fft(w_nuttall,N_F)))
+w_F_nuttall=np.concatenate((w_F_nuttall[N_F/2:],w_F_nuttall[:N_F/2]))
+leg_nuttall,=ax2.plot(np.arange(N_F),w_F_nuttall-np.max(w_F_nuttall),c='r',label="Nuttall")
+leg_prolate,=ax2.plot(np.arange(N_F),v_F_min-np.max(v_F_min),c='b',label="Prolate")
+ax2.set_title("nuttall versus prolate, frequency domain")
+ax2.legend(handles=[leg_nuttall,leg_prolate])
+print "w_nuttall end point: %g" % (w_nuttall[0],)
+plt.show()

### 2017-02-22 comp_offset_chirp_est_err.py
DDM can now use arbitrary odd number of bins.

@@ -11,7 +11,7 @@ import warnings
 
 F_s=16000
 W_l_ms=32
-
+R=3
 # prepare chirps
 
 chirps=ddm.build_offset_chirps(N_chirps=4,
@@ -23,9 +23,9 @@ chirps=ddm.build_offset_chirps(N_chirps=4,
 
 wins=['hann','c1-nuttall-4','c1-blackman-4','prolate-0.77-approx-47']
 line_stys=['solid','dotted','dashed','dashdot']
-sr_min=-60
+sr_min=-30
 srs=np.arange(sr_min,0,10)
-n_diffs=128
+n_diffs=64
 diffs=xrange(n_diffs)
 errs=dict()
 for w in wins:
@@ -69,8 +69,10 @@ for w in wins:
                     # Sum to make final signal
                     x=c1.x+c2_.x
                     try:
-                        errs_1=ddm.p2_1_3_est(x,c1,0,w,F_s)
-                        errs_2=ddm.p2_1_3_est(x,c2_,d,w,F_s)
+                        #errs_1=ddm.p2_1_3_est(x,c1,0,w,F_s)
+                        #errs_2=ddm.p2_1_3_est(x,c2_,d,w,F_s)
+                        errs_1=ddm.p2_1_3_est(x,c1,0,w,F_s,R)
+                        errs_2=ddm.p2_1_3_est(x,c2_,d,w,F_s,R)
                     except TypeError:
                         nlsqerrs += 1
                         continue

### 2017-02-22 ddm.py

@@ -133,6 +133,79 @@ def w_dw_sum_cos(M,a='hanning',norm=False):
     dw/=C
     return (w,dw)
 
+def ddm_p2_1_R(x,w,dw,kma0,R=3):
+    """
+    Compute parameters of 2nd order polynomial using R bins surrounding the
+    maximum of the STFT at the centre of signal x.
+
+    x:  
+        the signal to analyse, must have length of at least N_w where N_w is
+        the length of the window.
+    w:  
+        the analysis window.
+    dw: 
+        the derivative of the analysis window.
+    kma0:
+        the index of the maximum. From here the atoms are chosen as the one
+        corresponding to this index and the (N-1) surrounding ones.
+    R:
+        the number of atoms to use. Must be odd.
+
+    Returns
+
+    a:
+        a vector containing the estimated parameters.
+    """
+    if (R % 2 != 1):
+        raise Error('R must be odd.')
+
+    N_w=len(w)
+    nx0=np.arange(N_w)
+    x0=x[nx0]
+    #k_plus=(np.arange((R-1)/2) + kma0 + 1) % N_w
+    #k_minus=((kma0 - np.arange((R-1)/2) - 1) % N_w)[::-1]
+    k_plus=(np.arange((R-1)/2) + kma0 + 1)
+    k_minus=((kma0 - np.arange((R-1)/2) - 1))[::-1]
+    k_atoms=np.concatenate((k_minus,[kma0],k_plus))
+    # Shitty fourier basis, why?
+    F=np.exp(-2.*np.pi*1j*np.outer(k_atoms,nx0)/float(N_w))
+    Xp1w=np.dot(F,x0*w)
+    Xp2w=np.dot(F,2.*nx0*x0*w)
+    Xdw_=np.dot(F,x0*dw)
+    #Xp1w=np.fft.fft(x0*w)
+    #Xp2w=np.fft.fft(2.*nx0*x0*w)
+    #Xdw_=np.fft.fft(x0*dw)
+    Xdw=Xp1w*(-2.*np.pi*1j*k_atoms/float(N_w))+Xdw_
+    A=np.c_[
+            np.r_[
+#                Xp1w[k_atoms]
+                Xp1w
+                ],
+            np.r_[
+#                Xp2w[k_atoms]
+                Xp2w
+                ],
+            ]
+    c=np.c_[
+            np.r_[
+#                Xdw[k_atoms]
+                Xdw
[…]

### 2017-02-22 ddm_snr_win_comp.py

@@ -15,6 +15,8 @@ W_l_ms=32
 W_l=F_s*(W_l_ms/1000.)
 # Time indices
 t=np.arange(W_l)/float(F_s)
+# Number of bins to use in estimation
+R=3
 
 # Parameter ranges
 # Amplitude part
@@ -97,7 +99,8 @@ for k in errs.keys():
             # Add noise
             y=x+g_no*np.random.standard_normal(int(W_l))
             # Estimate parameters
-            alpha=ddm.ddm_p2_1_3(y,w,dw,kma0)
+            alpha=ddm.ddm_p2_1_R(y,w,dw,kma0,R)
+#            alpha=ddm.ddm_p2_1_3(y,w,dw,kma0)
             if (alpha == None):
                 # If there was a problem solving the system of equations, just
                 # ignore and try again

### 2017-02-28 paper/paper.tex
Added a bit on the motivation for sum-of-cosine window approximations
Have started design example section.

--- 2017-02-08 paper/paper.tex
@@
 have been developed. Many equivalent techniques have been developed for
-estimating the $a_j$ have been developed. In this paper we compare with the
+estimating the $a_j$. In this paper we compare with the
 Distribution Derivative Method (DDM) only, without loss of generality.
@@
 We examine how this mixture model influences the estimation of the $a_{i,j}$.
-Consider a mixture of $P$ components
+Consider a mixture of $P$ components.
 If we define the weighted signal sum
@@
 \right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
-is small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
+are small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
 can simply estimate the parameters $a_{i^{\ast},j}$ using
@@
 %
-i.e., the definition of the DFT.%
+i.e., the definition of the DFT of a windowed signal.
 \footnote{%
@@
 filter design problem under the constraints that the impulse response of the
-filter must be differentiable in $t$ and finite. To minimize the influence of
+filter be differentiable in $t$ and finite. To minimize the influence of
 all but one component, granted the components's energy concentrations are
-sufficiently separated in frequency, we desire impulse responses with maximum
+sufficiently separated in frequency, we desire impulse responses whose magnitude
+response gives maximum
 out-of-band rejection or equivalently, windows whose Fourier transform exhibits
-lower side-lobes.
+the lowest side-lobes.
 
 In all the publications these authors reviewed on the DDM, the window used was
-the Hann window.
-Nuttall has designed windows with lower
-side-lobes than the canonical Hann window which are still differentiable.
+the Hann window which is once-differentiable everywhere in the time-domain.
+Nuttall has designed windows with lower side-lobes than the canonical Hann
+window which are everywhere at least once-differentiable. It is also possible to
+design approximations to aribtrary symmetrical window functions using
+harmonically related cosines, as is discussed in the following section.
+
+\section{Differentiable approximations to windows}
+
+An differentiable approximation to a symmetrical window can be designed in a
+straight-forward way. (Harris) and (McGonnegal) have shown how to design optimal
+windows of length $N$ samples using a linear combination of $M$ harmonically
+related cosines
+\begin{equation}
+    w(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
+\mathcal{R}(\frac{n}{N})
+\end{equation}
+where $\mathcal{R}$ is the \textit{rectangle function}. This function is discontinous
+at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
+\[
+\sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
+\]
+
+We choose the $b_{k}$ so that the window $w$'s squared approximation error to
+$v$ is minimized
+while having $w(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{
+b^{\ast}_{k} \}$ to the mathematical program
+\begin{equation}
+    \text{minimize}
+    \sum_{n=0}^{N-1} ( v(n) 
+        - \sum_{k=0}^{M-1} b_{k} \cos(2 \pi k \frac{n}{N}))^{2}
+\end{equation}
+\[
+    \text{subject to} \\
+    \sum_{k=0}^{M-1} b_{k} \cos(\pi k ) = 0
+\]
+which can be solved using standard numerical linear algebra routines (Goulob and
+Van Loan p 585).
+
+\section{Approximating digital prolate spheroidal windows}
+
+Digital prolate spheroidal windows are a parametric approximation to functions
+proposed by Slepian et al. maximimzing the energy in a given bandwidth. These can be
+tuned to have extremely low side-lobes, at the expense of main-lobe width.
+Differentiation of these window functions may be possible but is not as
+straightforward as differentiation of the sum-of-cosine windows. Furthermore,
+the windows do not generally have end-points equal to 0. In the following we
+will demonstrate how to approximate one of these windows.
+
+(Verna, Bilbao et al.) showed how to construct prolate spheroidal windows under
+parmeters $N$, the window length in samples, and $W$. We chose $N$ based on the
+window length chosen in (Betser) for ease of comparison. $W^{\ast}$ was chosen
+by synthesizing windows with $W$ ranging between $0.01$ and $0.99$ at a resolution
+of $0.01$. The window with the lowest height of the highest sidelobe was obtained
+with $W=0.77$. It is shown in (figure). 
+mainlobe width.
+
+The approximation method yields a window virtually identical to the digital
+prolate spheroidal window: in our realisation, the approximation error was
+everywhere less than $10^{-13}$.
+
+% TODO: Plot these windows
 

### 2017-02-28 approx_psw_cosines.py

@@ -4,7 +4,10 @@ import numpy as np
 import matplotlib.pyplot as plt
 import cvxopt
 
-show_plot=False
+plt.rc('text',usetex=True)
+plt.rc('font',family='serif')
+
+show_plot=True
 
 # Window length
 N=512
@@ -57,15 +60,17 @@ w=ddm.w_dw_sum_cos(N,a)[0]
 N_F=N*os
 v_F=np.fft.fft(v,N_F)
 w_F=np.fft.fft(np.concatenate((w.reshape((1,N)),w[0].reshape((1,1))),axis=1),N_F).flatten()
-v_F=20*np.log10(np.abs(v_F))
-w_F=20*np.log10(np.abs(w_F))
+v_F_a=np.abs(v_F)
+w_F_a=np.abs(w_F)
+v_F=20*np.log10(v_F_a)
+w_F=20*np.log10(w_F_a)
 v_F-=np.max(v_F)
 w_F-=np.max(w_F)
 v_F=np.concatenate((v_F[N_F:],v_F[:N_F]))
 w_F=np.concatenate((w_F[N_F:],w_F[:N_F]))
 bins_F=np.arange(0,N,1./os)
 
-fig1,axs=plt.subplots(2,2)
+fig1,axs=plt.subplots(3,2)
 axs[0,0].plot(bins_F,v_F)
 axs[0,0].set_title('prolate spheroidal window, magnitude spectrum')
 axs[1,0].plot(bins_F,w_F)
@@ -76,6 +81,23 @@ axs[0,1].set_title('prolate spheroidal window, time-domain')
 axs[1,1].plot(n,w)
 axs[1,1].set_title('sum-of-cosine approx. window, time-domain')
 
+axs[2,0].plot(bins_F,20*np.log10(np.abs(v_F_a-w_F_a)))
+axs[2,0].set_title('log approximation error, magnitude spectrum')
+axs[2,1].plot(n,np.log10(np.abs(v[:-1]-w)))
+axs[2,1].set_title('log approximation error, time-domain')
+
+fig2,axs2=plt.subplots(2,1,num=2)
+axs2[0].plot(n,w)
+axs2[0].set_title('Sum-of-cosine approximation, time-domain')
+axs2[0].set_xlabel('Sample number')
+axs2[0].set_ylabel('Amplitude')
+axs2[1].plot(n,np.log10(np.abs(v[:-1]-w)))
+axs2[1].set_title('Approximation error, time-domain')
[…]

### 2017-02-28 synth_min_digital_prolate_window.py

@@ -4,6 +4,9 @@ import ddm
 import matplotlib.pyplot as plt
 import sigmod as sm
 
+plt.rc('text',usetex=True)
+plt.rc('font',family='serif')
+
 # Length of window
 N=513
 # Length of DFT (controls zero-padding)

### 2017-03-05 approx_psw_cosines.py
Improved plotting, added prolate window with narrower main lobe
Added function to compute precise 3dB bandwidth of windows using Newton's
method.

Can find windows close to a specified window using constrained
least-squares (keeps them continuous at the end points).

Should be able to compute CRLB (not tested).

@@ -99,5 +99,8 @@ axs2[1].set_ylabel('$\log_{10}$ absolute error')
 for ax_ in axs2:
     ax_.set_xlim([0,N])
 
+print 'prolate endpoint: %g' % (v[0],)
+print 'approx endpoint: %g' % (w[0],)
+
 if (show_plot):
     plt.show()

### 2017-03-05 bw_bins_test.py

@@ -1,0 +1,13 @@
+import numpy as np
+import numpy.linalg
+import ddm
+import matplotlib.pyplot as plt
+import sigmod as sm
+
+N=512
+
+w=ddm.w_dw_sum_cos(512,a='hanning')[0]
+
+k_opt=ddm.bw_bins(w,k_hint=1.)
+
+print '3db bandwidth: %g' % (k_opt * 2.,)

### 2017-03-05 comp_offset_chirp_est_err.py

@@ -21,7 +21,7 @@ chirps=ddm.build_offset_chirps(N_chirps=4,
                                W_l_ms=W_l_ms,
                                b1_r=[0.,np.pi*F_s])
 
-wins=['hann','c1-nuttall-4','c1-blackman-4','prolate-0.77-approx-47']
+wins=['hann','c1-nuttall-4','c1-blackman-4','prolate-0.008-approx-5']
 line_stys=['solid','dotted','dashed','dashdot']
 sr_min=-30
 srs=np.arange(sr_min,0,10)

### 2017-03-05 ddm.py

@@ -3,6 +3,14 @@
 import numpy as np
 import numpy.linalg as LA
 import matplotlib.pyplot as plt
+import scipy.optimize as spopt
+import cvxopt
+
+FONT_OPT=dict()
+FONT_OPT['dafx']={
+        'family':'serif',
+        'sans-serif':'Times'
+}
 
 def eig_pow_method(A,d=1.e-6,maxiters=1000):
     """
@@ -62,6 +70,12 @@ def w_dw_sum_cos(M,a='hanning',norm=False):
             c=np.r_[0.54,0.46]
         elif (a=='naive-min-blackman-4'):
             c=np.r_[0.35875,0.48829,0.14128,0.01168]
+        elif (a=='prolate-0.008-approx-5'):
+            c=np.r_[3.128258203861262743e-01,
+                    4.655346501582137142e-01,
+                    1.851027605614040672e-01,
+                    3.446534984178639682e-02,
+                    2.071419052469766937e-03]
         elif (a=='prolate-0.77-approx-47'):
             # Does the number of figures contribute significantly to the
             # accuracy?
@@ -481,4 +495,108 @@ def psw_design(N,W):
     (L,V)=np.linalg.eig(A)
     v=V[:,np.argmax(np.abs(L))]
     return v
+
+def bw_bins(w,A_bw=10.**(-3./20.),k_hint=0,k_max=0):
+    """
+    Find the bin closest to k_hint that has ampltiude A_bw.
+    This is useful for finding the 3db bandwidth of windows.
+    Note that this amplitude is normalized by the DTFT at the maximum bin
+    (k_max).
+
+    Arguments:
+        
+        w:
+            the window whose DTFT will be used to find the bin.
+        A_bw:
+            the amplitude of the desired bin.
+        k_hint:
+            the bin from which the search will start, can be float.
+        k_max:
+            the bin where the DTFT will be maximum, can be float.
+
+    Returns:
+        k, the bin whose amplitude is closest to A_bw.
+    """
+    # Fourier transform at maxmimum bin
+    N=len(w)
+    n=np.arange(N)
+    W_0=np.inner(w,np.exp(-2.*np.pi*1j*n*float(k_max)/N))
+    def _f(x):
+        result = np.inner(w,np.exp(-2.*np.pi*1j*n*x/float(N)))/W_0 
+        result = result * np.conj(result)
[…]

### 2017-03-05 ddm_snr_win_comp.py

@@ -33,21 +33,22 @@ ph3_r=[-1.e6,1.e6]
 # Number of evaluations to perform
 N_eval=100
 
-
 # SNRs to test
 snrs=np.arange(-2,20)*(10.)
 
 # Errors
 errs=dict()
-keys=['hann','c1-nuttall-4','c1-nuttall-3','c1-blackman-4','prolate-0.77-approx-47']
-key_clrs=['b','g','r','m','c']
-for k,c in zip(keys,key_clrs):
+keys=['hann','c1-nuttall-4','c1-nuttall-3','prolate-0.008-approx-5']
+key_clrs=['k' for _ in xrange(4)]
+key_ls=['solid','dotted','dashed','dashdot']
+for k,c,ls in zip(keys,key_clrs,key_ls):
     errs[k]=dict()
     # Amplitude part
     errs[k]['a']=[[],[],[]]
     # Phase part
     errs[k]['ph']=[[],[],[]]
-    errs[k]['clr']=c
+    # Plotting descriptors
+    errs[k]['plot_dict']={'c':c,'ls':ls}
 
 for k in errs.keys():
 
@@ -146,10 +147,10 @@ fig, axarr = plt.subplots(3,2)
 
 for k in errs.keys():
     for i,pl in zip(xrange(len(errs[k]['a'])),axarr[:,0]):
-        pl.plot(snrs,np.log10(errs[k]['a'][i]),c=errs[k]['clr'],label=k)
+        pl.plot(snrs,np.log10(errs[k]['a'][i]),label=k,**errs[k]['plot_dict'])
         pl.set_title('a_%d' % (i,))
     for i,pl in zip(xrange(len(errs[k]['ph'])),axarr[:,1]):
-        pl.plot(snrs,np.log10(errs[k]['ph'][i]),c=errs[k]['clr'],label=k)
+        pl.plot(snrs,np.log10(errs[k]['ph'][i]),label=k,**errs[k]['plot_dict'])
         pl.set_title('ph_%d' % (i,))
 
 axarr[0,0].legend(fontsize=10)

### 2017-03-05 search_dpw_bw.py

@@ -1,0 +1,101 @@
+import numpy as np
+import numpy.linalg
+import ddm
+import matplotlib.pyplot as plt
+import sigmod as sm
+
+# Length of window
+N=513
+# Length of DFT (controls zero-padding)
+N_F=1024
+#n_F=np.arange(N_F)
+#N=513
+# Design coefficients
+# This range found empirically to give peak side-lobes close to desired one
+W=np.arange(0.005,0.011,0.001)
+#W=np.array([0.009])
+#W=np.array([0.009])
+# Ratio of max to peak sidelobe (dB)
+a=np.zeros(len(W))
+# The 3db-bandwidth desired
+bw_des=2.
+#bw_des=1.91
+#W=.8
+i=np.arange(N,dtype='double')
+# Number of cosines to use in approximation
+M_w=N/8
+# Constraints to use when approximating (just continuous)
+c_w={'c1'}
+
+w_close=None
+bw_diff_close=100.
+v_close=None
+v_F_close=None
+for n,W_ in enumerate(W):
+    #A=np.diag(np.cos(2*np.pi*W_)*(((N-1.)/2.-i)**2.))
+    #A+=np.diag(0.5*i[1:]*(N-i[1:]),-1)
+    #A+=np.diag(0.5*i[1:]*(N-i[1:]),1)
+    ##(l,v)=ddm.eig_pow_method(A)
+    #(L,V)=np.linalg.eig(A)
+    #v=V[:,np.argmax(np.abs(L))]
+    v=ddm.psw_design(N,W_)
+    # Remove endpoint because it should be the same as the first point
+    v=v[:-1]
+    # Make window positive
+    if (np.abs(np.min(v)) > np.abs(np.max(v))):
+        v *= -1.
+    # Make window maximum equal to 1
+    v/=np.max(v)
+    try:
+        k_opt=ddm.bw_bins(v,k_hint=bw_des/2.)
+    except RuntimeError:
+        a[n]=None
+        continue
+    bw_diff=np.abs(2.*k_opt-bw_des)
+    #(ma,mai)=sm.lextrem(v_F)
+    #ma_srt=np.sort(ma.flatten())
+    #a[n]=ma_srt[-1]-ma_srt[-2]
+    #a_diff=np.abs(a_des-a[n])
+    a[n]=np.abs(k_opt*2.)
[…]

### 2017-03-05 search_dpw_bw_m.py

@@ -1,0 +1,175 @@
+import numpy as np
+import numpy.linalg
+import ddm
+import matplotlib.pyplot as plt
+import sigmod as sm
+
+plt.rc('text',usetex=True)
+plt.rc('font',**ddm.FONT_OPT['dafx'])
+
+# Search for number of cosines that best approximate window
+
+# Length of window
+N=513
+# Length of DFT (controls zero-padding)
+N_F=1024
+#n_F=np.arange(N_F)
+#N=513
+# Design coefficients
+# This range found empirically to give peak side-lobes close to desired one
+W=np.arange(0.005,0.011,0.001)
+#W=np.array([0.009])
+#W=np.array([0.009])
+# Ratio of max to peak sidelobe (dB)
+a=np.zeros(len(W))
+# The 3db-bandwidth desired
+#bw_des=2.
+bw_des=1.91
+#W=.8
+i=np.arange(N,dtype='double')
+# Number of cosines to use in approximation
+M_w=np.arange(2,50)
+# Constraints to use when approximating (just continuous)
+c_w={'c1'}
+
+w_close=None
+bw_diff_close=100.
+v_close=None
+v_F_close=None
+for n,W_ in enumerate(W):
+    v=ddm.psw_design(N,W_)
+    # Remove endpoint because it should be the same as the first point
+    v=v[:-1]
+    # Make window positive
+    if (np.abs(np.min(v)) > np.abs(np.max(v))):
+        v *= -1.
+    # Make window maximum equal to 1
+    v/=np.max(v)
+    try:
+        k_opt=ddm.bw_bins(v,k_hint=bw_des/2.)
+    except RuntimeError:
+        a[n]=None
+        continue
+    bw_diff=np.abs(2.*k_opt-bw_des)
+    #(ma,mai)=sm.lextrem(v_F)
+    #ma_srt=np.sort(ma.flatten())
+    #a[n]=ma_srt[-1]-ma_srt[-2]
+    #a_diff=np.abs(a_des-a[n])
+    a[n]=np.abs(k_opt*2.)
+    if (bw_diff < bw_diff_close):
+        bw_diff_close=bw_diff
+        w_close=W_
+        v_close=v
[…]

### 2017-03-05 ddm.py
Added CRLB to plots
Improved plot arrangement.

@@ -595,8 +595,8 @@ def crlb_pq(a,t,sig2):
     F=np.zeros((q,q),dtype='float')
     for i in xrange(q):
         for j in xrange(q):
-            F[i,j]=2./sig2 * np.sum(np.pow(t,i+j) *
-                    exp(2*np.polyval(a[::-1],t)))
+            F[i,j]=2./sig2 * np.sum(np.power(t,i+j) *
+                    np.exp(2*np.polyval(a[::-1],t)))
     # Return diagonal of inverse
     return np.diag(np.linalg.inv(F))
 

### 2017-03-05 ddm_snr_win_comp.py

@@ -7,6 +7,9 @@ import ddm
 import numpy as np
 import matplotlib.pyplot as plt
 
+plt.rc('text',usetex=True)
+plt.rc('font',**ddm.FONT_OPT['dafx'])
+
 # Sample rate (Hz)
 F_s=16000
 # Window length (ms)
@@ -34,39 +37,49 @@ ph3_r=[-1.e6,1.e6]
 N_eval=100
 
 # SNRs to test
-snrs=np.arange(-2,20)*(10.)
+snrs=np.arange(-2,17)*(10.)
 
 # Errors
 errs=dict()
-keys=['hann','c1-nuttall-4','c1-nuttall-3','prolate-0.008-approx-5']
-key_clrs=['k' for _ in xrange(4)]
-key_ls=['solid','dotted','dashed','dashdot']
-for k,c,ls in zip(keys,key_clrs,key_ls):
+keys=['crlb','hann','c1-nuttall-4','c1-nuttall-3','prolate-0.008-approx-5']
+key_clrs=['grey']+['k' for _ in xrange(4)]
+key_ls=['solid','solid','dotted','dashed','dashdot']
+key_labels=['C','H','N4','N3','P5']
+for k,c,ls,lab in zip(keys,key_clrs,key_ls,key_labels):
     errs[k]=dict()
     # Amplitude part
     errs[k]['a']=[[],[],[]]
     # Phase part
     errs[k]['ph']=[[],[],[]]
     # Plotting descriptors
-    errs[k]['plot_dict']={'c':c,'ls':ls}
+    errs[k]['plot_dict']={'c':c,'ls':ls,'label':lab}
 
 for k in errs.keys():
 
     # Analysis window, and derivative
-    w,dw=ddm.w_dw_sum_cos(W_l,k,norm=False)
+    if k != 'crlb':
+        w,dw=ddm.w_dw_sum_cos(W_l,k,norm=False)
     
     for snr in snrs:
         
         # Amplitude part
-        a0_err=0.
-        a1_err=0.
-        a2_err=0.
-        a3_err=0.
+        # mean aggregate
+        a0_err_mean_ag=0
+        a1_err_mean_ag=0
+        a2_err_mean_ag=0
+        # 2nd moment aggregate (to compute variance at the end)
+        a0_err_2mom_ag=0
+        a1_err_2mom_ag=0
+        a2_err_2mom_ag=0
         # Phase part
-        ph0_err=0.
-        ph1_err=0.
[…]

### 2017-03-06 comp_offset_chirp_est_err.py
Improved estimation error comparison plots for 2 components.

@@ -7,6 +7,9 @@ from matplotlib import cm
 
 import warnings
 
+plt.rc('text',usetex=True)
+plt.rc('font',**ddm.FONT_OPT['dafx'])
+
 #warnings.simplefilter('error','RuntimeWarning')
 
 F_s=16000
@@ -21,11 +24,12 @@ chirps=ddm.build_offset_chirps(N_chirps=4,
                                W_l_ms=W_l_ms,
                                b1_r=[0.,np.pi*F_s])
 
-wins=['hann','c1-nuttall-4','c1-blackman-4','prolate-0.008-approx-5']
+wins=['hann','c1-nuttall-4','c1-nuttall-3','prolate-0.008-approx-5']
 line_stys=['solid','dotted','dashed','dashdot']
-sr_min=-30
-srs=np.arange(sr_min,0,10)
-n_diffs=64
+labels=['H','C4','C4','P5']
+sr_min=-60
+srs=np.arange(sr_min,10,20)
+n_diffs=40
 diffs=xrange(n_diffs)
 errs=dict()
 for w in wins:
@@ -35,7 +39,7 @@ for w in wins:
         errs[w][s]['diffs']=[0 for _ in diffs]
         errs[w][s]['diffs_log']=[0 for _ in diffs]
 
-cmap=plt.get_cmap('gnuplot')
+cmap=plt.get_cmap('Greys')
 
 # Chirp creator
 cp2c=ddm.chirp_p2_creator(W_l_ms,F_s)
@@ -83,14 +87,25 @@ for w in wins:
 
 fig=plt.figure(1)
 
-for w,ls in zip(wins,line_stys):
+diffs_min=1000.
+diffs_max=-1000.
+for w,ls,lab in zip(wins,line_stys,labels):
     for s in srs:
-        clr=cmap(s/float(sr_min))
+        clr=cmap((-1.*s+20.)/(-1.*float(sr_min)+20.))
         print errs[w][s]['diffs_log']
         plt.plot(diffs,
-                errs[w][s]['diffs_log'],c=clr,ls=ls)
+                errs[w][s]['diffs_log'],c=clr,ls=ls,label=lab + ' %d dB' % (s,))
+        if np.max(errs[w][s]['diffs_log']) > diffs_max:
+            diffs_max = np.max(errs[w][s]['diffs_log'])
+        if np.min(errs[w][s]['diffs_log']) < diffs_min:
+            diffs_min = np.min(errs[w][s]['diffs_log'])
 
[…]

### 2017-03-08 paper/paper.tex
Added CRLB to plots
Improved plot arrangement.
Added figures to paper.

@@
 \ninept
+
+\usepackage{hyphenat}
+\hyphenation{spher-oidal}
 
@@
 \section{The polynomial phase sinusoid}
-Recently techniques estimating the parameters of polynomial phase sinusoids,
+Recently techniques for estimating the parameters of complex polynomial phase sinusoids,
 i.e., signals of the form
-\[
+\begin{equation}
+    \label{eq:polyphaseexp}
     x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j)
-\]
-have been developed. Many equivalent techniques have been developed for
-estimating the $a_j$. In this paper we compare with the
+\end{equation}
+with $a_{i} \in \mathbb{C}$, have been developed. Many equivalent techniques have
+been developed for estimating the $a_j$. In this paper we compare with the
 Distribution Derivative Method (DDM) only, without loss of generality.
@@
 functions'' or atoms $\psi$. These atoms must be once differentiable with respect to
-$t$ and be non-zero only on a finite interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
+time variable $t$ and be non-zero only on a finite interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
 %
@@
 %
-\[
+\begin{equation}
+    \label{eq:polyphaseexpmix}
     s(t) = \sum_{i=1}^{P} x_{i}(t)
-\]
+\end{equation}
 %
@@
 \section{Designing the $\psi_{r}$}
+\label{sec:designingatoms}
 
-In practice, an approximation of \ref{eq:ddm:inner:prod:def} is evaluated using
+In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
 the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
@@
     \left\langle x , \psi_{\omega} \right\rangle \approx 
-    \frac{1}{N} \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
+    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
 \]
 %
-i.e., the definition of the DFT of a windowed signal.
+i.e., the definition of the DFT of a windowed signal.%
 \footnote{%
@@
 The DFT is readily interpreted as a bank of bandpass filters centred at
-normalized frequencies $\frac{r}{N}$ and with frequency response described by
+normalized frequencies%
+\footnote{%
+In this article as in much of the literature on signal processing the index $r$
+of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
+\frac{r}{N}$ will be referred to as its bin number.
+}
+$\frac{r}{N}$ and with frequency response described by
 the Fourier transform of modulated $w$. Therefore choosing $\psi$ amounts to a
@@
 
-An differentiable approximation to a symmetrical window can be designed in a
+A differentiable approximation to a symmetrical window can be designed in a
 straight-forward way. (Harris) and (McGonnegal) have shown how to design optimal
@@
 \end{equation}
-where $\mathcal{R}$ is the \textit{rectangle function}. This function is discontinous
+where $\mathcal{R}$ is the \textit{rectangle function}. This function is
+discontinuous
 at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
@@
 \begin{equation}
+    \label{eq:searchcontwinprogram}
     \text{minimize}
@@
 \]
-which can be solved using standard numerical linear algebra routines (Goulob and
-Van Loan p 585).
+which can be solved using constrained least-squares -- a standard numerical
+linear algebra routine (Goulob and Van Loan p 585).
 
-\section{Approximating digital prolate spheroidal windows}
+\section{Continuous window design example}
+\label{sec:designexample}
+\begin{figure*}[t]
+    \centerline{\includegraphics[width=5in]{{search_dpw_bw_m_fig_mainlobe}.eps}}
+\caption{\label{fig:dpwmainlobe} Comparing the mainlobe characteristics of the
+continuous 4-term Nuttall window, the digital prolate window with $W=0.008$, and
+the continuous approximation to the digital prolate window.}
+\end{figure*}
+
+\begin{figure*}[t]
+    \centerline{\includegraphics[width=5in]{{search_dpw_bw_m_fig_asymptotic}.eps}}
+\caption{\label{fig:dpwasymptotic} Comparing the asymptotic power spectrum
+characteristics of the continuous 4-term Nuttall window, the digital prolate
+window with $W=0.008$, and the continuous approximation to the digital prolate
+window.}
+\end{figure*}
+
+As a design example we show how to create a continuous approximation of a digital
+prolate spheroidal window.
 
 Digital prolate spheroidal windows are a parametric approximation to functions
-proposed by Slepian et al. maximimzing the energy in a given bandwidth. These can be
-tuned to have extremely low side-lobes, at the expense of main-lobe width.
-Differentiation of these window functions may be possible but is not as
-straightforward as differentiation of the sum-of-cosine windows. Furthermore,
-the windows do not generally have end-points equal to 0. In the following we
-will demonstrate how to approximate one of these windows.
+proposed by Slepian et al. whose Fourier transform's energy is maximized in a
+given bandwidth. These can be tuned to have extremely low side-lobes, at the
+expense of main-lobe width.  Differentiation of these window functions may be
+possible but is not as straightforward as differentiation of the sum-of-cosine
+windows above. Furthermore, the windows do not generally have end-points equal to 0.
+In the following we will demonstrate how to approximate a digital prolate
+spheroidal window.
 
 (Verna, Bilbao et al.) showed how to construct prolate spheroidal windows under
-parmeters $N$, the window length in samples, and $W$. We chose $N$ based on the
-window length chosen in (Betser) for ease of comparison. $W^{\ast}$ was chosen
-by synthesizing windows with $W$ ranging between $0.01$ and $0.99$ at a resolution
-of $0.01$. The window with the lowest height of the highest sidelobe was obtained
-with $W=0.77$. It is shown in (figure). 
-mainlobe width.
+parameters $N$, the window length in samples, and $W$. We chose $N=512$ based on
+the window length chosen in (Betser) for ease of comparison. Its parameter value
+was chosen by synthesizing windows with $W$ ranging between $0.005$ and $0.010$
+at a resolution of $0.001$. The window with the closest 3db bandwidth to the
+4-term Nuttall window was obtained with $W=0.008$. Its magnitude response is
+shown in Fig.~\ref{fig:dpwmainlobe}~and~\ref{fig:dpwasymptotic}. We see that
+this window's asymptotic roll-off is 6 dB per octave and is therefore not
+continuous (Nuttall). We designed an approximate window using
+Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and $N/8$ to find
+the best approximation to the digital prolate window's mainlobe using a small
+number of cosines. The $M$ giving the best approximation was $5$. The magnitude
+response of the approximation is shown in Fig.~\ref{fig:dpwmainlobe}.  We see
+that we obtain a lower highest side-lobe level by slightly sarificing the
+narrowness of the mainlobe. Furthermore in Fig.~\ref{fig:dpwasymptotic} we
+observe that the rolloff of the window is 18 dB per octave because it is
+continuous at all points in its domain.
 
-The approximation method yields a window virtually identical to the digital
-prolate spheroidal window: in our realisation, the approximation error was
-everywhere less than $10^{-13}$.
+\section{The performance of improved windows}
+
+\begin{figure*}[ht]
+    \centerline{\includegraphics[width=5in]{{ddm_snr_win_comp}.eps}}
+\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
+phase sinusoids averaged over 1000 trials. \textit{C} is the Cram\'{e}r-Rao
+lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
+Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continous
+5-cosine-term approximation to a digital prolate window as described in
+Sec.~\ref{sec:designexample}.}
+\end{figure*}
+
+As in (Betser) we synthesized random sinusoids using Eq.~\ref{eq:polyphaseexp}
+with $Q=2$ and compared the average estimation error variance with the
+theoretical minimum given by the Cram\'{e}r-Rao bound. The original Hann window,
+the windows proposed by Nuttall and the new digital prolate based window were
+used to synthesize the atoms as described in Sec.~\ref{sec:designingatoms} and
+their their estimation error variance was compared (see
+Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
+with the atoms, three containing the most signal energy were used in the
+estimations. We see that windows with lower-sidelobes exhibit the lowest
+possible error variance at the sacrifice of some estimator efficiency.
+
+\begin{figure*}[ht]
+    \centerline{\includegraphics[width=5in]{{comp_offset_chirp_est_err}.eps}}
+\caption{\label{fig:mixwincomp}}
+\end{figure*}
+
+To evaluate the performance of the various windows when estimating the
+parameters of components in mixture we synthesized signals using
+Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$. One of the two components was
+scaled to give a desired signal power ratio with the other component. The
+parameters of both components were estimated and the total squared estimation
+error for all the parameters was recorded. In Fig.~\ref{fig:mixwincomp} we see
+that there is generally less estimation error for components having similar
+signal power. This is to be expected as the more powerful signal will mask the
+other less in these scenarios. The estimation error is large when the atoms
+containing the most signal energy for each component are not greatly separated
+in frequency. This is likely due to the convolution of the Fourier transform of
+the window with the signal -- indeed windows with a larger mainlobe exhibit a
+larger `radius' in which the error of the parameter estimation will be high.
+However, for atoms sufficiently separated in frequency, windows with lower
+sidelobes are better at attenuating the other component and for these the
+estimation error is lowest.
 

### 2017-03-08 comp_offset_chirp_est_err.py

@@ -17,7 +17,7 @@ W_l_ms=32
 R=3
 # prepare chirps
 
-chirps=ddm.build_offset_chirps(N_chirps=4,
+chirps=ddm.build_offset_chirps(N_chirps=6,
                                # Sample rate (Hz)
                                F_s=F_s,
                                # Window length (ms)
@@ -27,8 +27,8 @@ chirps=ddm.build_offset_chirps(N_chirps=4,
 wins=['hann','c1-nuttall-4','c1-nuttall-3','prolate-0.008-approx-5']
 line_stys=['solid','dotted','dashed','dashdot']
 labels=['H','C4','C4','P5']
-sr_min=-60
-srs=np.arange(sr_min,10,20)
+sr_min=-30
+srs=np.arange(sr_min,10,10)
 n_diffs=40
 diffs=xrange(n_diffs)
 errs=dict()
@@ -107,5 +107,7 @@ plt.xlim([0,n_diffs-1])
 plt.ylim([diffs_min,diffs_max])
 plt.title('Total mean-squared estimation error for two signals at various ' +
     'signal power ratios')
+
+plt.savefig('paper/comp_offset_chirp_est_err.eps')
 
 plt.show()

### 2017-03-08 ddm_snr_win_comp.py

@@ -34,7 +34,7 @@ ph2_r=[-1.e4,1.e4]
 ph3_r=[-1.e6,1.e6]
 
 # Number of evaluations to perform
-N_eval=100
+N_eval=1000
 
 # SNRs to test
 snrs=np.arange(-2,17)*(10.)
@@ -207,7 +207,7 @@ for k in errs.keys():
         pl.set_title('$\Re\{a_%d\}$' % (i,))
         pl.set_ylabel('Error variance ($\log_{10}$)')
         if (i == 2):
-            pl.set_xlabel('SNR')
+            pl.set_xlabel('SNR (dB)')
         pl.set_xlim([snrs[0],snrs[-1]])
         if (np.max(np.log10(errs[k]['a'][i])) > a_maxs[i]):
             a_maxs[i]=np.max(np.log10(errs[k]['a'][i]))
@@ -218,7 +218,7 @@ for k in errs.keys():
         pl.plot(snrs,np.log10(errs[k]['ph'][i]),**errs[k]['plot_dict'])
         pl.set_title('$\Im\{a_%d\}$' % (i,))
         if (i == 2):
-            pl.set_xlabel('SNR')
+            pl.set_xlabel('SNR (dB)')
         pl.set_xlim([snrs[0],snrs[-1]])
         if (np.max(np.log10(errs[k]['ph'][i])) > ph_maxs[i]):
             ph_maxs[i]=np.max(np.log10(errs[k]['ph'][i]))
@@ -233,5 +233,7 @@ for i,pl in zip(xrange(len(errs[k]['ph'])),axarr[:,1]):
 fig.suptitle('Parameter estimation error variance in various SNR')
 
 axarr[0,0].legend(fontsize=10,loc='lower left')
+
+plt.savefig('paper/ddm_snr_win_comp.eps')
 
 plt.show()

### 2017-03-08 search_dpw_bw_m.py

@@ -142,6 +142,7 @@ for pa in plot_args.keys():
 
 fig_titles=['Nuttall, Prolate and its approximation: asymptotic behaviour',
     'Nuttall, Prolate and its approximation: main lobe']
+fig_short_titles=['asymptotic','mainlobe']
 fig_xlims=[[0,(N-1)/2],[0,(N-1)/16]]
 fig_ylims=[[-250,0],[-160,0]]
 fig_xlabels=['Bin number' for _ in xrange(n_figs)]
@@ -163,6 +164,8 @@ for fignum in xrange(n_figs):
     axs[fignum].legend(handles=[leg_nuttall,leg_prolate,leg_aprx])
     axs[fignum].set_xlabel(fig_xlabels[fignum])
     axs[fignum].set_ylabel(fig_ylabels[fignum])
+    figs[fignum].savefig('search_dpw_bw_m-fig_%s.eps' %
+            (fig_short_titles[fignum],))
 
 print "w_nuttall end point: %g" % (w_nuttall[0],)
 

### 2017-03-09 paper/paper.tex
Improved plots, paper. Still not done ugh

@@
 \label{sec:intro}
-%Additive synthesis using a sum of sinusoids plus noise is a powerful model for
-%representing audio, allowing for the easy implementation of many manipulations
-%such as time-stretching and transposition. In its most basic form, peaks in the
-%short-time spectrum are identified as representing sinusoids and connected based
-%on some criteria. As the phase evolution of the sinusoid is assumed linear over
-%the analysis frame, only the phase and frequency of the sinusoids at these
-%analysis points are used to fit a plausible phase function. Recently, there has
-%been interest in using higher order phase functions as the estimation of their
-%parameters has been made possible by a new set of techniques of only moderate
-%computational complexity using signal derivatives. Theoretically, the estimation
-%of the parameters of a polynomial phase function of arbitrary order make it
-%possible to approximate any analytical phase function to desired precision.
-%Empirically, the use of higher order phase models allow for higher quality
-%manipulations.
+Additive synthesis using a sum of sinusoids plus noise is a powerful model for
+representing audio (Xerra, McAulay), allowing for the easy implementation of
+many manipulations such as time-stretching and transposition (Haken-Fitz,
+Marchand enhanced time-stretching).
+In its most basic form, peaks in the
+short-time spectrum are identified as representing sinusoids and connected based
+on some criteria. As the phase evolution of the sinusoid is assumed linear over
+the analysis frame, only the phase and frequency of the sinusoids at these
+analysis points are used to fit a plausible phase function. Recently, there has
+been interest in using higher order phase functions \cite{xuepiecewise} as the estimation of
+their parameters has been made possible by a new set of techniques of only
+moderate computational complexity using signal derivatives \cite{hamilton2011non}.  The use
+of higher-order phase models allows for higher quality representations, for
+example in the analysis of birdsong \cite{stowell2013improved} or the
+regularization of mathematical programs for audio source separation \cite{creager2016musicalsource}.
+The original techniques estimating the parameters of higher-order phase models
+considered signals containing only one component, although the technique
+has been applied to mixtures of components. In addition to proposing improved
+analysis techniques, the performance of the techniques on mixtures of signals is
+evaluated.
+
+%Theoretically, the estimation of the parameters of a polynomial
+%phase function of arbitrary order make it possible to approximate any analytical
+%phase function to desired precision.
 %
@@
 i.e., signals of the form
+%
 \begin{equation}
@@
 \end{equation}
-with $a_{i} \in \mathbb{C}$, have been developed. Many equivalent techniques have
-been developed for estimating the $a_j$. In this paper we compare with the
-Distribution Derivative Method (DDM) only, without loss of generality.
+%
+with $a_{j} \in \mathbb{C}$, have been developed. Many techniques
+utilizing derivatives of the signal or the analysis window have
+been developed for estimating the $a_j$. The theoretical equivalence of these
+techniques is described in \cite{hamilton2011non}. This paper focuses on the
+Distribution Derivative Method (DDM) only \cite{betser2009sinusoidal}, as it only requires a once-differentiable
+analysis window and no signal derivatives, which is convenient for signal
+processing applications.
+
+In \cite{hamilton2012comparisons} the accuracy
+of the DDM in estimating each $a_{j}$ is evaluated for $Q=1$ with the constraint
+that $\Re{a_1}=0$ and for $2 \leq Q \leq 3$ with the Hann window used to form
+the test functions. In (Roebel) twice-differentiated windows are used to
+estimate the frequency slopes of chirp signals. Results on the accuracy of
+estimation for signals made of a mixture of chirps are given for the frequency
+slope ($\Im{a_2}$) only, but a variety of windows are compared.
+
+In this paper, we evaluate the performance of various once-differentiable
+windows in estimating the $a_{j}$. We are interested in windows with lower
+sidelobes in order to better estimate parameters of sinusoidal chirp signals in
+mixture. A technique to design once-differentiable approximations to aribitrary
+symmetrical windows is presented along with a design example for a
+high-performance window.
 
@@
 We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
-the theory of distributions (Laurent Schwartz), the DDM
+the theory of distributions \cite{schwartz1959theorie}, the DDM
 makes use of ``test
-functions'' or atoms $\psi$. These atoms must be once differentiable with respect to
-time variable $t$ and be non-zero only on a finite interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
+functions'' or atoms $\psi$. These atoms must be once differentiable with
+respect to time variable $t$ and be non-zero only on a finite interval
+$[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
 %
@@
     \left\langle \mathcal{T}^{j-1} x , \overline{\psi}_{r} \right\rangle
-    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
+    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dt} \right\rangle
 \end{equation}
 for $1 \leq r \leq R$.
+
+To estimate $a_0$ we write the signal we are analysing as
+\[
+    x(t) = \exp(a_0) \gamma(t) + \eta (t)
+\]
+where $\eta (t)$ is the error signal, the part of the signal that is not explained
+by our model, and $\gamma (t)$ is the part of the signal
+whose coefficients have already been estimated
+\[
+    \gamma(t) = \exp \left( \sum_{j=1}^{Q} a_j t^{j} \right)
+\]
+Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
+\[
+    \left\langle x , \gamma \right\rangle
+    =
+    \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
+        \left\langle \eta , \gamma \right\rangle
+\]
+The inner-product between $\eta$ and $\gamma$ is $0$, by the orthogonality
+principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
+depend on $t$, we have
+\[
+    \left\langle x , \gamma \right\rangle
+    =
+    \exp(a_0) \left\langle \gamma , \gamma \right\rangle
+\]
+so we can estimate $a_0$ as
+\begin{equation}
+    \label{eq:ddmesta0}
+    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
+        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
+\end{equation}
 
@@
 sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
-interest to consider a signals featuring a sum of $P$ such components, i.e.,
+interest to consider signals featuring a sum of $P$ such components, i.e.,
 %
@@
 %
-and substitute $g$ for $f$ in \ref{eq:ddm:weighted:sig:derivative} we obtain
+and substitute $g$ for $f$ in Eq.~\ref{eq:ddm:weighted:sig:derivative} we obtain
 %
 \begin{multline}
+    \label{eq:mixest}
     \sum_{i=1}{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
@@
 \[
-    \sum_{j=1}^{Q} j a_{i,j} 
-    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r} \right\rangle
-    = -\left\langle x_i, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
+    \sum_{j=1}^{Q} j a_{{i^{\ast}},j} 
+    \left\langle \mathcal{T}^{j-1} x_{i^{\ast}} , \overline{\psi}_{r} \right\rangle
+    = -\left\langle x_{i^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
 \]
-for $1 \leq r \leq R$.
+for $1 \leq r \leq R$. To compute $a_{i^{\ast},0}$ we simply use
+\[
+    \gamma_{i^{\ast}}(t) = \exp \left( \sum_{j=1}^{Q} a_{i^{\ast},j} t^{j} \right)
+\]
+in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.
 
@@
 out-of-band rejection or equivalently, windows whose Fourier transform exhibits
-the lowest side-lobes.
+the lowest sidelobes.
 
@@
 the Hann window which is once-differentiable everywhere in the time-domain.
-Nuttall has designed windows with lower side-lobes than the canonical Hann
+Nuttall \cite{nuttall1981some} has designed windows with lower sidelobes than the canonical Hann
 window which are everywhere at least once-differentiable. It is also possible to
@@
 A differentiable approximation to a symmetrical window can be designed in a
-straight-forward way. (Harris) and (McGonnegal) have shown how to design optimal
-windows of length $N$ samples using a linear combination of $M$ harmonically
-related cosines
+straight-forward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
+is shown how to design optimal windows of length $N$ samples using a linear
+combination of $M$ harmonically related cosines
 \begin{equation}
@@
 which can be solved using constrained least-squares -- a standard numerical
-linear algebra routine (Goulob and Van Loan p 585).
+linear algebra routine \cite[p.~585]{golub1996matrix}.
 
@@
 \begin{figure*}[t]
-    \centerline{\includegraphics[width=5in]{{search_dpw_bw_m_fig_mainlobe}.eps}}
-\caption{\label{fig:dpwmainlobe} Comparing the mainlobe characteristics of the
-continuous 4-term Nuttall window, the digital prolate window with $W=0.008$, and
-the continuous approximation to the digital prolate window.}
-\end{figure*}
-
-\begin{figure*}[t]
-    \centerline{\includegraphics[width=5in]{{search_dpw_bw_m_fig_asymptotic}.eps}}
-\caption{\label{fig:dpwasymptotic} Comparing the asymptotic power spectrum
-characteristics of the continuous 4-term Nuttall window, the digital prolate
-window with $W=0.008$, and the continuous approximation to the digital prolate
-window.}
+    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
+\caption{\label{fig:dpwmainlobe} Comparing the main-lobe and asymptotic power
+spectrum characteristics of the continuous 4-term Nuttall window, the digital
+prolate window with $W=0.008$, and the continuous approximation to the digital
+prolate window.}
 \end{figure*}
@@
 Digital prolate spheroidal windows are a parametric approximation to functions
-proposed by Slepian et al. whose Fourier transform's energy is maximized in a
-given bandwidth. These can be tuned to have extremely low side-lobes, at the
-expense of main-lobe width.  Differentiation of these window functions may be
-possible but is not as straightforward as differentiation of the sum-of-cosine
-windows above. Furthermore, the windows do not generally have end-points equal to 0.
-In the following we will demonstrate how to approximate a digital prolate
-spheroidal window.
+proposed by whose Fourier transform's energy is maximized in a given bandwidth
+\cite{slepian1978prolate}. These can be tuned to have extremely low sidelobes,
+at the expense of main-lobe width.  Differentiation of these window functions
+may be possible but is not as straightforward as differentiation of the
+sum-of-cosine windows above. Furthermore, the windows do not generally have
+end-points equal to 0. In the following we will demonstrate how to approximate
+a digital prolate spheroidal window with one that is everywhere at least
+once-differentiable.
 
-(Verna, Bilbao et al.) showed how to construct prolate spheroidal windows under
-parameters $N$, the window length in samples, and $W$. We chose $N=512$ based on
-the window length chosen in (Betser) for ease of comparison. Its parameter value
+In \cite{verma1996digital} it was shown how to construct digital prolate
+spheroidal windows under parameters $N$, the window length in samples, and a
+parameter $W$. We chose $N=512$ based on the window length chosen in
+\cite{betser2009sinusoidal} for ease of comparison. Its $W$ parameter's value
 was chosen by synthesizing windows with $W$ ranging between $0.005$ and $0.010$
@@
 shown in Fig.~\ref{fig:dpwmainlobe}~and~\ref{fig:dpwasymptotic}. We see that
-this window's asymptotic roll-off is 6 dB per octave and is therefore not
-continuous (Nuttall). We designed an approximate window using
-Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and $N/8$ to find
-the best approximation to the digital prolate window's mainlobe using a small
-number of cosines. The $M$ giving the best approximation was $5$. The magnitude
-response of the approximation is shown in Fig.~\ref{fig:dpwmainlobe}.  We see
-that we obtain a lower highest side-lobe level by slightly sarificing the
-narrowness of the mainlobe. Furthermore in Fig.~\ref{fig:dpwasymptotic} we
-observe that the rolloff of the window is 18 dB per octave because it is
-continuous at all points in its domain.
+this window's asymptotic roll-off is 6 dB per octave and is therefore has a
+discontinuity somewhere in its domain \cite{nuttall1981some}. We designed an approximate
+window using Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and
+$N/8$ to find the best approximation to the digital prolate window's main lobe
+using a small number of cosines. The $M$ giving the best approximation was $5$.
+The magnitude response of the approximation is shown in
+Fig.~\ref{fig:dpwmainlobe}.  We see that we obtain a lower highest sidelobe
+level than the Nuttall and Prolate windows by slightly sarificing the narrowness
+of the main lobe. Furthermore in Fig.~\ref{fig:dpwasymptotic} we observe that
+the rolloff of the window is 18 dB per octave because it is once-differentiable
+at all points in its domain.
 
@@
 
-As in (Betser) we synthesized random sinusoids using Eq.~\ref{eq:polyphaseexp}
+As in \cite{betser2009sinusoidal} we synthesized random sinusoids using Eq.~\ref{eq:polyphaseexp}
 with $Q=2$ and compared the average estimation error variance with the
@@
 Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
-with the atoms, three containing the most signal energy were used in the
-estimations. We see that windows with lower-sidelobes exhibit the lowest
-possible error variance at the sacrifice of some estimator efficiency.
+with the atoms, the three atoms whose inner products were greatest were used in
+the estimations, i.e., $R=3$ in Eq.~\ref{eq:ddmsyseq}. We see that windows with
+lower sidelobes exhibit the lowest possible error variance at the sacrifice of
+some estimator efficiency.
 
@@
 that there is generally less estimation error for components having similar
-signal power. This is to be expected as the more powerful signal will mask the
-other less in these scenarios. The estimation error is large when the atoms
+signal power. This is to be expected as there will be less masking of the weaker
+signal in these scenarios. The estimation error is large when the atoms
 containing the most signal energy for each component are not greatly separated
-in frequency. This is likely due to the convolution of the Fourier transform of
-the window with the signal -- indeed windows with a larger mainlobe exhibit a
+in frequency. This is due to the convolution of the Fourier transform of
+the window with the signal, and agrees with what was predicted by
+Eq.~\ref{eq:mixest}: indeed windows with a larger main lobe exhibit a
 larger `radius' in which the error of the parameter estimation will be high.
-However, for atoms sufficiently separated in frequency, windows with lower
-sidelobes are better at attenuating the other component and for these the
-estimation error is lowest.
-
-% TODO: Plot these windows
+However, for signals with local inner product maxima are with atoms sufficiently
+separated in frequency, windows with lower sidelobes are better at attenuating
+the other component and for these the estimation error is lowest.
 
@@
 %\newpage
-\nocite{*}
+%\nocite{*}
 \bibliographystyle{IEEEbib}
-%\bibliography{paper} % requires file DAFx17_tmpl.bib
+\bibliography{paper} % requires file DAFx17_tmpl.bib
 

### 2017-03-09 comp_offset_chirp_est_err.py

@@ -26,7 +26,7 @@ chirps=ddm.build_offset_chirps(N_chirps=6,
 
 wins=['hann','c1-nuttall-4','c1-nuttall-3','prolate-0.008-approx-5']
 line_stys=['solid','dotted','dashed','dashdot']
-labels=['H','C4','C4','P5']
+labels=['H','C4','C3','P5']
 sr_min=-30
 srs=np.arange(sr_min,10,10)
 n_diffs=40
@@ -94,13 +94,13 @@ for w,ls,lab in zip(wins,line_stys,labels):
         clr=cmap((-1.*s+20.)/(-1.*float(sr_min)+20.))
         print errs[w][s]['diffs_log']
         plt.plot(diffs,
-                errs[w][s]['diffs_log'],c=clr,ls=ls,label=lab + ' %d dB' % (s,))
+                errs[w][s]['diffs_log'],c=clr,ls=ls,label=lab + ' $%d$ dB' % (s,))
         if np.max(errs[w][s]['diffs_log']) > diffs_max:
             diffs_max = np.max(errs[w][s]['diffs_log'])
         if np.min(errs[w][s]['diffs_log']) < diffs_min:
             diffs_min = np.min(errs[w][s]['diffs_log'])
 
-plt.xlabel('Difference of between maxima in bins')
+plt.xlabel('Difference between maxima in bins')
 plt.ylabel('log10 MSE')
 plt.legend(fontsize=10,loc='upper right')
 plt.xlim([0,n_diffs-1])

### 2017-03-09 ddm_snr_win_comp.py

@@ -34,7 +34,7 @@ ph2_r=[-1.e4,1.e4]
 ph3_r=[-1.e6,1.e6]
 
 # Number of evaluations to perform
-N_eval=1000
+N_eval=100
 
 # SNRs to test
 snrs=np.arange(-2,17)*(10.)
@@ -230,7 +230,10 @@ for i,pl in zip(xrange(len(errs[k]['a'])),axarr[:,0]):
 for i,pl in zip(xrange(len(errs[k]['ph'])),axarr[:,1]):
     pl.set_ylim([ph_mins[i],ph_maxs[i]])
 
-fig.suptitle('Parameter estimation error variance in various SNR')
+fig.suptitle(
+    'Parameter estimation error variance in various SNR',
+    # hacky way to get title size
+    fontsize=axarr[0,0].title.get_fontproperties().get_size_in_points())
 
 axarr[0,0].legend(fontsize=10,loc='lower left')
 

### 2017-03-09 search_dpw_bw_m.py

@@ -127,30 +127,31 @@ w_F_nuttall_plt=w_F_nuttall_plt[wFnp_i]
 #ax2.legend(handles=[leg_nuttall,leg_prolate,leg_aprx])
 
 n_figs=2
-figs=[None for _ in xrange(n_figs)]
-axs=[None for _ in xrange(n_figs)]
-plot_funs=['axs[fignum].semilogx','axs[fignum].plot']
+figs,axs=plt.subplots(1,2)
+plot_funs=['axs[fignum].plot','axs[fignum].plot']
 plot_args={
     "Nuttall" : [{'ls':'dotted'} for _ in xrange(n_figs)],
     "Prolate" : [{'ls':'solid'} for _ in xrange(n_figs)],
     "Prolate Approximation" : [{'ls':'dashed'} for _ in xrange(n_figs)]
 }
 for pa in plot_args.keys():
-    plot_args[pa][0]['basex']=2
     for pa_ in plot_args[pa]:
         pa_['c']='k'
 
-fig_titles=['Nuttall, Prolate and its approximation: asymptotic behaviour',
-    'Nuttall, Prolate and its approximation: main lobe']
+fig_titles=['Nuttall, Prolate and its approximation:\n asymptotic behaviour',
+    'Nuttall, Prolate and its approximation:\n main lobe']
 fig_short_titles=['asymptotic','mainlobe']
-fig_xlims=[[0,(N-1)/2],[0,(N-1)/16]]
+fig_xlims=[[(N-1.)/N_F,(N-1)/2],[0,(N-1)/16]]
 fig_ylims=[[-250,0],[-160,0]]
 fig_xlabels=['Bin number' for _ in xrange(n_figs)]
-fig_ylabels=['Power (dB)' for _ in xrange(n_figs)]
-
+fig_ylabels=['Power (dB)','']
+fig_xscales=['log','linear']
+fig_xscales_kwargs=[{'basex':2},{}]
+leg_nuttall =None
+leg_prolate =None
+leg_aprx    =None
 #for fig in figs:
 for fignum in xrange(n_figs):
-    figs[fignum],axs[fignum]=plt.subplots(1,1)
     leg_nuttall,=eval(plot_funs[fignum])(np.arange(N_F)[wFnp_i]/(float(N_F)/(N-1)),
             w_F_nuttall_plt,label="Nuttall",**plot_args["Nuttall"][fignum])
[…]

### 2017-03-11 paper/paper.tex
Improved introduction and overall organization
Put in all references properly.

Working on plotting estimation error for each parameter.

@@
 
+\begin{figure*}[t]
+    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
+\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
+spectrum characteristics of the continuous 4-term Nuttall window, the digital
+prolate window with $W=0.008$, and the continuous approximation to the digital
+prolate window.}
+\end{figure*}
+
+\begin{figure*}[ht]
+    \centerline{\includegraphics[width=5in]{{ddm_snr_win_comp}.eps}}
+\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
+phase sinusoids averaged over 1000 trials. \textit{C} is the Cram\'{e}r-Rao
+lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
+Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continous
+5-cosine-term approximation to a digital prolate window as described in
+Sec.~\ref{sec:designexample}.}
+\end{figure*}
+
+\begin{figure*}[ht]
+    \centerline{\includegraphics[width=5in]{{comp_offset_chirp_est_err}.eps}}
+\caption{\label{fig:mixwincomp}}
+\end{figure*}
+
 \section{Introduction}
@@
 Additive synthesis using a sum of sinusoids plus noise is a powerful model for
-representing audio (Xerra, McAulay), allowing for the easy implementation of
-many manipulations such as time-stretching and transposition (Haken-Fitz,
-Marchand enhanced time-stretching).
-In its most basic form, peaks in the
-short-time spectrum are identified as representing sinusoids and connected based
-on some criteria. As the phase evolution of the sinusoid is assumed linear over
+representing audio \cite{serra1989system}, allowing for the easy implementation
+of many manipulations such as time-stretching \cite{marchand2004enhanced} and
+timbre-morphing \cite{haken2007beyond}.
+%
+Here the phase evolution of the sinusoid is assumed linear over
 the analysis frame, only the phase and frequency of the sinusoids at these
-analysis points are used to fit a plausible phase function. Recently, there has
-been interest in using higher order phase functions \cite{xuepiecewise} as the estimation of
+analysis points are used to fit a plausible phase function after some
+the analysis points are connected to form a partial
+\cite{mcaulay1986speech}. 
+%
+Recently, there has
+been interest in using higher-order phase functions \cite{xuepiecewise} as the estimation of
 their parameters has been made possible by a new set of techniques of only
-moderate computational complexity using signal derivatives \cite{hamilton2011non}.  The use
-of higher-order phase models allows for higher quality representations, for
-example in the analysis of birdsong \cite{stowell2013improved} or the
+moderate computational complexity using signal derivatives \cite{hamilton2011non}.
+%
+The use
+of higher-order phase models allows for accurate description of highly modulated
+signals, for
+example in the analysis of birdsong \cite{stowell2013improved}.
+%
+The frequency
+modulation information has also been used in the
 regularization of mathematical programs for audio source separation \cite{creager2016musicalsource}.
-The original techniques estimating the parameters of higher-order phase models
-considered signals containing only one component, although the technique
-has been applied to mixtures of components. In addition to proposing improved
-analysis techniques, the performance of the techniques on mixtures of signals is
-evaluated.
-
-%Theoretically, the estimation of the parameters of a polynomial
-%phase function of arbitrary order make it possible to approximate any analytical
-%phase function to desired precision.
 %
-%The technique we will consider in this paper is the Distribution Derivative
-%Method for its convenience: the technique does not require computing derivatives
-%of the signal to be analysed. It does, however, require a
-%$p$ times differentiable analysis window where $p+1$ is the order of the
-%phase polynomial to be estimated.
-%
-%In the few reports on the technique, the window used is the Hann window. This
-%window is many-times differentiable but 
-%
-%Complex polynomial phase models whose estimation is 
-\section{The polynomial phase sinusoid}
-Recently techniques for estimating the parameters of complex polynomial phase sinusoids,
-i.e., signals of the form
+The sinusoidal model typically considered is
 %
@@
     \label{eq:polyphaseexp}
-    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j)
+    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j) + \eta(t)
+\end{equation}
+where $\eta(t)$ is white gaussian noise.
+%
+Although this technique can be exteded to describe a single
+sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
+interest to consider signals featuring a sum of $P$ such components, i.e.,
+%
+\begin{equation}
+    \label{eq:polyphaseexpmix}
+    s(t) = \sum_{i=1}^{P} x_{i}(t) + \eta(t)
 \end{equation}
 %
-with $a_{j} \in \mathbb{C}$, have been developed. Many techniques
-utilizing derivatives of the signal or the analysis window have
-been developed for estimating the $a_j$. The theoretical equivalence of these
-techniques is described in \cite{hamilton2011non}. This paper focuses on the
-Distribution Derivative Method (DDM) only \cite{betser2009sinusoidal}, as it only requires a once-differentiable
-analysis window and no signal derivatives, which is convenient for signal
-processing applications.
+with
+%
+\[
+    x_{i}(t) = \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j)
+\]
+%
+In situations where multiple signal sources are known to exist (e.g., recordings
+of multiple speakers or performers) such a model is plausible.
+%
+Previous work on these methods has generally assumed signals containing a single
+component, i.e., $P=1$ or applied the technique assuming the influence of other
+components is negligible. Later we will refine when this assumption can be made.
 
-In \cite{hamilton2012comparisons} the accuracy
-of the DDM in estimating each $a_{j}$ is evaluated for $Q=1$ with the constraint
-that $\Re{a_1}=0$ and for $2 \leq Q \leq 3$ with the Hann window used to form
-the test functions. In (Roebel) twice-differentiated windows are used to
-estimate the frequency slopes of chirp signals. Results on the accuracy of
-estimation for signals made of a mixture of chirps are given for the frequency
-slope ($\Im{a_2}$) only, but a variety of windows are compared.
+\cite{hamilton2012comparisons} gives a comprehensive evaluation of the signal
+derivative methods. In \cite{robel2002estimating} the extent to which two
+components in mixture can corrupt estimations of the frequency slope
+($\Im{a_{0,2}}$ and $\Im{a_{1,2}}$) is investigated in the context of the
+reassignment method, a related technique, but the corruption of the other
+parameters is not considered.
+
+The signal-derivatives technique we will consider is the
+Distribution Derivative Method for its convenience: the technique does not
+require computing derivatives of the signal to be analysed. It does, however, require a
+$p$ times differentiable analysis window where $p+1$ is the order of the
+phase polynomial to be estimated.
 
@@
 high-performance window.
+
+%\section{The polynomial phase sinusoid}
+%Recently techniques for estimating the parameters of complex polynomial phase sinusoids,
+%i.e., signals of the form
+%%
+%\begin{equation}
+%    \label{eq:polyphaseexp}
+%    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j)
+%\end{equation}
+%%
+%with $a_{j} \in \mathbb{C}$, have been developed. Many techniques
+%utilizing derivatives of the signal or the analysis window have
+%been developed for estimating the $a_j$. The theoretical equivalence of these
+%techniques is described in \cite{hamilton2011non}. This paper focuses on the
+%Distribution Derivative Method (DDM) only \cite{betser2009sinusoidal}, as it only requires a once-differentiable
+%analysis window and no signal derivatives, which is convenient for signal
+%processing applications.
+%
+%In \cite{hamilton2012comparisons} the accuracy
+%of the DDM in estimating each $a_{j}$ is evaluated for $Q=1$ with the constraint
+%that $\Re{a_1}=0$ and for $2 \leq Q \leq 3$ with the Hann window used to form
+%the test functions. In (Roebel) twice-differentiated windows are used to
+%estimate the frequency slopes of chirp signals. Results on the accuracy of
+%estimation for signals made of a mixture of chirps are given for the frequency
+%slope ($\Im{a_2}$) only, but a variety of windows are compared.
+%
+%In this paper, we evaluate the performance of various once-differentiable
+%windows in estimating the $a_{j}$. We are interested in windows with lower
+%sidelobes in order to better estimate parameters of sinusoidal chirp signals in
+%mixture. A technique to design once-differentiable approximations to aribitrary
+%symmetrical windows is presented along with a design example for a
+%high-performance window.
 
@@
 \[
-    x(t) = \exp(a_0) \gamma(t) + \eta (t)
+    x(t) = \exp(a_0) \gamma(t) + \epsilon (t)
 \]
-where $\eta (t)$ is the error signal, the part of the signal that is not explained
+where $\epsilon (t)$ is the error signal, the part of the signal that is not explained
 by our model, and $\gamma (t)$ is the part of the signal
@@
     \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
-        \left\langle \eta , \gamma \right\rangle
+        \left\langle \epsilon , \gamma \right\rangle
 \]
-The inner-product between $\eta$ and $\gamma$ is $0$, by the orthogonality
+The inner-product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
 principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
@@
 
-Although this technique can be exteded to describe a single
-sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
-interest to consider signals featuring a sum of $P$ such components, i.e.,
-%
-\begin{equation}
-    \label{eq:polyphaseexpmix}
-    s(t) = \sum_{i=1}^{P} x_{i}(t)
-\end{equation}
-%
-with
-%
-\[
-    x_{i}(t) = \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j)
-\]
-%
-In situations where multiple signal sources are known to exist (e.g., recordings
-of multiple speakers or performers) such a model is plausible.
-
-We examine how this mixture model influences the estimation of the $a_{i,j}$.
+We examine how the mixture model influences the estimation of the $a_{i,j}$ in
+Eq.~\ref{eq:polyphaseexpmix}.
 Consider a mixture of $P$ components.
@@
 }
-$\frac{r}{N}$ and with frequency response described by
-the Fourier transform of modulated $w$. Therefore choosing $\psi$ amounts to a
+$\frac{r}{N}$ and with frequency response described by the Fourier transform of
+modulated $w$ \cite{allen1977unified}. Therefore choosing $\psi$ amounts to a
 filter design problem under the constraints that the impulse response of the
-filter be differentiable in $t$ and finite. To minimize the influence of
-all but one component, granted the components's energy concentrations are
-sufficiently separated in frequency, we desire impulse responses whose magnitude
-response gives maximum
-out-of-band rejection or equivalently, windows whose Fourier transform exhibits
-the lowest sidelobes.
+filter be differentiable in $t$ and finite. To minimize the influence of all but
+one component, granted the components's energy concentrations are sufficiently
+separated in frequency, we desire impulse responses whose magnitude response
+gives maximum out-of-band rejection or equivalently, windows whose Fourier
+transform exhibits the lowest sidelobes.
 
 In all the publications these authors reviewed on the DDM, the window used was
-the Hann window which is once-differentiable everywhere in the time-domain.
-Nuttall \cite{nuttall1981some} has designed windows with lower sidelobes than the canonical Hann
-window which are everywhere at least once-differentiable. It is also possible to
-design approximations to aribtrary symmetrical window functions using
-harmonically related cosines, as is discussed in the following section.
+the Hann window which is once-differentiable everywhere in the time-domain. In
+\cite{robel2002estimating}, a publication on the reassignment method, other
+windows than the Hann are considered but these windows must be
+twice-differentiable.  Nuttall \cite{nuttall1981some} has designed windows with
+lower sidelobes than the canonical Hann window which are everywhere at least
+once-differentiable. It is also possible to design approximations to aribtrary
+symmetrical window functions using harmonically related cosines, as is discussed
+in the following section.
 
@@
 A differentiable approximation to a symmetrical window can be designed in a
-straight-forward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
+straightforward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
 is shown how to design optimal windows of length $N$ samples using a linear
@@
 
-We choose the $b_{k}$ so that the window $w$'s squared approximation error to
+Rather design based on an optimality criterion, such as the height of the
+highest sidelobe, a once-differentiable approximation to an existing window $v$ is
+desired. To do this, we choose the $b_{k}$ so that the window $w$'s squared approximation error to
 $v$ is minimized
@@
 \label{sec:designexample}
-\begin{figure*}[t]
-    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
-\caption{\label{fig:dpwmainlobe} Comparing the main-lobe and asymptotic power
-spectrum characteristics of the continuous 4-term Nuttall window, the digital
-prolate window with $W=0.008$, and the continuous approximation to the digital
-prolate window.}
-\end{figure*}
 
@@
 Digital prolate spheroidal windows are a parametric approximation to functions
-proposed by whose Fourier transform's energy is maximized in a given bandwidth
+whose Fourier transform's energy is maximized in a given bandwidth
 \cite{slepian1978prolate}. These can be tuned to have extremely low sidelobes,
@@
 4-term Nuttall window was obtained with $W=0.008$. Its magnitude response is
-shown in Fig.~\ref{fig:dpwmainlobe}~and~\ref{fig:dpwasymptotic}. We see that
+shown in Fig.~\ref{fig:dpw}. We see that
 this window's asymptotic roll-off is 6 dB per octave and is therefore has a
@@
 The magnitude response of the approximation is shown in
-Fig.~\ref{fig:dpwmainlobe}.  We see that we obtain a lower highest sidelobe
+Fig.~\ref{fig:dpw}.  We see that we obtain a lower highest sidelobe
 level than the Nuttall and Prolate windows by slightly sarificing the narrowness
-of the main lobe. Furthermore in Fig.~\ref{fig:dpwasymptotic} we observe that
+of the main lobe. Furthermore in Fig.~\ref{fig:dpw} we observe that
 the rolloff of the window is 18 dB per octave because it is once-differentiable
@@
 
-\begin{figure*}[ht]
-    \centerline{\includegraphics[width=5in]{{ddm_snr_win_comp}.eps}}
-\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
-phase sinusoids averaged over 1000 trials. \textit{C} is the Cram\'{e}r-Rao
-lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
-Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continous
-5-cosine-term approximation to a digital prolate window as described in
-Sec.~\ref{sec:designexample}.}
-\end{figure*}
-
-As in \cite{betser2009sinusoidal} we synthesized random sinusoids using Eq.~\ref{eq:polyphaseexp}
-with $Q=2$ and compared the average estimation error variance with the
-theoretical minimum given by the Cram\'{e}r-Rao bound. The original Hann window,
+To compare the average estimation error variance with the
+theoretical minimum given by the Cram\'{e}r-Rao bound we synthesized random sinusoids using Eq.~\ref{eq:polyphaseexp}
+with $Q=2$ and parameters choosen from uniform distributions justified in
+\cite{betser2009sinusoidal}. The original Hann window,
 the windows proposed by Nuttall and the new digital prolate based window were
 used to synthesize the atoms as described in Sec.~\ref{sec:designingatoms} and
-their their estimation error variance was compared (see
+their estimation error variance was compared (see
 Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
@@
 
-\begin{figure*}[ht]
-    \centerline{\includegraphics[width=5in]{{comp_offset_chirp_est_err}.eps}}
-\caption{\label{fig:mixwincomp}}
-\end{figure*}
-
 To evaluate the performance of the various windows when estimating the
 parameters of components in mixture we synthesized signals using
-Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$. One of the two components was
-scaled to give a desired signal power ratio with the other component. The
-parameters of both components were estimated and the total squared estimation
-error for all the parameters was recorded. In Fig.~\ref{fig:mixwincomp} we see
-that there is generally less estimation error for components having similar
-signal power. This is to be expected as there will be less masking of the weaker
-signal in these scenarios. The estimation error is large when the atoms
-containing the most signal energy for each component are not greatly separated
-in frequency. This is due to the convolution of the Fourier transform of
-the window with the signal, and agrees with what was predicted by
-Eq.~\ref{eq:mixest}: indeed windows with a larger main lobe exhibit a
-larger `radius' in which the error of the parameter estimation will be high.
-However, for signals with local inner product maxima are with atoms sufficiently
+Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
+uniform distributions specified in \cite{betser2009sinusoidal}. One of the two
+components was scaled to give a desired signal power ratio with the other
+component. The parameters of both components were estimated and the total
+squared estimation error for all the parameters was recorded. In
+Fig.~\ref{fig:mixwincomp} we see that there is generally less estimation error
+for components having similar signal power. This is to be expected as there will
+be less masking of the weaker signal in these scenarios. The estimation error is
+large when the atoms containing the most signal energy for each component are
+not greatly separated in frequency. This is due to the convolution of the
+Fourier transform of the window with the signal, and agrees with what was
+predicted by Eq.~\ref{eq:mixest}: indeed windows with a larger main lobe exhibit
+a larger `radius' in which the error of the parameter estimation will be high.
+However, for signals where local inner product maxima are from atoms sufficiently
 separated in frequency, windows with lower sidelobes are better at attenuating

### 2017-03-11 comp_offset_chirp_est_err.py

@@ -17,7 +17,7 @@ W_l_ms=32
 R=3
 # prepare chirps
 
-chirps=ddm.build_offset_chirps(N_chirps=6,
+chirps=ddm.build_offset_chirps(N_chirps=4,
                                # Sample rate (Hz)
                                F_s=F_s,
                                # Window length (ms)
@@ -28,8 +28,8 @@ wins=['hann','c1-nuttall-4','c1-nuttall-3','prolate-0.008-approx-5']
 line_stys=['solid','dotted','dashed','dashdot']
 labels=['H','C4','C3','P5']
 sr_min=-30
-srs=np.arange(sr_min,10,10)
-n_diffs=40
+srs=np.arange(sr_min,10,30)
+n_diffs=20
 diffs=xrange(n_diffs)
 errs=dict()
 for w in wins:
@@ -38,6 +38,13 @@ for w in wins:
         errs[w][s]=dict()
         errs[w][s]['diffs']=[0 for _ in diffs]
         errs[w][s]['diffs_log']=[0 for _ in diffs]
+        errs[w][s]['diffs_params']=dict()
+        errs[w][s]['diffs_params']['a0']=[0 for _ in diffs]
+        errs[w][s]['diffs_params']['a1']=[0 for _ in diffs]
+        errs[w][s]['diffs_params']['a2']=[0 for _ in diffs]
+        errs[w][s]['diffs_params']['b0']=[0 for _ in diffs]
+        errs[w][s]['diffs_params']['b1']=[0 for _ in diffs]
+        errs[w][s]['diffs_params']['b2']=[0 for _ in diffs]
 
 cmap=plt.get_cmap('Greys')
 
@@ -80,12 +87,22 @@ for w in wins:
                     except TypeError:
                         nlsqerrs += 1
                         continue
-                    errs[w][s]['diffs'][d] += np.sum(errs_1) + np.sum(errs_2)
+                    errs[w][s]['diffs'][d] += (np.sum(np.power(errs_1,2.)) +
+                                                np.sum(np.power(errs_2,2.)))
+                    for param,err1,err2 in zip(['a0','a1','a2','b0','b1','b2'],
+                                            errs_1,errs_2):
+                        errs[w][s]['diffs_params'][param][d] =  (err1**2. +
[…]

### 2017-03-11 ddm.py

@@ -453,6 +453,10 @@ def p2_1_3_est(x,ch,kma0,w_name='hann',F_s=16000,R=3):
         The bin of the centre atom in the estimation scheme.
     w_name:
         The name of the kind of window to use (see: w_dw_sum_cos)
+
+    Returns:
+
+        A tuple containing the absolute error for each parameter.
     """
     # Generate window
     w,dw=w_dw_sum_cos(len(x),w_name,norm=False)

### 2017-03-16 paper/paper.tex
Compare error on each paramater for 2 components.

@@
 \hyphenation{spher-oidal}
+%\hyphenation{amp-li-tude}
+%\hyphenation{mod-u-lat-ed}
 
@@
 
+\input{ddm_snr_win_comp_defs.txt}
+\input{comp_offset_chirp_est_err_defs.txt}
+
 \begin{document}
@@
 \begin{abstract}
-TODO
+    The accuracy of the Distribution Derivative Method (DDM)
+    \cite{betser2009sinusoidal} is evaluated on mixtures of chirp signals. It is
+    shown that accurate estimation can be obtained when the sets of atoms for
+    which the inner product is large are disjoint.  This amounts to designing
+    atoms with windows whose Fourier transform exhibits low sidelobes but which
+    are once-differentiable in the time-domain. A technique for designing
+    once-differentiable approximations to windows is presented and the accuracy
+    of these windows in estimating the parameters of chirps in mixture is
+    evaluated.
 \end{abstract}
-
-\begin{figure*}[t]
-    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
-\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
-spectrum characteristics of the continuous 4-term Nuttall window, the digital
-prolate window with $W=0.008$, and the continuous approximation to the digital
-prolate window.}
-\end{figure*}
-
-\begin{figure*}[ht]
-    \centerline{\includegraphics[width=5in]{{ddm_snr_win_comp}.eps}}
-\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
-phase sinusoids averaged over 1000 trials. \textit{C} is the Cram\'{e}r-Rao
-lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
-Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continous
-5-cosine-term approximation to a digital prolate window as described in
-Sec.~\ref{sec:designexample}.}
-\end{figure*}
-
-\begin{figure*}[ht]
-    \centerline{\includegraphics[width=5in]{{comp_offset_chirp_est_err}.eps}}
-\caption{\label{fig:mixwincomp}}
-\end{figure*}
 
@@
 components in mixture can corrupt estimations of the frequency slope
-($\Im{a_{0,2}}$ and $\Im{a_{1,2}}$) is investigated in the context of the
+($\Im\{a_{0,2}\}$ and $\Im\{a_{1,2}\}$) is investigated in the context of the
 reassignment method, a related technique, but the corruption of the other
@@
 The signal-derivatives technique we will consider is the
-Distribution Derivative Method for its convenience: the technique does not
+DDM for its convenience: the technique does not
 require computing derivatives of the signal to be analysed. It does, however, require a
-$p$ times differentiable analysis window where $p+1$ is the order of the
-phase polynomial to be estimated.
+once-differentiable analysis window.
 
@@
 by our model, and $\gamma (t)$ is the part of the signal
-whose coefficients have already been estimated
+whose coefficients have already been estimated, i.e.,
 \[
@@
     \label{eq:mixest}
-    \sum_{i=1}{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
+    \sum_{i=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
     0
@@
 \label{sec:designingatoms}
-
+%
+\begin{figure*}[t]
+    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
+\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
+spectrum characteristics of the continuous 4-term Nuttall window, the digital
+prolate window with $W=0.008$, and the continuous approximation to the digital
+prolate window.}
+\end{figure*}
+%
 In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
@@
 \section{Differentiable approximations to windows}
-
+%
+\begin{figure*}[ht]
+    \centerline{\includegraphics[width=7in]{{ddm_snr_win_comp}.eps}}
+\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
+    phase sinusoids averaged over $K_{1}=\Ksnr{}$ trials using atoms generated from
+    various windows. \textit{C} is the Cram\'{e}r-Rao
+lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
+Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continous
+5-cosine-term approximation to a digital prolate window as described in
+Sec.~\ref{sec:designexample}.}
+\end{figure*}
+%
 A differentiable approximation to a symmetrical window can be designed in a
@@
 
-\section{Continuous window design example}
+\section{A continuous window design example}
 \label{sec:designexample}
-
+%
+\begin{figure*}[ht]
+    \centerline{\includegraphics[width=7in]{{comp_offset_chirp_est_err_params}.eps}}
+\caption{\label{fig:mixwincomp} The mean squared estimation error for each
+    parameter in an analysis of two components in mixture. A set of
+    $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
+    maximum bin differences $0 \leq d < \Doffset{}$. The signal power ratio
+    between components is indicated using shades of grey: lighter shades
+    indicate a ratio closer to $1$. The ratio in decibels is indicated in the
+    plot legend. The names indicate the windows used to generate the atoms for
+    estimation: \textit{N3} and \textit{N4} are the 3- and 4-cosine-term
+    continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
+is the continous 5-cosine-term approximation to a digital prolate window as
+described in Sec.~\ref{sec:designexample}.}
+\end{figure*}
+%
 As a design example we show how to create a continuous approximation of a digital
@@
 shown in Fig.~\ref{fig:dpw}. We see that
-this window's asymptotic roll-off is 6 dB per octave and is therefore has a
+this window's asymptotic falloff is 6 dB per octave and therefore has a
 discontinuity somewhere in its domain \cite{nuttall1981some}. We designed an approximate
@@
 of the main lobe. Furthermore in Fig.~\ref{fig:dpw} we observe that
-the rolloff of the window is 18 dB per octave because it is once-differentiable
+the falloff of the window is 18 dB per octave because it is once-differentiable
 at all points in its domain.
@@
 To compare the average estimation error variance with the
-theoretical minimum given by the Cram\'{e}r-Rao bound we synthesized random sinusoids using Eq.~\ref{eq:polyphaseexp}
+theoretical minimum given by the Cram\'{e}r-Rao bound we synthesized $K_{1}$ random
+chirps using Eq.~\ref{eq:polyphaseexp}
 with $Q=2$ and parameters choosen from uniform distributions justified in
@@
 Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
-uniform distributions specified in \cite{betser2009sinusoidal}. One of the two
-components was scaled to give a desired signal power ratio with the other
-component. The parameters of both components were estimated and the total
-squared estimation error for all the parameters was recorded. In
-Fig.~\ref{fig:mixwincomp} we see that there is generally less estimation error
-for components having similar signal power. This is to be expected as there will
-be less masking of the weaker signal in these scenarios. The estimation error is
-large when the atoms containing the most signal energy for each component are
-not greatly separated in frequency. This is due to the convolution of the
-Fourier transform of the window with the signal, and agrees with what was
-predicted by Eq.~\ref{eq:mixest}: indeed windows with a larger main lobe exhibit
-a larger `radius' in which the error of the parameter estimation will be high.
-However, for signals where local inner product maxima are from atoms sufficiently
-separated in frequency, windows with lower sidelobes are better at attenuating
-the other component and for these the estimation error is lowest.
+uniform distributions specified in \cite{betser2009sinusoidal}. A set
+$\mathcal{C}$ of $K_{2}$ components was synthesized. The atom $r^{\ast}$ for which
+the inner product was maximized was determined for each unmixed chirp and the
+chirp was modulated by $\exp(-2\pi \frac{r^{\ast} n}{N}\sqrt{-1})$ for $0 \leq n
+< N$ in order to move this maximum to $r=0$. Then for each desired difference
+$d$ between maxima in bins, with $0 \leq d < D$, two unique chirps were
+selected from $\mathcal{C}$ and one chirp was modulated by $\exp(2\pi
+\frac{d n}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to give the desired difference in
+maxima. This component was also scaled by a constant to give a desired signal
+power ratio with the other component. The parameters of both components were
+estimated using the bins surrounding $r=0$ and $r=d$ for each component
+respectively and the squared estimation error for each parameter was summed and divided
+by $K_{2}(K_{2}-1)$ to give the averaged squared estimation error for each
+parameter at each difference $d$.
+
+In Fig.~\ref{fig:mixwincomp} we see that there is generally less estimation
+error for components having similar signal power. This is to be expected as
+there will be less masking of the weaker signal in these scenarios.  The
+estimation error is large when the atoms containing the most signal energy for
+each component are not greatly separated in frequency. This is due to the
+convolution of the Fourier transform of the window with the signal, and agrees
+with what was predicted by Eq.~\ref{eq:mixest}: indeed windows with a larger
+main lobe exhibit a larger `radius' in which the error of the parameter
+estimation will be high.  However, for signals where local inner product maxima
+are from atoms sufficiently separated in frequency, windows with lower sidelobes
+are better at attenuating the other component and for these the estimation error
+is lowest.
 
@@
 
-\section{Acknowledgments}
+Motivated by the need to analyse mixtures of frequency- and
+am\-pli\-tude-mod\-u\-lat\-ed
+sinusoids (Eq.\ref{eq:polyphaseexpmix}), we have shown that the DDM can be
+employed under a single-component
+assumption when components have roughly disjoint sets of atoms for which their
+inner products take on large values. This indicates the need for windows whose
+Fourier transform exhibits low sidelobes. We developed windows whose sidelobes
+are minimized while remaining everywhere once-differentiable: a requirement to
+generate valid atoms for the DDM. These windows were shown to improve parameter
+estimation of $P=1$ and $P=2$ components in mixture, granted the components
+exhibited reasonable separation in frequency between the atoms for which the
+inner product was maximized.
+
+Further work should evaluate these windows on sinusoids of different orders,
+i.e., $Q \gg 1$. Optimal main-lobe widths for windows should be determined
+depending on the separation of local maxima in the power spectrum. It should
+also be determined if these windows improve the modeling of real-world acoustic
+signals.
+
+%\section{Acknowledgments}
 
@@
 
-\section{Appendix}
+%\section{Appendix}
 

### 2017-03-16 comp_offset_chirp_est_err.py

@@ -10,14 +10,17 @@ import warnings
 plt.rc('text',usetex=True)
 plt.rc('font',**ddm.FONT_OPT['dafx'])
 
+show_plots=False
+
 #warnings.simplefilter('error','RuntimeWarning')
 
 F_s=16000
 W_l_ms=32
 R=3
 # prepare chirps
+N_chirps=10
 
-chirps=ddm.build_offset_chirps(N_chirps=4,
+chirps=ddm.build_offset_chirps(N_chirps=N_chirps,
                                # Sample rate (Hz)
                                F_s=F_s,
                                # Window length (ms)
@@ -29,7 +32,7 @@ line_stys=['solid','dotted','dashed','dashdot']
 labels=['H','C4','C3','P5']
 sr_min=-30
 srs=np.arange(sr_min,10,30)
-n_diffs=20
+n_diffs=40
 diffs=xrange(n_diffs)
 errs=dict()
 for w in wins:
@@ -62,7 +65,7 @@ for w in wins:
             errs[w][s]['diffs'][d]=0.
             errs[w][s]['diffs_log'][d]=0.
             for c1 in chirps:
-                for c2 in chirps:
+                for c2 in list(set(chirps) - set([c1])):
                     p_x1=c1.p_x()
                     p_x2=c2.p_x()
                     # desired power ratio
@@ -96,20 +99,20 @@ for w in wins:
 
             for param,err1,err2 in zip(['a0','a1','a2','b0','b1','b2'],
                                     errs_1,errs_2):
-                errs[w][s]['diffs_params'][param][d] /= len(chirps)**2. - nlsqerrs
-            errs[w][s]['diffs'][d] /= len(chirps)**2. - nlsqerrs
+                errs[w][s]['diffs_params'][param][d] /= len(chirps)*(len(chirps)-1) - nlsqerrs
+            errs[w][s]['diffs'][d] /= len(chirps)*(len(chirps)-1) - nlsqerrs
             errs[w][s]['diffs_log'][d] =np.log10(errs[w][s]['diffs'][d])
-            print 'nerrs: %d for sr %f' % (nlsqerrs,s)
+            #print 'nerrs: %d for sr %f' % (nlsqerrs,s)
 
 fig=plt.figure(1)
[…]

### 2017-03-16 ddm_snr_win_comp.py

@@ -10,6 +10,8 @@ import matplotlib.pyplot as plt
 plt.rc('text',usetex=True)
 plt.rc('font',**ddm.FONT_OPT['dafx'])
 
+show_plots=False
+
 # Sample rate (Hz)
 F_s=16000
 # Window length (ms)
@@ -34,7 +36,7 @@ ph2_r=[-1.e4,1.e4]
 ph3_r=[-1.e6,1.e6]
 
 # Number of evaluations to perform
-N_eval=100
+N_eval=1000
 
 # SNRs to test
 snrs=np.arange(-2,17)*(10.)
@@ -235,8 +237,16 @@ fig.suptitle(
     # hacky way to get title size
     fontsize=axarr[0,0].title.get_fontproperties().get_size_in_points())
 
+for pl in axarr.flatten():
+    pl.title.get_fontproperties().set_size(10)
+
 axarr[0,0].legend(fontsize=10,loc='lower left')
 
+fig.set_size_inches(10,7)
 plt.savefig('paper/ddm_snr_win_comp.eps')
 
-plt.show()
+with open('paper/ddm_snr_win_comp_defs.txt','w') as f:
+    f.write('\\newcommand{\Ksnr}{%d}\n' % (N_eval,))
+
+if (show_plots):
+    plt.show()

### 2017-04-06 paper/paper.tex
First round of corrections done.

@@
 \twoaffiliations{
-\paperauthorA \,\sthanks{}}
-{\href{http://www.cirmmt.org/}{https://mt.music.mcgill.ca/spcl/home} %
+\paperauthorA \,}
+{\href{http://www.cirmmt.org/}{%Sound Processing and Control Laboratory
+        SPCL %
+        \sthanks{Sound Processing and Control Laboratory} \\%
+%        Centre for Interdisciplinary Research in Music Media and Technology
+        CIRMMT %
+        \sthanks{Centre for Interdisciplinary Research in Music Media and Technology}%
+    }
 \\ McGill University %
@@
 }
-{\paperauthorB \,\sthanks{}}
-{\href{http://www.cirmmt.org/}{https://mt.music.mcgill.ca/spcl/home} %
+{\paperauthorB \,}
+{\href{http://www.cirmmt.org/}{%Sound Processing and Control Laboratory
+        SPCL \\%
+%        \sthanks{Sound Processing and Control Laboratory} \\%
+%        Centre for Interdisciplinary Research in Music Media and Technology
+        CIRMMT %
+%        \sthanks{Centre for Interdisciplinary Research in Music Media and Technology}%
+    } %
 \\ McGill University %
@@
 {\tt %
-\href{mailto:philippe.depalle@music.mcgill.ca}{philippe.depalle@music.mcgill.ca}}
+\href{mailto:philippe.depalle@mcgill.ca}{philippe.depalle@mcgill.ca}}
 }
@@
 their parameters has been made possible by a new set of techniques of only
-moderate computational complexity using signal derivatives \cite{hamilton2011non}.
+moderate computational complexity using signal derivatives \cite{hamilton2012unified}.
 %
@@
     \label{eq:polyphaseexp}
-    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j) + \eta(t)
+    s(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j) + \eta(t)
 \end{equation}
-where $\eta(t)$ is white gaussian noise.
+where $\eta(t)$ is white Gaussian noise.
 %
-Although this technique can be exteded to describe a single
+Although this technique can be extended to describe a single
 sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
@@
     \label{eq:polyphaseexpmix}
-    s(t) = \sum_{i=1}^{P} x_{i}(t) + \eta(t)
+    x(t) = \sum_{i=1}^{P} x_{i}(t) + \eta(t)
 \end{equation}
@@
 In this paper, we evaluate the performance of various once-differentiable
-windows in estimating the $a_{j}$. We are interested in windows with lower
-sidelobes in order to better estimate parameters of sinusoidal chirp signals in
-mixture. A technique to design once-differentiable approximations to aribitrary
-symmetrical windows is presented along with a design example for a
-high-performance window.
+windows in estimating the coefficients
+$a_{j}$. We are interested in windows with lower sidelobes in order to better
+estimate parameters of sinusoidal chirp signals in mixture. A technique to
+design once-differentiable approximations to arbitrary symmetrical windows is
+presented along with a design example for a high-performance window.
 
-%\section{The polynomial phase sinusoid}
-%Recently techniques for estimating the parameters of complex polynomial phase sinusoids,
-%i.e., signals of the form
-%%
-%\begin{equation}
-%    \label{eq:polyphaseexp}
-%    x(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j)
-%\end{equation}
-%%
-%with $a_{j} \in \mathbb{C}$, have been developed. Many techniques
-%utilizing derivatives of the signal or the analysis window have
-%been developed for estimating the $a_j$. The theoretical equivalence of these
-%techniques is described in \cite{hamilton2011non}. This paper focuses on the
-%Distribution Derivative Method (DDM) only \cite{betser2009sinusoidal}, as it only requires a once-differentiable
-%analysis window and no signal derivatives, which is convenient for signal
-%processing applications.
-%
-%In \cite{hamilton2012comparisons} the accuracy
-%of the DDM in estimating each $a_{j}$ is evaluated for $Q=1$ with the constraint
-%that $\Re{a_1}=0$ and for $2 \leq Q \leq 3$ with the Hann window used to form
-%the test functions. In (Roebel) twice-differentiated windows are used to
-%estimate the frequency slopes of chirp signals. Results on the accuracy of
-%estimation for signals made of a mixture of chirps are given for the frequency
-%slope ($\Im{a_2}$) only, but a variety of windows are compared.
-%
-%In this paper, we evaluate the performance of various once-differentiable
-%windows in estimating the $a_{j}$. We are interested in windows with lower
-%sidelobes in order to better estimate parameters of sinusoidal chirp signals in
-%mixture. A technique to design once-differentiable approximations to aribitrary
-%symmetrical windows is presented along with a design example for a
-%high-performance window.
-
-\section{The estimation of $a_j$}
+\section{Estimating the \lowercase{$a_{j}$}}
 We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
@@
     \frac{dx}{dt}(t)\overline{\psi}(t)
-    + x(t)\frac{d\overline{\psi}}{dt}(t) \\
-    = \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
+    + x(t)\frac{d\overline{\psi}}{dt}(t) = \\
+    \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
     + x(t)\frac{d\overline{\psi}}{dt}(t)
@@
 Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
-$\frac{df(t)}{dt}$ we obtain
+$\frac{df(t)}{dt}dt$ we obtain
 %
 \begin{multline*}
-    \int_{-\infty}^{\infty}\frac{df(t)}{dt}dt \\
-    = \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
+    \int_{-\infty}^{\infty}\frac{df(t)}{dt}dt = \\
+    \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
     + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
@@
 
-From this we can see that to estimate the coefficients $a_j$, $ 1 \leq q \leq Q
-$ we simply need $R$ atoms with $R \geq Q$ to solve the linear system of
+Estimating coefficients $a_j$, ${1 < j \leq Q}$,
+simply requires $R$ atoms with $R \geq Q$ to solve the linear system of
 equations
@@
 
-To estimate $a_0$ we write the signal we are analysing as
+To estimate $a_0$ we rewrite the signal we are analysing as
 \[
@@
 \]
-The inner-product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
+The inner product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
 principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
@@
 
-\section{The estimation of the $a_{i,j}$ of $P$ components}
+\section{Estimating the \lowercase{$a_{i,j}$} of $P$ components}
 
@@
     \label{eq:mixest}
-    \sum_{i=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
+    \sum_{i=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}}
+    \frac{df_{i}}{dt}(t)dt =
     0
     \\ = 
-    \sum_{i=1}^{P}
+    \sum_{i=1}^{P} \left(
     \sum_{j=1}^{Q} j a_{i,j} 
     \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
-     + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle
+    + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle \right)
 \end{multline}
@@
 and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
-$T$ the sample period in seconds. In this way, the atoms $\psi_{\omega}(t)$ chosen
+$T$ the sample period in seconds. In this way, the chosen atoms $\psi_{\omega}(t)$ 
 are the products of the elements of the Fourier basis and an appropriately
@@
 
-In all the publications these authors reviewed on the DDM, the window used was
+In all the publications reviewed on the DDM for this paper, the window used was
 the Hann window which is once-differentiable everywhere in the time-domain. In
@@
 lower sidelobes than the canonical Hann window which are everywhere at least
-once-differentiable. It is also possible to design approximations to aribtrary
+once-differentiable. It is also possible to design approximations to arbitrary
 symmetrical window functions using harmonically related cosines, as is discussed
@@
 lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
-Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continous
+Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continuous
 5-cosine-term approximation to a digital prolate window as described in
@@
     continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
-is the continous 5-cosine-term approximation to a digital prolate window as
+is the continuous 5-cosine-term approximation to a digital prolate window as
 described in Sec.~\ref{sec:designexample}.}
@@
 spheroidal windows under parameters $N$, the window length in samples, and a
-parameter $W$. We chose $N=512$ based on the window length chosen in
-\cite{betser2009sinusoidal} for ease of comparison. Its $W$ parameter's value
-was chosen by synthesizing windows with $W$ ranging between $0.005$ and $0.010$
-at a resolution of $0.001$. The window with the closest 3db bandwidth to the
-4-term Nuttall window was obtained with $W=0.008$. Its magnitude response is
-shown in Fig.~\ref{fig:dpw}. We see that
-this window's asymptotic falloff is 6 dB per octave and therefore has a
-discontinuity somewhere in its domain \cite{nuttall1981some}. We designed an approximate
+parameter $W$ choosing the (normalized) frequency range in which the proportion
+of the main lobe's energy is to be maximized. We chose $N=512$ based on the
+window length chosen in \cite{betser2009sinusoidal} for ease of comparison. Its
+$W$ parameter's value was chosen by synthesizing windows with $W$ ranging
+between $0.005$ and $0.010$ at a resolution of $0.001$. The window with the
+closest 3 dB bandwidth to the 4-term Nuttall window was obtained with $W=0.008$.
+Its magnitude response is shown in Fig.~\ref{fig:dpw}. We see that this window's
+asymptotic falloff is 6 dB per octave and therefore has a discontinuity
+somewhere in its domain \cite{nuttall1981some}. We designed an approximate
 window using Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and
@@
 using a small number of cosines. The $M$ giving the best approximation was $5$.
-The magnitude response of the approximation is shown in
-Fig.~\ref{fig:dpw}.  We see that we obtain a lower highest sidelobe
-level than the Nuttall and Prolate windows by slightly sarificing the narrowness
-of the main lobe. Furthermore in Fig.~\ref{fig:dpw} we observe that
-the falloff of the window is 18 dB per octave because it is once-differentiable
-at all points in its domain.
+The magnitude response of the approximation is shown in Fig.~\ref{fig:dpw}.  We
+see that we obtain a lower highest sidelobe level than the Nuttall and Prolate
+windows by slightly sacrificing the narrowness of the main lobe. Furthermore in
+Fig.~\ref{fig:dpw} we observe that the falloff of the window is 18 dB per octave
+because it is once-differentiable at all points in its domain.
 
@@
 chirps using Eq.~\ref{eq:polyphaseexp}
-with $Q=2$ and parameters choosen from uniform distributions justified in
+with $Q=2$ and parameters chosen from uniform distributions justified in
 \cite{betser2009sinusoidal}. The original Hann window,
@@
 Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
-uniform distributions specified in \cite{betser2009sinusoidal}. A set
-$\mathcal{C}$ of $K_{2}$ components was synthesized. The atom $r^{\ast}$ for which
-the inner product was maximized was determined for each unmixed chirp and the
-chirp was modulated by $\exp(-2\pi \frac{r^{\ast} n}{N}\sqrt{-1})$ for $0 \leq n
-< N$ in order to move this maximum to $r=0$. Then for each desired difference
-$d$ between maxima in bins, with $0 \leq d < D$, two unique chirps were
-selected from $\mathcal{C}$ and one chirp was modulated by $\exp(2\pi
-\frac{d n}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to give the desired difference in
-maxima. This component was also scaled by a constant to give a desired signal
-power ratio with the other component. The parameters of both components were
-estimated using the bins surrounding $r=0$ and $r=d$ for each component
-respectively and the squared estimation error for each parameter was summed and divided
-by $K_{2}(K_{2}-1)$ to give the averaged squared estimation error for each
-parameter at each difference $d$.
+uniform distributions specified in \cite{betser2009sinusoidal}.  We desired to
+see how the accuracy of estimation is influenced by the difference (in bins)
+between the locally maximized atoms and the difference in signal power between
+the two components. To obtain a set of components from which test signals
+exhibiting the desired differences could be constructed, we synthesized a set
+$\mathcal{C}$ of $K_{2}$ components for which the energy is maximized in bin 0.
+Test signals were obtained by choosing a pair of unique components from this set
+and modulating one to give the desired difference.  This was carried out as
+follows: the atom $r^{\ast}$ for which the inner product was maximized was
+determined for each unmixed chirp and the chirp was modulated by $\exp(-2\pi
+\frac{r^{\ast} n}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to move this maximum
+to $r=0$. Then for each desired difference $d$, with $0 \leq d < D$, two unique
+chirps were selected from $\mathcal{C}$ and one chirp was modulated by
+$\exp(2\pi \frac{n d}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to give the
+desired difference between maxima. This component was also scaled by a constant
+to give a desired signal power ratio with the other component. The parameters of
+both components were estimated using the bins surrounding $r=0$ and $r=d$ for
+each component respectively and the squared estimation error for each parameter
+was summed and divided by $K_{2}(K_{2}-1)$ (the number of choices of two unique
+components) to give the averaged squared estimation error for each parameter at
+each difference $d$.
 
-In Fig.~\ref{fig:mixwincomp} we see that there is generally less estimation
-error for components having similar signal power. This is to be expected as
-there will be less masking of the weaker signal in these scenarios.  The
-estimation error is large when the atoms containing the most signal energy for
-each component are not greatly separated in frequency. This is due to the
+The behaviour of the windows when used to analyse mixtures of non-stationary
+signals is similar the behaviour of windows used for harmonic analysis in the
+stationary case \cite{harris1978use}; here we obtain further insight into how
+each coefficient of the polynomial is influenced by main-lobe width and sidelobe
+height. In Fig.~\ref{fig:mixwincomp} we see that there is generally less
+estimation error for components having similar signal power. This is to be
+expected as there will be less masking of the weaker signal in these scenarios.
+The estimation error is large when the atoms containing the most signal energy
+for each component are not greatly separated in frequency.  This is due to the
 convolution of the Fourier transform of the window with the signal, and agrees
 with what was predicted by Eq.~\ref{eq:mixest}: indeed windows with a larger
-main lobe exhibit a larger `radius' in which the error of the parameter
-estimation will be high.  However, for signals where local inner product maxima
+main lobe exhibit a larger ``radius'' in which the error of the parameter
+estimation will be high.  However, for signals where local inner-product maxima
 are from atoms sufficiently separated in frequency, windows with lower sidelobes
@@
 am\-pli\-tude-mod\-u\-lat\-ed
-sinusoids (Eq.\ref{eq:polyphaseexpmix}), we have shown that the DDM can be
+sinusoids (Eq.~\ref{eq:polyphaseexpmix}), we have shown that the DDM can be
 employed under a single-component
@@
 generate valid atoms for the DDM. These windows were shown to improve parameter
-estimation of $P=1$ and $P=2$ components in mixture, granted the components
+estimation of $P=1$ component in noise and $P=2$ components in mixture without
+noise, granted the components
 exhibited reasonable separation in frequency between the atoms for which the

### 2017-04-06 comp_offset_chirp_est_err.py

@@ -29,7 +29,7 @@ chirps=ddm.build_offset_chirps(N_chirps=N_chirps,
 
 wins=['hann','c1-nuttall-4','c1-nuttall-3','prolate-0.008-approx-5']
 line_stys=['solid','dotted','dashed','dashdot']
-labels=['H','C4','C3','P5']
+labels=['H','N4','N3','P5']
 sr_min=-30
 srs=np.arange(sr_min,10,30)
 n_diffs=40
@@ -49,7 +49,7 @@ for w in wins:
         errs[w][s]['diffs_params']['b1']=[0 for _ in diffs]
         errs[w][s]['diffs_params']['b2']=[0 for _ in diffs]
 
-cmap=plt.get_cmap('Greys')
+cmap=plt.get_cmap('viridis')
 
 # Chirp creator
 cp2c=ddm.chirp_p2_creator(W_l_ms,F_s)

### 2017-04-06 ddm_snr_win_comp.py

@@ -44,7 +44,7 @@ snrs=np.arange(-2,17)*(10.)
 # Errors
 errs=dict()
 keys=['crlb','hann','c1-nuttall-4','c1-nuttall-3','prolate-0.008-approx-5']
-key_clrs=['grey']+['k' for _ in xrange(4)]
+key_clrs=['LightGrey']+['k' for _ in xrange(4)]
 key_ls=['solid','solid','dotted','dashed','dashdot']
 key_labels=['C','H','N4','N3','P5']
 for k,c,ls,lab in zip(keys,key_clrs,key_ls,key_labels):

### 2017-04-09 paper/paper.tex
Some final minor changes concerning plot range.

@@
 % Please use these commands to define title and author(s) of the paper:
-\def\papertitle{Improved Atoms for the Distribution Derivative Method}
+\def\papertitle{On the design and use of once-differentiable high dynamic
+resolution atoms for the Distribution Derivative Method}
 \def\paperauthorA{Nicholas Esterer}
@@
 \usepackage{color}
+\usepackage{cite}
 
@@
     once-differentiable approximations to windows is presented and the accuracy
-    of these windows in estimating the parameters of chirps in mixture is
+    of these windows in estimating the parameters of sinusoidal chirps in mixture is
     evaluated.
@@
 %
-Here the phase evolution of the sinusoid is assumed linear over
-the analysis frame, only the phase and frequency of the sinusoids at these
-analysis points are used to fit a plausible phase function after some
-the analysis points are connected to form a partial
-\cite{mcaulay1986speech}. 
+In these papers,
+\cite{serra1989system,marchand2004enhanced,haken2007beyond} the
+phase evolution of the sinusoid is assumed linear over the analysis frame, only
+the phase and frequency of the sinusoids at these analysis points are used to
+fit a plausible phase function after some the analysis points are connected to
+form a partial \cite{mcaulay1986speech}. 
 %
@@
 regularization of mathematical programs for audio source separation \cite{creager2016musicalsource}.
-%
+
 The sinusoidal model typically considered is
@@
 %
-Although this technique can be extended to describe a single
-sinusoid of arbitrary complexity simply by increasing $Q$, it is still of
-interest to consider signals featuring a sum of $P$ such components, i.e.,
+Although this technique can be extended to describe a single sinusoid of
+arbitrary complexity simply by increasing $Q$, it remains essential to consider
+signals featuring a sum of $P$ such components, whether they represent the harmonic structure of a musical sound or the union of partials resulting from a mixture of multiple signal sources (e.g., recordings of multiple speakers or performers),  i.e.,
 %
@@
 %
-In situations where multiple signal sources are known to exist (e.g., recordings
-of multiple speakers or performers) such a model is plausible.
-%
-Previous work on these methods has generally assumed signals containing a single
-component, i.e., $P=1$ or applied the technique assuming the influence of other
-components is negligible. Later we will refine when this assumption can be made.
-
-\cite{hamilton2012comparisons} gives a comprehensive evaluation of the signal
-derivative methods. In \cite{robel2002estimating} the extent to which two
-components in mixture can corrupt estimations of the frequency slope
-($\Im\{a_{0,2}\}$ and $\Im\{a_{1,2}\}$) is investigated in the context of the
-reassignment method, a related technique, but the corruption of the other
+As regards the design and evaluation of signal-derivatives analysis techniques,
+previous work has generally assumed signals containing a single component, i.e.,
+$P$ = 1 or assumed the influence of other components to be negligible. Later we
+will refine when this assumption can be made. In \cite{hamilton2012comparisons}
+the authors provide a comprehensive evaluation of various signal-derivatives
+analysis methods applied to a single-component signal. In
+\cite{robel2002estimating} the extent to which two components in mixture can
+corrupt estimations of the frequency slope ($\Im\{a_{0,2}\}$ and
+$\Im\{a_{1,2}\}$) is investigated in the context of the reassignment method, one
+of the ``signal-derivatives'' techniques, but the corruption of the other
 parameters is not considered.
 
-The signal-derivatives technique we will consider is the
-DDM for its convenience: the technique does not
-require computing derivatives of the signal to be analysed. It does, however, require a
-once-differentiable analysis window.
+In this paper, we revisit the quality of signal-derivatives estimation of
+\textit{all} the $a_{j}$ when analyzing a \textit{mixture} of components. We focus on
+the DDM \cite{betser2009sinusoidal} analysis method for its convenience as it
+can simply be considered as an atomic decomposition (see
+Sec.~\ref{sec:estimating_aj}), and does not require computing derivatives
+of the signal to be analysed.
 
-In this paper, we evaluate the performance of various once-differentiable
-windows in estimating the coefficients
-$a_{j}$. We are interested in windows with lower sidelobes in order to better
-estimate parameters of sinusoidal chirp signals in mixture. A technique to
-design once-differentiable approximations to arbitrary symmetrical windows is
-presented along with a design example for a high-performance window.
+DDM does, however, require a once-differentiable analysis window. As we are
+interested in windows with lower sidelobes in order to better estimate
+parameters of sinusoidal chirp signals in mixture, we seek windows that
+combine these two properties. For this, a technique to design
+once-differentiable approximations to arbitrary symmetrical windows is proposed
+and presented along with a design example for a high-performance window. Finally
+we evaluate the performance of various once-differentiable windows in estimating
+the $a_{j}$.
 
 \section{Estimating the \lowercase{$a_{j}$}}
+\label{sec:estimating_aj}
 We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
@@
     \label{eq:ddm:weighted:sig:derivative}
-    \frac{df(t)}{dt} = 
+    \frac{df}{dt}(t) = 
     \frac{dx}{dt}(t)\overline{\psi}(t)
@@
 Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
-$\frac{df(t)}{dt}dt$ we obtain
+$\frac{df}{dt}(t)$ we obtain
 %
 \begin{multline*}
-    \int_{-\infty}^{\infty}\frac{df(t)}{dt}dt = \\
+    \int_{-\infty}^{\infty}\frac{df}{dt}(t)dt = \\
     \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
@@
     0
-    \\ = 
+    = \\ 
     \sum_{i=1}^{P} \left(
@@
 %
-i.e., the definition of the DFT of a windowed signal.%
+i.e., the definition of the DFT of a windowed signal%
 \footnote{%
@@
     product with $\psi$ is evaluated.
-}%
+}. %
 The DFT is readily interpreted as a bank of bandpass filters centred at
@@
 
-Rather design based on an optimality criterion, such as the height of the
-highest sidelobe, a once-differentiable approximation to an existing window $v$ is
-desired. To do this, we choose the $b_{k}$ so that the window $w$'s squared approximation error to
-$v$ is minimized
-while having $w(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{
-b^{\ast}_{k} \}$ to the mathematical program
+Rather than design based on an optimality criterion, such as the height of the
+highest sidelobe \cite{rabiner1970approach}, a once-differentiable approximation
+to an existing window $v$ is desired. To do this, we choose the $b_{k}$ so that
+the window $w$'s squared approximation error to $v$ is minimized while having
+$w(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{ b^{\ast}_{k} \}$ to the
+mathematical program
 \begin{equation}
@@
 \]
-which can be solved using constrained least-squares -- a standard numerical
+which can be solved using constrained least-squares; a standard numerical
 linear algebra routine \cite[p.~585]{golub1996matrix}.
@@
     maximum bin differences $0 \leq d < \Doffset{}$. The signal power ratio
-    between components is indicated using shades of grey: lighter shades
-    indicate a ratio closer to $1$. The ratio in decibels is indicated in the
+    between components is indicated with colours and the corresponding ratio in decibels is indicated in the
     plot legend. The names indicate the windows used to generate the atoms for
@@
 
+\begin{table}[]
+    \caption{The coefficients of the once-differentiable approximation to a digital prolate
+    window designed in Sec.~\ref{sec:designexample}.
+    \label{tab:contprolate}}
+    \begin{center}
+        \begin{tabular}{c c c}
+            $b_0$ & $ = $ & 3.128 $\times 10^{-1}$ \\
+            $b_1$ & $ = $ & 4.655 $\times 10^{-1}$ \\
+            $b_2$ & $ = $ & 1.851 $\times 10^{-1}$ \\
+            $b_3$ & $ = $ & 3.446 $\times 10^{-2}$ \\
+            $b_4$ & $ = $ & 2.071 $\times 10^{-3}$ 
+            %3.128258203861262743 $\times 10^{-1}$ &
+            %4.655346501582137142 $\times 10^{-1}$ &
+            %1.851027605614040672 $\times 10^{-1}$ &
+            %3.446534984178639682 $\times 10^{-2}$ &
+            %2.071419052469766937 $\times 10^{-3}$ \\
+        \end{tabular}
+    \end{center}
+\end{table}%
+
 In \cite{verma1996digital} it was shown how to construct digital prolate
@@
 asymptotic falloff is 6 dB per octave and therefore has a discontinuity
-somewhere in its domain \cite{nuttall1981some}. We designed an approximate
+somewhere in its domain \cite{nuttall1981some}.
+
+We designed an approximate
 window using Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and
@@
 using a small number of cosines. The $M$ giving the best approximation was $5$.
-The magnitude response of the approximation is shown in Fig.~\ref{fig:dpw}.  We
-see that we obtain a lower highest sidelobe level than the Nuttall and Prolate
-windows by slightly sacrificing the narrowness of the main lobe. Furthermore in
+The magnitude response of the approximation is shown in Fig.~\ref{fig:dpw} and
+its coefficients are listed in Tab.~\ref{tab:contprolate}; the temporal shape is
+very close to a digital prolate spheroidal window with $W=0.008$ and is
+therefore omitted for brevity.
+
+It is seen that a lower highest sidelobe level than the Nuttall and Prolate
+windows is obtained by slightly sacrificing the narrowness of the main lobe. Furthermore in
 Fig.~\ref{fig:dpw} we observe that the falloff of the window is 18 dB per octave
@@
 desired difference between maxima. This component was also scaled by a constant
-to give a desired signal power ratio with the other component. The parameters of
+to give a desired signal power ratio with the other component (the power ratios
+tested were 0 dB and -30 dB). The parameters of
 both components were estimated using the bins surrounding $r=0$ and $r=d$ for
@@
 The behaviour of the windows when used to analyse mixtures of non-stationary
-signals is similar the behaviour of windows used for harmonic analysis in the
+signals is similar to the behaviour of windows used for harmonic analysis in the
 stationary case \cite{harris1978use}; here we obtain further insight into how
-each coefficient of the polynomial is influenced by main-lobe width and sidelobe
+the estimation of each coefficient of the polynomial in
+Eq.~$\ref{eq:polyphaseexp}$ is influenced by main-lobe width and sidelobe
 height. In Fig.~\ref{fig:mixwincomp} we see that there is generally less
@@
 with what was predicted by Eq.~\ref{eq:mixest}: indeed windows with a larger
-main lobe exhibit a larger ``radius'' in which the error of the parameter
-estimation will be high.  However, for signals where local inner-product maxima
-are from atoms sufficiently separated in frequency, windows with lower sidelobes
-are better at attenuating the other component and for these the estimation error
-is lowest.
+main lobe exhibit a larger ``radius'' (bandwidth) in which the error of the
+parameter estimation will be high.  However, for signals where local
+inner-product maxima are from atoms sufficiently separated in frequency, windows
+with lower sidelobes are better at attenuating the other component and for these
+the estimation error is lowest.
 

### 2017-04-09 comp_offset_chirp_est_err.py

@@ -32,6 +32,14 @@ line_stys=['solid','dotted','dashed','dashdot']
 labels=['H','N4','N3','P5']
 sr_min=-30
 srs=np.arange(sr_min,10,30)
+
+# make colours
+cmap=plt.get_cmap('magma')
+clrs=[(x+1.)/float(len(srs)+1.) for x in xrange(len(srs))]
+clr_dict=dict()
+for clr, s in zip(clrs,srs):
+    clr_dict[s]=cmap(clr)
+
 n_diffs=40
 diffs=xrange(n_diffs)
 errs=dict()
@@ -48,8 +56,6 @@ for w in wins:
         errs[w][s]['diffs_params']['b0']=[0 for _ in diffs]
         errs[w][s]['diffs_params']['b1']=[0 for _ in diffs]
         errs[w][s]['diffs_params']['b2']=[0 for _ in diffs]
-
-cmap=plt.get_cmap('viridis')
 
 # Chirp creator
 cp2c=ddm.chirp_p2_creator(W_l_ms,F_s)
@@ -109,9 +115,12 @@ fig2,axs=plt.subplots(3,2,sharex=True)
 
 diffs_min=1000.
 diffs_max=-1000.
+diffs_min2=1000.
+diffs_max2=-1000.
+diff_extrem_margin=0.5
 for w,ls,lab in zip(wins,line_stys,labels):
     for s in srs:
-        clr=cmap((-1.*s+20.)/(-1.*float(sr_min)+20.))
+        clr=clr_dict[s]
         #print errs[w][s]['diffs_log']
         plt.figure(1)
         plt.plot(diffs,
@@ -124,9 +133,17 @@ for w,ls,lab in zip(wins,line_stys,labels):
         for plt_i,param_name in enumerate(['a0','a1','a2']):
             axs[plt_i,0].plot(diffs,
                 np.log10(errs[w][s]['diffs_params'][param_name]),c=clr,ls=ls,label=lab + ' $%d$ dB' % (s,))
+            if np.max(np.log10(errs[w][s]['diffs_params'][param_name])) > diffs_max2:
+                diffs_max2 =np.max(np.log10(errs[w][s]['diffs_params'][param_name])) 
+            if np.min(np.log10(errs[w][s]['diffs_params'][param_name])) < diffs_min2:
+                diffs_min2 = np.min(np.log10(errs[w][s]['diffs_params'][param_name]))
[…]

### 2017-04-09 ddm_snr_win_comp.py

@@ -240,7 +240,7 @@ fig.suptitle(
 for pl in axarr.flatten():
     pl.title.get_fontproperties().set_size(10)
 
-axarr[0,0].legend(fontsize=10,loc='lower left')
+axarr[0,0].legend(handlelength=3.0,fontsize=10,loc='lower left')
 
 fig.set_size_inches(10,7)
 plt.savefig('paper/ddm_snr_win_comp.eps')

### 2017-06-08 paper/paper.tex
Added non-integer bin differences. Need to check why it behaves weirdly
when rounding because it worked okay without rounding, which must just use the floor, no?

Also working on drawing flow chart to describe evaluation procedure but having difficulty specifying edges with
corners.

@@
 \fi
+
+% Flowchart drawing stuff
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows}
+\tikzstyle{startstop} = [rectangle,draw=black,text centered]%, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
+\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
+\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text
+centered, draw=black, text width=3cm]
+\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
@@
     $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
-    maximum bin differences $0 \leq d < \Doffset{}$. The signal power ratio
+    maximum bin differences $0 \leq d < \Doffset{}$, with $d$ varied in
+    $\Dstep{}$ bin increments. Only local maxima are plotted for clarity. The signal power ratio
     between components is indicated with colours and the corresponding ratio in decibels is indicated in the
@@
 with the atoms, the three atoms whose inner products were greatest were used in
-the estimations, i.e., $R=3$ in Eq.~\ref{eq:ddmsyseq}. We see that windows with
-lower sidelobes exhibit the lowest possible error variance at the sacrifice of
-some estimator efficiency.
+the estimations, i.e., $R=3$ in Eq.~\ref{eq:ddmsyseq}. The windows with the
+lowest sidelobes only give the lowest error variance at very favourable SNRs, at
+real-world SNRs the original Hann window still performs best at estimating the
+parameters of a single component signal.
+
+\begin{tikzpicture}[node distance=2cm]
+
+    \node (start) [process] {Synthesize $K_{2}$ single-component signals};
+    \node (modulate) [process, below of=start] {Modulate down so peak bin is at frequency 0 for all signals};
+    \node (setd) [process, below of=modulate] {Set $d=0$};
+    \node (choosepair) [process, below of=setd] {Choose pair of signals};
+    \node (scaleone) [process, below of=choosepair] {Scale one in the pair to give desired power and peak bin according to $d$};
+    \node (addpair) [process, below of=scaleone] {Add pair together};
+    \node (tryestimate1) [process, below of=addpair] {Try estimating parameters of component with atoms at bins $\{-1,0,1\}$};
+    \node (tryestimate2) [process, below of=tryestimate1] {Try estimating parameters of component with atoms at bins $\{\hat{d}-1,\hat{d},\hat{d}+1\}$};
+    \node (sumerrs) [process, below of=tryestimate2] {Sum estimation errors of
+    each parameter and divide by $K_{2}(K_{2}-1)$};
+    \node (incd) [process, below of=sumerrs] {Increment $d$ by $\Dstep{}$ unless $d=\Doffset$};
+
+    \draw [arrow] (start) -- (modulate);
+    \draw [arrow] (modulate) -- (setd);
+    \draw [arrow] (setd) -- (choosepair);
+    \draw [arrow] (choosepair) -- (scaleone);
+    \draw [arrow] (scaleone) -- (addpair);
+    \draw [arrow] (addpair) -- (tryestimate1);
+    \draw [arrow] (tryestimate1) -- (tryestimate2);
+    \draw [arrow] (tryestimate2) -- (sumerrs);
+    \draw [arrow] (sumerrs) -- (incd);
+    \draw [arrow] (incd) -- node[anchor=east,above]{} (choosepair);
+
+\end{tikzpicture}
 
@@
 to give a desired signal power ratio with the other component (the power ratios
-tested were 0 dB and -30 dB). The parameters of
-both components were estimated using the bins surrounding $r=0$ and $r=d$ for
+tested were 0 dB and -30 dB). Because the estimation must use valid atom
+indices, $d$ was rounded to the nearest integer $\hat{d}$. The parameters of
+both components were estimated using the bins surrounding $r=0$ and $r=\hat{d}$ for
 each component respectively and the squared estimation error for each parameter

### 2017-06-08 comp_offset_chirp_est_err.py

@@ -41,14 +41,17 @@ for clr, s in zip(clrs,srs):
     clr_dict[s]=cmap(clr)
 
 n_diffs=40
-diffs=xrange(n_diffs)
+diff_step=0.25
+diffs=np.arange(0,n_diffs,diff_step)
 errs=dict()
 for w in wins:
     errs[w]=dict()
     for s in srs:
         errs[w][s]=dict()
         errs[w][s]['diffs']=[0 for _ in diffs]
+        errs[w][s]['diffs_sig']=[0 for _ in diffs]
         errs[w][s]['diffs_log']=[0 for _ in diffs]
+        errs[w][s]['diffs_sig_log']=[0 for _ in diffs]
         errs[w][s]['diffs_params']=dict()
         errs[w][s]['diffs_params']['a0']=[0 for _ in diffs]
         errs[w][s]['diffs_params']['a1']=[0 for _ in diffs]
@@ -65,11 +68,11 @@ for w in wins:
     # For all desired signal ratios
     for s in srs:
         # for all differences
-        for d in diffs:
+        for di,d in enumerate(diffs):
             #iterate through all pairs of chirps
             nlsqerrs=0
-            errs[w][s]['diffs'][d]=0.
-            errs[w][s]['diffs_log'][d]=0.
+            errs[w][s]['diffs'][di]=0.
+            errs[w][s]['diffs_log'][di]=0.
             for c1 in chirps:
                 for c2 in list(set(chirps) - set([c1])):
                     p_x1=c1.p_x()
@@ -89,32 +92,43 @@ for w in wins:
                     # Sum to make final signal
                     x=c1.x+c2_.x
                     try:
-                        #errs_1=ddm.p2_1_3_est(x,c1,0,w,F_s)
-                        #errs_2=ddm.p2_1_3_est(x,c2_,d,w,F_s)
-                        errs_1=ddm.p2_1_3_est(x,c1,0,w,F_s,R)
-                        errs_2=ddm.p2_1_3_est(x,c2_,d,w,F_s,R)
+                        errs_1,params_1=ddm.p2_1_3_est(x,c1,0,w,F_s,R)
+                        errs_2,params_2=ddm.p2_1_3_est(x,c2_,np.round(d),w,F_s,R)
                     except TypeError:
                         nlsqerrs += 1
                         continue
[…]

### 2017-06-08 ddm.py

@@ -457,6 +457,7 @@ def p2_1_3_est(x,ch,kma0,w_name='hann',F_s=16000,R=3):
     Returns:
 
         A tuple containing the absolute error for each parameter.
+        A tuple containing the estimated parameters.
     """
     # Generate window
     w,dw=w_dw_sum_cos(len(x),w_name,norm=False)
@@ -485,7 +486,8 @@ def p2_1_3_est(x,ch,kma0,w_name='hann',F_s=16000,R=3):
     b0_err=min([(ch.b0-b0_)%(2.*np.pi),(b0_-ch.b0)%(2.*np.pi)])
     b1_err=min([(ch.b1-b1_)%(np.pi*F_s),(b1_-ch.b1)%(np.pi*F_s)])
     b2_err=np.abs(ch.b2-b2_)
-    return (a0_err,a1_err,a2_err,b0_err,b1_err,b2_err)
+    return ((a0_err,a1_err,a2_err,b0_err,b1_err,b2_err),
+                (a0_,a1_,a2_,b0_,b1_,b2_))
 
 def psw_design(N,W):
     """
@@ -604,3 +606,11 @@ def crlb_pq(a,t,sig2):
     # Return diagonal of inverse
     return np.diag(np.linalg.inv(F))
 
+def localmax(x):
+    """
+    Returns local maxima of x and the mask used to get them. Includes endpoints
+    even though not necessarily local maxima.
+    """
+    x=np.array(x).flatten()
+    xmask=np.r_[True,(x[1:]>x[:-1])[:-1]&(x[:-1]>x[1:])[1:],True]
+    return (x[xmask],xmask)

### 2017-06-11 paper/paper.tex
Incorporated revisions, removed local maxima plotting of 2 component estimates.

@@
 \usepackage{cite}
+\usepackage{float}
 
@@
 \usepackage{tikz}
-\usetikzlibrary{shapes.geometric, arrows}
+\usetikzlibrary{shapes.geometric, arrows, positioning, calc}
 \tikzstyle{startstop} = [rectangle,draw=black,text centered]%, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
 \tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
-\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text
+\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=0cm, text
 centered, draw=black, text width=3cm]
+\tikzstyle{emptybox} = []
 \tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
 \tikzstyle{arrow} = [thick,->,>=stealth]
+\tikzstyle{noarrow} = [thick,-,>=stealth]
 
@@
 \\ Montreal, Quebec, Canada \\
-{\tt %
+\tt %
 \href{mailto:philippe.depalle@mcgill.ca}{philippe.depalle@mcgill.ca}}
-}
 
@@
 
-The sinusoidal model typically considered is
+The sinusoidal model approximating signal $s$ typically considered is
 %
@@
     \label{eq:polyphaseexp}
-    s(t) = \exp(a_0 + \sum_{j=1}^{Q} a_j t^j) + \eta(t)
+    \tilde{s}(t) = \exp(a_0 + \sum_{q=1}^{Q} a_{q} t^q) + \eta(t)
 \end{equation}
-where $\eta(t)$ is white Gaussian noise.
+where $\tilde{s}$ is the approximating signal, $t$ the variable of time, the
+$a_{q} \in \mathbb{C}$ coefficients of the argument's polynomial, and $\eta(t)$
+white Gaussian noise.
 %
@@
     \label{eq:polyphaseexpmix}
-    x(t) = \sum_{i=1}^{P} x_{i}(t) + \eta(t)
+    x(t) = \sum_{p=1}^{P} x_{p}(t) + \eta(t)
 \end{equation}
@@
 %
-\[
-    x_{i}(t) = \exp(a_{i,0} + \sum_{j=1}^{Q} a_{i,j} t^j)
-\]
+\begin{equation}
+    x_{p}(t) = \exp(a_{p,0} + \sum_{q=1}^{Q} a_{p,q} t^q)
+\end{equation}
 %
@@
 $\Im\{a_{1,2}\}$) is investigated in the context of the reassignment method, one
-of the ``signal-derivatives'' techniques, but the corruption of the other
+of the signal-derivatives techniques, but the corruption of the other
 parameters is not considered.
@@
 In this paper, we revisit the quality of signal-derivatives estimation of
-\textit{all} the $a_{j}$ when analyzing a \textit{mixture} of components. We focus on
+\textit{all} the $a_{q}$ when analyzing a \textit{mixture} of components. We focus on
 the DDM \cite{betser2009sinusoidal} analysis method for its convenience as it
@@
 
-DDM does, however, require a once-differentiable analysis window. As we are
+The DDM does, however, require a once-differentiable analysis window. As we are
 interested in windows with lower sidelobes in order to better estimate
@@
 we evaluate the performance of various once-differentiable windows in estimating
-the $a_{j}$.
+the $a_{q}$.
 
-\section{Estimating the \lowercase{$a_{j}$}}
+\section{Estimating the parameters \lowercase{$a_{q}$}}
 \label{sec:estimating_aj}
-We will now show briefly how the DDM can be used to estimate the $a_j$. Based on
+We will now show briefly how the DDM can be used to estimate the $a_{q}$. Based on
 the theory of distributions \cite{schwartz1959theorie}, the DDM
@@
 respect to time variable $t$ and be non-zero only on a finite interval
-$[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define
+$[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define the inner product
 %
@@
 %
-\[
+\begin{equation}
 \mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
-\]
+\end{equation}
 %
@@
 %
-\[
+\begin{equation}
     f(t) = x(t) \overline{\psi}(t)
-\]
+\end{equation}
 %
@@
     + x(t)\frac{d\overline{\psi}}{dt}(t) = \\
-    \left( \sum_{j=1}^{Q} j a_j t^{j-1} \right) x(t)\overline{\psi}(t)
+    \left( \sum_{q=1}^{Q} q a_{q} t^{q-1} \right) x(t)\overline{\psi}(t)
     + x(t)\frac{d\overline{\psi}}{dt}(t)
@@
 %
-\begin{multline*}
+\begin{multline}
     \int_{-\infty}^{\infty}\frac{df}{dt}(t)dt = \\
-    \sum_{j=1}^{Q} j a_j \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{j-1} x(t) \overline{\psi}(t) dt
+    \sum_{q=1}^{Q} q a_{q} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{q-1} x(t) \overline{\psi}(t) dt
     + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
-\end{multline*}
+\end{multline}
 %
@@
 %
-\[ 
-    \sum_{j=1}^{Q} j a_j 
-    \left\langle \mathcal{T}^{j-1} x , \overline{\psi} \right\rangle
+\begin{equation} 
+    \sum_{q=1}^{Q} q a_{q} 
+    \left\langle \mathcal{T}^{q-1} x , \overline{\psi} \right\rangle
     = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
-\]
+\end{equation}
 %
 
-Estimating coefficients $a_j$, ${1 < j \leq Q}$,
+Estimating coefficients $a_{q}$, ${1 < q \leq Q}$,
 simply requires $R$ atoms with $R \geq Q$ to solve the linear system of
@@
     \label{eq:ddmsyseq}
-    \sum_{j=1}^{Q} j a_j 
-    \left\langle \mathcal{T}^{j-1} x , \overline{\psi}_{r} \right\rangle
+    \sum_{q=1}^{Q} q a_{q} 
+    \left\langle \mathcal{T}^{q-1} x , \overline{\psi}_{r} \right\rangle
     = -\left\langle x, \frac{d\overline{\psi}_{r}}{dt} \right\rangle
@@
 To estimate $a_0$ we rewrite the signal we are analysing as
-\[
+\begin{equation}
     x(t) = \exp(a_0) \gamma(t) + \epsilon (t)
-\]
+\end{equation}
 where $\epsilon (t)$ is the error signal, the part of the signal that is not explained
@@
 whose coefficients have already been estimated, i.e.,
-\[
-    \gamma(t) = \exp \left( \sum_{j=1}^{Q} a_j t^{j} \right)
-\]
+\begin{equation}
+    \gamma(t) = \exp \left( \sum_{q=1}^{Q} a_{q} t^{q} \right)
+\end{equation}
 Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
-\[
+\begin{equation}
     \left\langle x , \gamma \right\rangle
@@
         \left\langle \epsilon , \gamma \right\rangle
-\]
+\end{equation}
 The inner product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
@@
 depend on $t$, we have
-\[
+\begin{equation}
     \left\langle x , \gamma \right\rangle
@@
     \exp(a_0) \left\langle \gamma , \gamma \right\rangle
-\]
+\end{equation}
 so we can estimate $a_0$ as
@@
 
-\section{Estimating the \lowercase{$a_{i,j}$} of $P$ components}
+As will be seen in subsequent sections, the DDM typically involves taking the
+discrete Fourier transform (DFT) of the signal windowed by both an everywhere once-differentiable function of
+finite support (e.g., the Hann window) and this function's derivative. A small
+subset of atoms corresponding to the peak bins in the DFT are used in
+Eq.~\ref{eq:ddmsyseq} to solve for the parameters $a_{q}$.
 
-We examine how the mixture model influences the estimation of the $a_{i,j}$ in
+\section{Estimating the \lowercase{$a_{p,q}$} of $P$ components}
+
+We examine how the mixture model influences the estimation of the $a_{p,q}$ in
 Eq.~\ref{eq:polyphaseexpmix}.
@@
 %
-\[
-    g(t) = \sum_{i=1}^{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}^{P} f_{i}(t)
-\]
+\begin{equation}
+    g(t) = \sum_{p=1}^{P} x_{p}(t) \overline{\psi}(t) = \sum_{p=1}^{P} f_{p}(t)
+\end{equation}
 %
@@
     \label{eq:mixest}
-    \sum_{i=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}}
-    \frac{df_{i}}{dt}(t)dt =
+    \sum_{p=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}}
+    \frac{df_{p}}{dt}(t)dt =
     0
     = \\ 
-    \sum_{i=1}^{P} \left(
-    \sum_{j=1}^{Q} j a_{i,j} 
-    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
+    \sum_{p=1}^{P} \left(
+    \sum_{q=1}^{Q} q a_{p,q} 
+    \left\langle \mathcal{T}^{q-1} x_i , \overline{\psi} \right\rangle
     + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle \right)
@@
 %
-From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
+From this we see if $\left\langle \mathcal{T}^{q-1} x_i , \overline{\psi}_{r}
 \right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
-are small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
-can simply estimate the parameters $a_{i^{\ast},j}$ using
-\[
-    \sum_{j=1}^{Q} j a_{{i^{\ast}},j} 
-    \left\langle \mathcal{T}^{j-1} x_{i^{\ast}} , \overline{\psi}_{r} \right\rangle
-    = -\left\langle x_{i^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
-\]
-for $1 \leq r \leq R$. To compute $a_{i^{\ast},0}$ we simply use
-\[
-    \gamma_{i^{\ast}}(t) = \exp \left( \sum_{j=1}^{Q} a_{i^{\ast},j} t^{j} \right)
-\]
+are small for all but $p = p^{\ast}$ and a subset of $R$ atoms, we
+can simply estimate the parameters $a_{p^{\ast},q}$ using
+\begin{equation}
+    \sum_{q=1}^{Q} q a_{{p^{\ast}},q} 
+    \left\langle \mathcal{T}^{q-1} x_{p^{\ast}} , \overline{\psi}_{r} \right\rangle
+    = -\left\langle x_{p^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
+\end{equation}
+for $1 \leq r \leq R$. To compute $a_{p^{\ast},0}$ we simply use
+\begin{equation}
+    \gamma_{p^{\ast}}(t) = \exp \left( \sum_{q=1}^{Q} a_{p^{\ast},q} t^{q} \right)
+\end{equation}
 in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.
@@
 In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
-the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
-and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
+the DFT on a signal $x$ that is properly sampled
+and so can be evaluated at a finite number of time-points $nT$ with $n \in [0,N-1]$ and
 $T$ the sample period in seconds. In this way, the chosen atoms $\psi_{\omega}(t)$ 
@@
 %
-\[
-    \psi_{\omega}(t) = w(t) \exp(-\sqrt{-1} \omega t)
-\]
+\begin{equation}
+    \label{eq:fourieratom}
+    \psi_{\omega}(t) = w(t) \exp(-j \omega t)
+\end{equation}
 %
-Defining $N = \frac{L_{t}}{T}$ and $\omega = 2
-\pi \frac{r}{N}$, the approximate
-inner product is then
+Defining $N = \frac{L_{t}}{T}$ and angular frequency at bin $r$ as $\omega = 2
+\pi \frac{r}{N}$, the approximate inner product is then
 %
-\[
+\begin{equation}
+    \label{eq:approxinnerprod}
     \left\langle x , \psi_{\omega} \right\rangle \approx 
-    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
-\]
+    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi j r \frac{n}{N}) 
+\end{equation}
 %
@@
 normalized frequencies%
-\footnote{%
-In this article as in much of the literature on signal processing the index $r$
-of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
-\frac{r}{N}$ will be referred to as its bin number.
-}
+%\footnote{%
+%In this article as in much of the literature on signal processing the index $r$
+%of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
+%\frac{r}{N}$ will be referred to as its bin number.
+%}
 $\frac{r}{N}$ and with frequency response described by the Fourier transform of
@@
 \begin{equation}
-    w(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
+    \tilde{w}(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
 \mathcal{R}(\frac{n}{N})
@@
 at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
-\[
+\begin{equation}
 \sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
-\]
+\end{equation}
 
@@
 highest sidelobe \cite{rabiner1970approach}, a once-differentiable approximation
-to an existing window $v$ is desired. To do this, we choose the $b_{k}$ so that
-the window $w$'s squared approximation error to $v$ is minimized while having
-$w(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{ b^{\ast}_{k} \}$ to the
+to an existing window $w$ is desired. To do this, we choose the $b_{k}$ so that
+the window $\tilde{w}$'s squared approximation error to $w$ is minimized while having
+$\tilde{w}(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{ b^{\ast}_{k} \}$ to the
 mathematical program
@@
     \text{minimize}
-    \sum_{n=0}^{N-1} ( v(n) 
+    \sum_{n=0}^{N-1} ( w(n) 
         - \sum_{k=0}^{M-1} b_{k} \cos(2 \pi k \frac{n}{N}))^{2}
 \end{equation}
-\[
+\begin{equation}
     \text{subject to} \\
     \sum_{k=0}^{M-1} b_{k} \cos(\pi k ) = 0
-\]
+\end{equation}
 which can be solved using constrained least-squares; a standard numerical
@@
     maximum bin differences $0 \leq d < \Doffset{}$, with $d$ varied in
-    $\Dstep{}$ bin increments. Only local maxima are plotted for clarity. The signal power ratio
+    $\Dstep{}$ bin increments. The signal power ratio
     between components is indicated with colours and the corresponding ratio in decibels is indicated in the
@@
 
+\subsection{Signals with single component}
+
 To compare the average estimation error variance with the
@@
 
-\begin{tikzpicture}[node distance=2cm]
-
-    \node (start) [process] {Synthesize $K_{2}$ single-component signals};
-    \node (modulate) [process, below of=start] {Modulate down so peak bin is at frequency 0 for all signals};
-    \node (setd) [process, below of=modulate] {Set $d=0$};
-    \node (choosepair) [process, below of=setd] {Choose pair of signals};
-    \node (scaleone) [process, below of=choosepair] {Scale one in the pair to give desired power and peak bin according to $d$};
-    \node (addpair) [process, below of=scaleone] {Add pair together};
-    \node (tryestimate1) [process, below of=addpair] {Try estimating parameters of component with atoms at bins $\{-1,0,1\}$};
-    \node (tryestimate2) [process, below of=tryestimate1] {Try estimating parameters of component with atoms at bins $\{\hat{d}-1,\hat{d},\hat{d}+1\}$};
-    \node (sumerrs) [process, below of=tryestimate2] {Sum estimation errors of
+\begin{figure}[H]
+    \centering
+            \begin{tikzpicture}[node distance=0.25cm]
+                \node (start) [process] at (0,0) {Synthesize $K_{2}$ single-component signals};
+                \node (modulate) [process, below = of start] {Modulate so that peak bin is at frequency 0 for all signals};
+                \node (setd) [process, below = of modulate] {Set $d=0$};
+                \node (choosepair) [process, below = of setd] {Choose
+                    $K_{2}(K_{2}-1)$ pairs of signals};
+                \node (dum1) [emptybox, right = of choosepair] {};
+                \node (scaleone) [process, below = of choosepair] {Scale one in
+                each pair to give desired power and modulate to peak bin according to $d$};
+                \node (addpair) [process, below = of scaleone] {Add each pair together};
+                \node (tryestimate1) [process, below = of addpair] {For each
+                pair, try
+                estimating parameters of unmodulated component with atoms at bins $\{-1,0,1\}$};
+                \node (tryestimate2) [process, below = of tryestimate1] {For
+                each pair, try
+                estimating parameters of modulated component with atoms at bins $\{d-1,d,d+1\}$};
+                \node (sumerrs) [process, below = of tryestimate2] {Sum estimation errors of
                 each parameter and divide by $K_{2}(K_{2}-1)$};
-    \node (incd) [process, below of=sumerrs] {Increment $d$ by $\Dstep{}$ unless $d=\Doffset$};
+                \node (incd) [process, below = of sumerrs] {Increment $d$ by
+                $\Delta_{d}$};
+                \node (dum2) [emptybox, right = of incd] {};
+                \node (dum3) [emptybox, below = of incd] {};
+                \node (dum3b) [emptybox, left = of incd] {};
+                \node (dum4) [emptybox] at (dum3b |- dum3) {};
+%                \node let \p{dum3b}=(dum3b), \p{dum3}=(dum3) in (dum4) [emptybox] at (\x{dum3b},\y{dum3}) {};
+                \node (dum5) [emptybox, left = of setd] {};
 
@@
                 \draw [arrow] (sumerrs) -- (incd);
-    \draw [arrow] (incd) -- node[anchor=east,above]{} (choosepair);
+                \draw [noarrow] (incd) -- (dum2.center);
+                \draw [noarrow] (dum2.center) -- node [anchor=west,text
+                width=2cm,minimum width=3cm] {If $d < D$} (dum1.center) ;
+                \draw [arrow]   (dum1.center) -- (choosepair);
 
+                \draw [noarrow] (incd) -- (dum3.center);
+                \draw [noarrow] (dum3.center) -- (dum4.center);
+                \draw [noarrow] (dum4.center) -- node [anchor=east,text width=2cm,minimum width=2cm] {If
+                signal power ratios remaining} (dum5.center);
+                \draw [arrow] (dum5.center) -- (setd);
             \end{tikzpicture}
+    \caption{The evaluation procedure for 2-component
+    signals.\label{fig:2cevalflowchart}}
+\end{figure}
+
+\subsection{Signals with 2 components}
 
@@
 determined for each unmixed chirp and the chirp was modulated by $\exp(-2\pi
-\frac{r^{\ast} n}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to move this maximum
+\frac{r^{\ast} n}{N}j)$ for $0 \leq n < N$ in order to move this maximum
 to $r=0$. Then for each desired difference $d$, with $0 \leq d < D$, two unique
 chirps were selected from $\mathcal{C}$ and one chirp was modulated by
-$\exp(2\pi \frac{n d}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to give the
+$\exp(2\pi \frac{n d}{N}j)$ for $0 \leq n < N$ in order to give the
 desired difference between maxima. This component was also scaled by a constant
 to give a desired signal power ratio with the other component (the power ratios
-tested were 0 dB and -30 dB). Because the estimation must use valid atom
-indices, $d$ was rounded to the nearest integer $\hat{d}$. The parameters of
-both components were estimated using the bins surrounding $r=0$ and $r=\hat{d}$ for
-each component respectively and the squared estimation error for each parameter
-was summed and divided by $K_{2}(K_{2}-1)$ (the number of choices of two unique
-components) to give the averaged squared estimation error for each parameter at
-each difference $d$.
+tested were 0 dB and -30 dB). As we assume perfect peak-atom selection for this
+evaluation no inner-product maximizing $r^{\ast}$ is chosen, rather atoms with
+angular frequencies $\omega=2\pi\frac{\hat{d}}{N}$ for $\hat{d} \in
+\{d-1,d,d+1\}$ in Eq.~\ref{eq:fourieratom} (again, $R=3$) were chosen to carry
+out the estimation. $d$ was incremented by $\Delta_{d} = \Dstep{}$ and so
+$\hat{d}$ was not generally integral valued in this case. The parameters of the
+unmodulated component were estimated using angular frequencies
+$\omega=2\pi\frac{\hat{d}}{N}$ for $\hat{d} \in\{-1,0,1\}$ in
+Eq.~\ref{eq:fourieratom}. The squared
+estimation error for each parameter was summed and divided by $K_{2}(K_{2}-1)$
+(the number of choices of two unique components) to give the averaged squared
+estimation error for each parameter at each difference $d$. The procedure is
+summarized in Fig.~\ref{fig:2cevalflowchart}.
 
@@
 are minimized while remaining everywhere once-differentiable: a requirement to
-generate valid atoms for the DDM. These windows were shown to improve parameter
-estimation of $P=1$ component in noise and $P=2$ components in mixture without
+generate valid atoms for the DDM. These windows were shown to only improve parameter
+estimation of $P=1$ component with argument-polynomial of order $Q=2$ in low
+amounts of noise. However, for $P=2$ components of the same order in mixture without
 noise, granted the components
 exhibited reasonable separation in frequency between the atoms for which the
-inner product was maximized.
+inner product was maximized, these new windows substantially improved the
+estimation of all but the first argument-polynomial coefficient.
 

### 2017-06-11 comp_offset_chirp_est_err.py

@@ -11,6 +11,7 @@ plt.rc('text',usetex=True)
 plt.rc('font',**ddm.FONT_OPT['dafx'])
 
 show_plots=False
+localmax=False
 
 #warnings.simplefilter('error','RuntimeWarning')
 
@@ -93,7 +94,7 @@ for w in wins:
                     x=c1.x+c2_.x
                     try:
                         errs_1,params_1=ddm.p2_1_3_est(x,c1,0,w,F_s,R)
-                        errs_2,params_2=ddm.p2_1_3_est(x,c2_,np.round(d),w,F_s,R)
+                        errs_2,params_2=ddm.p2_1_3_est(x,c2_,d,w,F_s,R)
                     except TypeError:
                         nlsqerrs += 1
                         continue
@@ -145,7 +146,11 @@ for w,ls,lab in zip(wins,line_stys,labels):
             diffs_min = np.min(errs[w][s]['diffs_log'])
         plt.figure(2)
         for plt_i,param_name in enumerate(['a0','a1','a2']):
-            plotme,msk=ddm.localmax(errs[w][s]['diffs_params'][param_name])
+            if (localmax):
+                plotme,msk=ddm.localmax(errs[w][s]['diffs_params'][param_name])
+            else:
+                plotme,msk=(errs[w][s]['diffs_params'][param_name],
+                        np.arange(len(errs[w][s]['diffs_params'][param_name])))
             axs[plt_i,0].plot(diffs[msk],
                 np.log10(plotme),c=clr,ls=ls,label=lab + ' $%d$ dB' % (s,))
             if np.max(plotme) > diffs_max2:
@@ -153,7 +158,11 @@ for w,ls,lab in zip(wins,line_stys,labels):
             if np.min(plotme) < diffs_min2:
                 diffs_min2 = np.min(plotme)
         for plt_i,param_name in enumerate(['b0','b1','b2']):
-            plotme,msk=ddm.localmax(errs[w][s]['diffs_params'][param_name])
+            if (localmax):
+                plotme,msk=ddm.localmax(errs[w][s]['diffs_params'][param_name])
+            else:
+                plotme,msk=(errs[w][s]['diffs_params'][param_name],
+                        np.arange(len(errs[w][s]['diffs_params'][param_name])))
             axs[plt_i,1].plot(diffs[msk],
                 np.log10(plotme),c=clr,ls=ls,label=lab + ' $%d$ dB' % (s,))
             if np.max(plotme) > diffs_max2:

### 2017-06-11 search_dpw_bw_m.py

@@ -165,6 +165,7 @@ for fignum in xrange(n_figs):
     axs[fignum].set_xlabel(fig_xlabels[fignum])
     axs[fignum].set_ylabel(fig_ylabels[fignum])
     axs[fignum].set_xscale(fig_xscales[fignum],**fig_xscales_kwargs[fignum])
+    axs[fignum].grid(ls='dotted')
 
 axs[1].legend(fontsize=10,handles=[leg_nuttall,leg_prolate,leg_aprx])
 figs.set_size_inches(10,4)

### 2017-08-28 paper/paper.tex
Working on poster

@@
-% Template LaTeX file for DAFx-17 papers
-%
-% To generate the correct references using BibTeX, run
-%     latex, bibtex, latex, latex
-%
-% 1) Please compile using latex or pdflatex.
-% 2) If using pdflatex, you need your figures in a file format other than eps! e.g. png or jpg is working
-% 3) Please use "paperftitle" and "pdfauthor" definitions below
-
-%------------------------------------------------------------------------------------------
-%  !  !  !  !  !  !  !  !  !  !  !  ! user defined variables  !  !  !  !  !  !  !  !  !  !  !  !  !  !
-% Please use these commands to define title and author(s) of the paper:
 \def\papertitle{On the design and use of once-differentiable high dynamic
@@
 
-%-------------SINGLE-AUTHOR HEADER STARTS (uncomment below if your paper has a single author)-----------------------
-%\affiliation{
-%\paperauthorA \,\sthanks{Thanks to the predecessors for the templates}}
-%{\href{http://www.acoustics.ed.ac.uk}{Acoustics and Audio Group,} \\ University of Edinburgh\\ Edinburgh, UK\\
-%{\tt \href{mailto:dafx17@ed.ac.uk}{dafx17@ed.ac.uk}}
-%}
-%-----------------------------------SINGLE-AUTHOR HEADER ENDS------------------------------------------------------
-
-%---------------TWO-AUTHOR HEADER STARTS (uncomment below if your paper has two authors)-----------------------
 \twoaffiliations{
 \paperauthorA \,}
-{\href{http://www.cirmmt.org/}{%Sound Processing and Control Laboratory
-        SPCL %
-        \sthanks{Sound Processing and Control Laboratory} \\%
-%        Centre for Interdisciplinary Research in Music Media and Technology
-        CIRMMT %
-        \sthanks{Centre for Interdisciplinary Research in Music Media and Technology}%
-    }
-\\ McGill University %
-\\ Montreal, Quebec, Canada \\
+{\href{https://mt.music.mcgill.ca/spcl}{SPCL\sthanks{Sound Processing and Control Laboratory}} \\ McGill University\\ Montreal, Quebec, Canada\\
 {\tt \href{mailto:nicholas.esterer@mail.mcgill.ca}{nicholas.esterer@mail.mcgill.ca}}
@@
 {\paperauthorB \,}
-{\href{http://www.cirmmt.org/}{%Sound Processing and Control Laboratory
-        SPCL \\%
-%        \sthanks{Sound Processing and Control Laboratory} \\%
-%        Centre for Interdisciplinary Research in Music Media and Technology
-        CIRMMT %
-%        \sthanks{Centre for Interdisciplinary Research in Music Media and Technology}%
-    } %
-\\ McGill University %
-\\ Montreal, Quebec, Canada \\
-\tt %
-\href{mailto:philippe.depalle@mcgill.ca}{philippe.depalle@mcgill.ca}}
+{\href{https://mt.music.mcgill.ca/spcl}{SPCL} \\ McGill University\\ Montreal,
+Quebec, Canada\\ {\tt \href{mailto:philippe.depalle@mcgill.ca}{philippe.depalle@mcgill.ca}}
+}
 
@@
 \begin{equation}
-    \label{eq:polyphaseexpmix}
     x(t) = \sum_{p=1}^{P} x_{p}(t) + \eta(t)
@@
 \begin{equation}
+    \label{eq:polyphaseexpmix}
     x_{p}(t) = \exp(a_{p,0} + \sum_{q=1}^{Q} a_{p,q} t^q)
@@
 we evaluate the performance of various once-differentiable windows in estimating
-the $a_{q}$.
+the parameters $a_{q}$.
 
@@
 
-Estimating coefficients $a_{q}$, ${1 < q \leq Q}$,
-simply requires $R$ atoms with $R \geq Q$ to solve the linear system of
-equations
+Estimating coefficients $a_{q}$, ${1 < q \leq Q}$, simply requires $R$ atoms
+$\psi_{r}$ with $R \geq Q$ to solve the linear system of equations
 \begin{equation}
@@
     \sum_{q=1}^{Q} q a_{p,q} 
-    \left\langle \mathcal{T}^{q-1} x_i , \overline{\psi} \right\rangle
-    + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle \right)
+    \left\langle \mathcal{T}^{q-1} x_{p} , \overline{\psi} \right\rangle
+    + \left\langle x_{p}, \frac{d\overline{\psi}}{dt} \right\rangle \right)
 \end{multline}
 %
-From this we see if $\left\langle \mathcal{T}^{q-1} x_i , \overline{\psi}_{r}
-\right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
-are small for all but $p = p^{\ast}$ and a subset of $R$ atoms, we
-can simply estimate the parameters $a_{p^{\ast},q}$ using
+From this we see if $\left\langle \mathcal{T}^{q-1} x_{p} , \overline{\psi}_{r}
+\right\rangle$ and $\left\langle x_{p}, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
+are small for all but $p = p^{\ast}$ and a subset of $R$ atoms\footnote{%
+The notation $x^{\ast}$ will mean the value of the argument $x$ maximizing or minimizing some
+function.
+}%
+, we can simply estimate the parameters $a_{p^{\ast},q}$ using
 \begin{equation}
@@
 the DFT on a signal $x$ that is properly sampled
-and so can be evaluated at a finite number of time-points $nT$ with $n \in [0,N-1]$ and
+and so can be evaluated at a finite number of times $nT$ with $n \in [0,N-1]$ and
 $T$ the sample period in seconds. In this way, the chosen atoms $\psi_{\omega}(t)$ 
@@
 %
-Defining $N = \frac{L_{t}}{T}$ and angular frequency at bin $r$ as $\omega = 2
+Defining $N = \frac{L_{t}}{T}$ and angular frequency at bin $r$ as $\omega_{r} = 2
 \pi \frac{r}{N}$, the approximate inner product is then
@@
 \begin{equation}
-    \tilde{w}(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
+    \tilde{w}(n) = \sum_{m=0}^{M-1} b_{m} \cos (2 \pi m \frac{n}{N})
 \mathcal{R}(\frac{n}{N})
@@
 \begin{equation}
-\sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
+\sum_{m=0}^{M-1} b_{m} \cos ( \pm \pi m ) = 0
 \end{equation}
@@
 highest sidelobe \cite{rabiner1970approach}, a once-differentiable approximation
-to an existing window $w$ is desired. To do this, we choose the $b_{k}$ so that
+to an existing window $w$ is desired. To do this, we choose the $b_{m}$ so that
 the window $\tilde{w}$'s squared approximation error to $w$ is minimized while having
-$\tilde{w}(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{ b^{\ast}_{k} \}$ to the
+$\tilde{w}(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{ b^{\ast}_{m} \}$ to the
 mathematical program
@@
     \sum_{n=0}^{N-1} ( w(n) 
-        - \sum_{k=0}^{M-1} b_{k} \cos(2 \pi k \frac{n}{N}))^{2}
+        - \sum_{m=0}^{M-1} b_{m} \cos(2 \pi m \frac{n}{N}))^{2}
 \end{equation}
@@
     \text{subject to} \\
-    \sum_{k=0}^{M-1} b_{k} \cos(\pi k ) = 0
+    \sum_{m=0}^{M-1} b_{m} \cos(\pi m ) = 0
 \end{equation}
@@
 It is seen that a lower highest sidelobe level than the Nuttall and Prolate
-windows is obtained by slightly sacrificing the narrowness of the main lobe. Furthermore in
-Fig.~\ref{fig:dpw} we observe that the falloff of the window is 18 dB per octave
-because it is once-differentiable at all points in its domain.
+windows is obtained by slightly sacrificing the narrowness of the main lobe.
+More importantly, in Fig.~\ref{fig:dpw} we observe that the falloff of the
+window is 18 dB per octave because it is once-differentiable at all points in
+its domain.
 
@@
             \begin{tikzpicture}[node distance=0.25cm]
-                \node (start) [process] at (0,0) {Synthesize $K_{2}$ single-component signals};
-                \node (modulate) [process, below = of start] {Modulate so that peak bin is at frequency 0 for all signals};
-                \node (setd) [process, below = of modulate] {Set $d=0$};
+                \node (start) [process] at (0,0) {Synthesize $K_{2}$
+                single-component signals.};
+                \node (modulate) [process, below = of start] {Modulate so that
+                peak bin is at frequency 0 for all signals.};
+                \node (setd) [process, below = of modulate] {Set $d=0$.};
                 \node (choosepair) [process, below = of setd] {Choose
-                    $K_{2}(K_{2}-1)$ pairs of signals};
+                    $K_{2}(K_{2}-1)$ pairs of signals.};
                 \node (dum1) [emptybox, right = of choosepair] {};
                 \node (scaleone) [process, below = of choosepair] {Scale one in
-                each pair to give desired power and modulate to peak bin according to $d$};
-                \node (addpair) [process, below = of scaleone] {Add each pair together};
+                each pair to give desired power from $\mathcal{S}$ and modulate to peak bin
+                according to $d$.};
+                \node (addpair) [process, below = of scaleone] {Add each signal
+                pair together.};
                 \node (tryestimate1) [process, below = of addpair] {For each
                 pair, try
-                estimating parameters of unmodulated component with atoms at bins $\{-1,0,1\}$};
+                estimating parameters of unmodulated component with atoms at
+                bins $\{-1,0,1\}$.};
                 \node (tryestimate2) [process, below = of tryestimate1] {For
                 each pair, try
-                estimating parameters of modulated component with atoms at bins $\{d-1,d,d+1\}$};
+                estimating parameters of modulated component with atoms at bins
+                $\{d-1,d,d+1\}$.};
                 \node (sumerrs) [process, below = of tryestimate2] {Sum estimation errors of
-                each parameter and divide by $K_{2}(K_{2}-1)$};
+                each parameter and divide by $K_{2}(K_{2}-1)$.};
                 \node (incd) [process, below = of sumerrs] {Increment $d$ by
-                $\Delta_{d}$};
+                $\Delta_{d}$.};
                 \node (dum2) [emptybox, right = of incd] {};
@@
                 \draw [arrow] (sumerrs) -- (incd);
-                \draw [noarrow] (incd) -- (dum2.center);
-                \draw [noarrow] (dum2.center) -- node [anchor=west,text
-                width=2cm,minimum width=3cm] {If $d < D$} (dum1.center) ;
-                \draw [arrow]   (dum1.center) -- (choosepair);
 
-                \draw [noarrow] (incd) -- (dum3.center);
-                \draw [noarrow] (dum3.center) -- (dum4.center);
-                \draw [noarrow] (dum4.center) -- node [anchor=east,text width=2cm,minimum width=2cm] {If
-                signal power ratios remaining} (dum5.center);
-                \draw [arrow] (dum5.center) -- (setd);
+                \draw [arrow] (incd) -- (dum2.center) -- (dum2.center) -- 
+                    node [anchor=west,text width=2cm,minimum width=3cm] {If $d <
+                    D$.} (dum1.center) 
+                    -- (dum1.center) -- (choosepair);
+
+                \draw [arrow] (incd) -- (dum3.center) -- (dum3.center) --
+                (dum4.center) -- (dum4.center) -- 
+                node [anchor=east,text width=2cm,minimum width=2cm]
+                {If signal power ratios in $\mathcal{S}$ remaining to be
+                evaluated.} (dum5.center) --
+                 (dum5.center) -- (setd);
+
             \end{tikzpicture}
@@
 Test signals were obtained by choosing a pair of unique components from this set
-and modulating one to give the desired difference.  This was carried out as
+and modulating one to give the desired frequency and amplitude difference.  This was carried out as
 follows: the atom $r^{\ast}$ for which the inner product was maximized was
@@
 \frac{r^{\ast} n}{N}j)$ for $0 \leq n < N$ in order to move this maximum
-to $r=0$. Then for each desired difference $d$, with $0 \leq d < D$, two unique
+to $r=0$. Then for each desired difference $d$, with $0 \leq d < D$ (for the
+evaluation $D = \Doffset{}$), two unique
 chirps were selected from $\mathcal{C}$ and one chirp was modulated by
@@
 desired difference between maxima. This component was also scaled by a constant
-to give a desired signal power ratio with the other component (the power ratios
-tested were 0 dB and -30 dB). As we assume perfect peak-atom selection for this
+to give a desired signal power ratio from set $\mathcal{S}$ with the other component (the power ratios
+$\mathcal{S}$ tested were 0 dB and -30 dB). As we assume perfect peak-atom selection for this
 evaluation no inner-product maximizing $r^{\ast}$ is chosen, rather atoms with
@@
 Eq.~$\ref{eq:polyphaseexp}$ is influenced by main-lobe width and sidelobe
-height. In Fig.~\ref{fig:mixwincomp} we see that there is generally less
+height and slope. In Fig.~\ref{fig:mixwincomp} we see that there is generally less
 estimation error for components having similar signal power. This is to be
@@
 
-%\section{Acknowledgments}
+\section{Acknowledgments}
+This work was partially supported by grant from the Natural Sciences and Engineering Research Council of Canada awarded to Philippe Depalle (RGPIN-262808-2012).
 

### 2017-08-28 poster/sciposter/dafxposter/dafx-poster-reduced.tex
Working on poster

--- 2017-08-28 paper/paper.tex
@@
 \def\paperauthorB{Philippe Depalle}
+\documentclass[plainsections,landscape]{sciposter}
 
-% Authors' affiliations have to be set below
+\usepackage{epsfig}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{multicol}
+\usepackage{tcolorbox}
+%\usepackage{fancybullets}
+%\usepackage{amsmath,amssymb,amsfonts,amsthm}
+%\usepackage{euscript}
+%\usepackage[latin1]{inputenc}
+%\usepackage[T1]{fontenc}
+%\usepackage{ifpdf}
+%
+%\usepackage[english]{babel}
+%\usepackage{caption}
+%\usepackage{subfig} % or can use subcaption package
+%\usepackage{color}
+%\usepackage{cite}
+%\usepackage{float}
+%
+%\usepackage{hyphenat}
+%\hyphenation{spher-oidal}
+%%\hyphenation{amp-li-tude}
+%%\hyphenation{mod-u-lat-ed}
+%
+%\usepackage{times}
 
-%------------------------------------------------------------------------------------------
-\documentclass[twoside,a4paper]{article}
-\usepackage{dafx_17}
-\usepackage{amsmath,amssymb,amsfonts,amsthm}
-\usepackage{euscript}
-\usepackage[latin1]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{ifpdf}
+\newtheorem{Def}{Definition}
 
-\usepackage[english]{babel}
-\usepackage{caption}
-\usepackage{subfig} % or can use subcaption package
-\usepackage{color}
-\usepackage{cite}
-\usepackage{float}
+%\definecolor{BoxCol}{rgb}{0.9,0.9,0.9}
+% uncomment for grey background to \section boxes 
+% for use with default option boxedsections
 
-\setcounter{page}{1}
-\ninept
+%\definecolor{BoxCol}{rgb}{0.9,0.9,1}
+% uncomment for light blue background to \section boxes 
+% for use with default option boxedsections
 
-\usepackage{hyphenat}
-\hyphenation{spher-oidal}
-%\hyphenation{amp-li-tude}
-%\hyphenation{mod-u-lat-ed}
-
-\usepackage{times}
-% Saves a lot of ouptut space in PDF... after conversion with the distiller
-% Delete if you cannot get PS fonts working on your system.
-
-% pdf-tex settings: detect automatically if run by latex or pdflatex
-\newif\ifpdf
-\ifx\pdfoutput\relax
-\else
-   \ifcase\pdfoutput
-      \pdffalse
-   \else
-      \pdftrue
-\fi
-
-\ifpdf % compiling with pdflatex
-  \usepackage[pdftex,
-    pdftitle={\papertitle},
-    pdfauthor={\paperauthorA, \paperauthorB},
-    colorlinks=false, % links are activated as colror boxes instead of color text
-    bookmarksnumbered, % use section numbers with bookmarks
-    pdfstartview=XYZ % start with zoom=100% instead of full screen; especially useful if working with a big screen :-)
-  ]{hyperref}
-  \pdfcompresslevel=9
-  \usepackage[pdftex]{graphicx}
-  \usepackage[figure,table]{hypcap}
-\else % compiling with latex
-  \usepackage[dvips]{epsfig,graphicx}
-  \usepackage[dvips,
-    colorlinks=false, % no color links
-    bookmarksnumbered, % use section numbers with bookmarks
-    pdfstartview=XYZ % start with zoom=100% instead of full screen
-  ]{hyperref}
-  % hyperrefs are active in the pdf file after conversion
-  \usepackage[figure,table]{hypcap}
-\fi
+%\definecolor{SectionCol}{rgb}{0,0,0.5}
+% uncomment for dark blue \section text
 
@@
 \tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=0cm, text
-centered, draw=black, text width=3cm]
+centered, draw=black, text width=0.3\columnwidth]
 \tikzstyle{emptybox} = []
@@
 
-\twoaffiliations{
-\paperauthorA \,}
-{\href{https://mt.music.mcgill.ca/spcl}{SPCL\sthanks{Sound Processing and Control Laboratory}} \\ McGill University\\ Montreal, Quebec, Canada\\
-{\tt \href{mailto:nicholas.esterer@mail.mcgill.ca}{nicholas.esterer@mail.mcgill.ca}}
-}
-{\paperauthorB \,}
-{\href{https://mt.music.mcgill.ca/spcl}{SPCL} \\ McGill University\\ Montreal,
-Quebec, Canada\\ {\tt \href{mailto:philippe.depalle@mcgill.ca}{philippe.depalle@mcgill.ca}}
-}
+% Note: only give author names, not institute
+\author{\paperauthorA{} and \paperauthorB{}}
+
+% insert correct institute name
+\institute{Sound Processing and Control Laboratory (SPCL) at McGill University}
+
+\email{nicholas.esterer@mail.mcgill.ca, philippe.depalle@mcgill.ca}  % shows author email address below institute
 
@@
 \begin{document}
-% more pdf-tex settings:
-\ifpdf % used graphic file format for pdflatex
-  \DeclareGraphicsExtensions{.png,.jpg,.pdf}
-\else  % used graphic file format for latex
-  \DeclareGraphicsExtensions{.eps}
-\fi
+%define conference poster is presented at (appears as footer)
+
+\conference{{\em{\small{The 20$^{\text{\itshape th}}$ International Conference on Digital Audio Effects (DAFx-17), Edinburgh, UK, September 5--9, 2017}}}}
+
+%\LEFTSIDEfootlogo  
+% Uncomment to put footer logo on left side, and 
+% conference name on right side of footer
+
+% Some examples of caption control (remove % to check result)
+
+%\renewcommand{\algorithmname}{Algoritme} % for Dutch
+
+%\renewcommand{\mastercapstartstyle}[1]{\textit{\textbf{#1}}}
+%\renewcommand{\algcapstartstyle}[1]{\textsc{\textbf{#1}}}
+%\renewcommand{\algcapbodystyle}{\bfseries}
+%\renewcommand{\thealgorithm}{\Roman{algorithm}}
 
@@
 
+%%% Begin of Multicols-Enviroment
+\setlength{\columnseprule}{0pt}
+\begin{multicols}{3}
+
+%%% Abstract
 \begin{abstract}
@@
     once-differentiable approximations to windows is presented and the accuracy
-    of these windows in estimating the parameters of sinusoidal chirps in mixture is
-    evaluated.
+    of these windows in estimating the parameters of sinusoidal chirps in
+    mixture is evaluated.
 \end{abstract}
 
+%%% Introduction
 \section{Introduction}
 \label{sec:intro}
-Additive synthesis using a sum of sinusoids plus noise is a powerful model for
-representing audio \cite{serra1989system}, allowing for the easy implementation
-of many manipulations such as time-stretching \cite{marchand2004enhanced} and
-timbre-morphing \cite{haken2007beyond}.
-%
-In these papers,
-\cite{serra1989system,marchand2004enhanced,haken2007beyond} the
-phase evolution of the sinusoid is assumed linear over the analysis frame, only
-the phase and frequency of the sinusoids at these analysis points are used to
-fit a plausible phase function after some the analysis points are connected to
-form a partial \cite{mcaulay1986speech}. 
-%
+
 Recently, there has
-been interest in using higher-order phase functions \cite{xuepiecewise} as the estimation of
-their parameters has been made possible by a new set of techniques of only
-moderate computational complexity using signal derivatives \cite{hamilton2012unified}.
-%
-The use
-of higher-order phase models allows for accurate description of highly modulated
-signals, for
-example in the analysis of birdsong \cite{stowell2013improved}.
-%
-The frequency
-modulation information has also been used in the
-regularization of mathematical programs for audio source separation \cite{creager2016musicalsource}.
+been interest in using higher-order phase functions for the argument of sinusoidal
+    functions \cite{xuepiecewise} as the estimation of
+their parameters has been made possible by a set of techniques 
+using signal derivatives \cite{hamilton2012unified}.
 
-The sinusoidal model approximating signal $s$ typically considered is
-%
-\begin{equation}
-    \label{eq:polyphaseexp}
-    \tilde{s}(t) = \exp(a_0 + \sum_{q=1}^{Q} a_{q} t^q) + \eta(t)
-\end{equation}
-where $\tilde{s}$ is the approximating signal, $t$ the variable of time, the
-$a_{q} \in \mathbb{C}$ coefficients of the argument's polynomial, and $\eta(t)$
-white Gaussian noise.
-%
-Although this technique can be extended to describe a single sinusoid of
-arbitrary complexity simply by increasing $Q$, it remains essential to consider
-signals featuring a sum of $P$ such components, whether they represent the harmonic structure of a musical sound or the union of partials resulting from a mixture of multiple signal sources (e.g., recordings of multiple speakers or performers),  i.e.,
+For comparison with previous research on the DDM, we consider the estimation -- via the DDM -- of the parameters of a
+    parabolic phase function for which the imaginary parts of the parameters
+    represent the initial phase, frequency and frequency slope. The real parts
+    of the parameters represent the initial amplitude, amplitude slope and
+    amplitude curvature.
+
+The DDM requires a set of atoms that are once-differentiable everywhere in
+    the time-domain from which the parameters are estimated. We
+    show that on a mixture of sinusoids, accurate estimation for each sinusoid
+    can be obtained under a single-component
+assumption when components have roughly disjoint sets of atoms for which their
+inner products take on large values.
+
+Encouraging disjointedness amounts to designing atoms whose Fourier
+    transform exhibits low side-lobes under the additional constraint that
+    the atoms be everywhere once-differentiable. We show how to design atoms
+    with this latter property based on the shapes of ideal windows.
+
+\section{Estimating the \lowercase{$a_{p,q}$} of $P$ components}
+\begin{tcolorbox}
+    \begin{multicols}{2}
+The model for signal $x$ is
 %
@@
 %
-As regards the design and evaluation of signal-derivatives analysis techniques,
-previous work has generally assumed signals containing a single component, i.e.,
-$P$ = 1 or assumed the influence of other components to be negligible. Later we
-will refine when this assumption can be made. In \cite{hamilton2012comparisons}
-the authors provide a comprehensive evaluation of various signal-derivatives
-analysis methods applied to a single-component signal. In
-\cite{robel2002estimating} the extent to which two components in mixture can
-corrupt estimations of the frequency slope ($\Im\{a_{0,2}\}$ and
-$\Im\{a_{1,2}\}$) is investigated in the context of the reassignment method, one
-of the signal-derivatives techniques, but the corruption of the other
-parameters is not considered.
+and $\eta$ Gaussian-distributed white noise. 
+    \end{multicols}
+\end{tcolorbox}
 
-In this paper, we revisit the quality of signal-derivatives estimation of
-\textit{all} the $a_{q}$ when analyzing a \textit{mixture} of components. We focus on
-the DDM \cite{betser2009sinusoidal} analysis method for its convenience as it
-can simply be considered as an atomic decomposition (see
-Sec.~\ref{sec:estimating_aj}), and does not require computing derivatives
-of the signal to be analysed.
+\begin{tcolorbox}
+\begin{multicols}{2}
+Applying the DDM to a mixture of $P$ componentes, we obtain%
+\footnote{
+$\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)$
 
-The DDM does, however, require a once-differentiable analysis window. As we are
-interested in windows with lower sidelobes in order to better estimate
-parameters of sinusoidal chirp signals in mixture, we seek windows that
-combine these two properties. For this, a technique to design
-once-differentiable approximations to arbitrary symmetrical windows is proposed
-and presented along with a design example for a high-performance window. Finally
-we evaluate the performance of various once-differentiable windows in estimating
-the parameters $a_{q}$.
-
-\section{Estimating the parameters \lowercase{$a_{q}$}}
-\label{sec:estimating_aj}
-We will now show briefly how the DDM can be used to estimate the $a_{q}$. Based on
-the theory of distributions \cite{schwartz1959theorie}, the DDM
-makes use of ``test
-functions'' or atoms $\psi$. These atoms must be once differentiable with
-respect to time variable $t$ and be non-zero only on a finite interval
-$[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define the inner product
-%
-\begin{equation}
-    \label{eq:ddm:inner:prod:def}
-    \left\langle x , \psi \right\rangle = 
-    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
-\end{equation}
-%
-and the operator 
-%
-\begin{equation}
-\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
-\end{equation}
-%
-Consider the weighted signal
-%
-\begin{equation}
-    f(t) = x(t) \overline{\psi}(t)
-\end{equation}
-%
-differentiating with respect to $t$ we obtain
-%
-\begin{multline}
-    \label{eq:ddm:weighted:sig:derivative}
-    \frac{df}{dt}(t) = 
-    \frac{dx}{dt}(t)\overline{\psi}(t)
-    + x(t)\frac{d\overline{\psi}}{dt}(t) = \\
-    \left( \sum_{q=1}^{Q} q a_{q} t^{q-1} \right) x(t)\overline{\psi}(t)
-    + x(t)\frac{d\overline{\psi}}{dt}(t)
-\end{multline}
-%
-Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
-$\frac{df}{dt}(t)$ we obtain
-%
-\begin{multline}
-    \int_{-\infty}^{\infty}\frac{df}{dt}(t)dt = \\
-    \sum_{q=1}^{Q} q a_{q} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{q-1} x(t) \overline{\psi}(t) dt
-    + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
-\end{multline}
-%
-or, using the operator $\mathcal{T}^{\alpha}$,
-%
-\begin{equation} 
-    \sum_{q=1}^{Q} q a_{q} 
-    \left\langle \mathcal{T}^{q-1} x , \overline{\psi} \right\rangle
-    = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
-\end{equation}
-%
-
-Estimating coefficients $a_{q}$, ${1 < q \leq Q}$, simply requires $R$ atoms
-$\psi_{r}$ with $R \geq Q$ to solve the linear system of equations
-\begin{equation}
-    \label{eq:ddmsyseq}
-    \sum_{q=1}^{Q} q a_{q} 
-    \left\langle \mathcal{T}^{q-1} x , \overline{\psi}_{r} \right\rangle
-    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dt} \right\rangle
-\end{equation}
-for $1 \leq r \leq R$.
-
-To estimate $a_0$ we rewrite the signal we are analysing as
-\begin{equation}
-    x(t) = \exp(a_0) \gamma(t) + \epsilon (t)
-\end{equation}
-where $\epsilon (t)$ is the error signal, the part of the signal that is not explained
-by our model, and $\gamma (t)$ is the part of the signal
-whose coefficients have already been estimated, i.e.,
-\begin{equation}
-    \gamma(t) = \exp \left( \sum_{q=1}^{Q} a_{q} t^{q} \right)
-\end{equation}
-Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
-\begin{equation}
-    \left\langle x , \gamma \right\rangle
-    =
-    \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
-        \left\langle \epsilon , \gamma \right\rangle
-\end{equation}
-The inner product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
-principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
-depend on $t$, we have
-\begin{equation}
-    \left\langle x , \gamma \right\rangle
-    =
-    \exp(a_0) \left\langle \gamma , \gamma \right\rangle
-\end{equation}
-so we can estimate $a_0$ as
-\begin{equation}
-    \label{eq:ddmesta0}
-    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
-        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
-\end{equation}
-
-As will be seen in subsequent sections, the DDM typically involves taking the
-discrete Fourier transform (DFT) of the signal windowed by both an everywhere once-differentiable function of
-finite support (e.g., the Hann window) and this function's derivative. A small
-subset of atoms corresponding to the peak bins in the DFT are used in
-Eq.~\ref{eq:ddmsyseq} to solve for the parameters $a_{q}$.
-
-\section{Estimating the \lowercase{$a_{p,q}$} of $P$ components}
-
-We examine how the mixture model influences the estimation of the $a_{p,q}$ in
-Eq.~\ref{eq:polyphaseexpmix}.
-Consider a mixture of $P$ components.
-If we define the weighted signal sum
-%
-\begin{equation}
-    g(t) = \sum_{p=1}^{P} x_{p}(t) \overline{\psi}(t) = \sum_{p=1}^{P} f_{p}(t)
-\end{equation}
-%
-and substitute $g$ for $f$ in Eq.~\ref{eq:ddm:weighted:sig:derivative} we obtain
+$\left\langle x , \psi \right\rangle = 
+\int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt$
+}
 %
@@
     \label{eq:mixest}
-    \sum_{p=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}}
-    \frac{df_{p}}{dt}(t)dt =
-    0
-    = \\ 
     \sum_{p=1}^{P} \left(
@@
     + \left\langle x_{p}, \frac{d\overline{\psi}}{dt} \right\rangle \right)
+    \\
+    = 0
 \end{multline}
@@
 \end{equation}
-for $1 \leq r \leq R$. To compute $a_{p^{\ast},0}$ we simply use
+for $1 \leq r \leq R$.
+\end{multicols}
+\end{tcolorbox}
+
+\begin{tcolorbox}
+\begin{multicols}{2}
+To compute $a_{p^{\ast},0}$ we define
 \begin{equation}
@@
 \end{equation}
-in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.
+and estimate $a_0$ as
+\begin{equation}
+    \label{eq:ddmesta0}
+    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
+        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
+\end{equation}
+\end{multicols}
+\end{tcolorbox}
 
@@
 \label{sec:designingatoms}
+\begin{tcolorbox}
+\begin{multicols}{2}
 %
-\begin{figure*}[t]
-    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
-\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
-spectrum characteristics of the continuous 4-term Nuttall window, the digital
-prolate window with $W=0.008$, and the continuous approximation to the digital
-prolate window.}
-\end{figure*}
-%
-In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
-the DFT on a signal $x$ that is properly sampled
-and so can be evaluated at a finite number of times $nT$ with $n \in [0,N-1]$ and
-$T$ the sample period in seconds. In this way, the chosen atoms $\psi_{\omega}(t)$ 
+Canonically, the chosen atoms $\psi_{\omega}(t)$ 
 are the products of the elements of the Fourier basis and an appropriately
@@
 %
-i.e., the definition of the DFT of a windowed signal%
-\footnote{%
-    Notice however that this is an approximation of the inner product and should
-    not be interpreted as yielding the Fourier series coefficients of a properly
-    sampled signal $x$ periodic in $L_{t}$. This means that other
-    evaluations of the inner product that yield more accurate results are
-    possible. For example, the analytic solution is possible if $x$ is assumed
-    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
-    general analytic).  In this case the samples of $x$ are convolved with the
-    appropriate interpolating sinc functions and the integral of this function's
-    product with $\psi$ is evaluated.
-}. %
-The DFT is readily interpreted as a bank of bandpass filters centred at
-normalized frequencies%
-%\footnote{%
-%In this article as in much of the literature on signal processing the index $r$
-%of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
-%\frac{r}{N}$ will be referred to as its bin number.
-%}
-$\frac{r}{N}$ and with frequency response described by the Fourier transform of
-modulated $w$ \cite{allen1977unified}. Therefore choosing $\psi$ amounts to a
-filter design problem under the constraints that the impulse response of the
-filter be differentiable in $t$ and finite. To minimize the influence of all but
-one component, granted the components's energy concentrations are sufficiently
-separated in frequency, we desire impulse responses whose magnitude response
-gives maximum out-of-band rejection or equivalently, windows whose Fourier
-transform exhibits the lowest sidelobes.
-
-In all the publications reviewed on the DDM for this paper, the window used was
-the Hann window which is once-differentiable everywhere in the time-domain. In
-\cite{robel2002estimating}, a publication on the reassignment method, other
-windows than the Hann are considered but these windows must be
-twice-differentiable.  Nuttall \cite{nuttall1981some} has designed windows with
-lower sidelobes than the canonical Hann window which are everywhere at least
-once-differentiable. It is also possible to design approximations to arbitrary
-symmetrical window functions using harmonically related cosines, as is discussed
-in the following section.
+i.e., the definition of the DFT of a windowed signal.
+Therefore choosing $\psi$ amounts to a
+Fourier window design problem minimizing its side-lobes, under the constraint
+that the window be differentiable in $t$ and finite.
+\end{multicols}
+\end{tcolorbox}
 
@@
 %
-\begin{figure*}[ht]
-    \centerline{\includegraphics[width=7in]{{ddm_snr_win_comp}.eps}}
-\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
-    phase sinusoids averaged over $K_{1}=\Ksnr{}$ trials using atoms generated from
-    various windows. \textit{C} is the Cram\'{e}r-Rao
-lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
-Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continuous
-5-cosine-term approximation to a digital prolate window as described in
-Sec.~\ref{sec:designexample}.}
-\end{figure*}
+\newcommand{\imsize}{\columnwidth}
+\begin{figure}
+\begin{center}
+    {\resizebox{\imsize}{!}{\includegraphics{{search_dpw_bw_m}.eps}}}
+\end{center}
+\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
+spectrum characteristics of the continuous 4-term Nuttall window, the digital
+prolate window with $W=0.008$, and the continuous approximation to the digital
+prolate window.}
+\end{figure}
 %
+
+\begin{tcolorbox}
+\begin{multicols}{2}
 A differentiable approximation to a symmetrical window can be designed in a
@@
 at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
-\begin{equation}
-\sum_{m=0}^{M-1} b_{m} \cos ( \pm \pi m ) = 0
-\end{equation}
+$\sum_{m=0}^{M-1} b_{m} \cos ( \pm \pi m ) = 0$.
 
-Rather than design based on an optimality criterion, such as the height of the
-highest sidelobe \cite{rabiner1970approach}, a once-differentiable approximation
-to an existing window $w$ is desired. To do this, we choose the $b_{m}$ so that
+Therefore, we choose the $b_{m}$ so that
 the window $\tilde{w}$'s squared approximation error to $w$ is minimized while having
@@
 \end{equation}
-which can be solved using constrained least-squares; a standard numerical
-linear algebra routine \cite[p.~585]{golub1996matrix}.
+which can be solved using constrained least-squares\cite[p.~585]{golub1996matrix}.
+\end{multicols}
+\end{tcolorbox}
 
-\section{A continuous window design example}
-\label{sec:designexample}
-%
-\begin{figure*}[ht]
-    \centerline{\includegraphics[width=7in]{{comp_offset_chirp_est_err_params}.eps}}
-\caption{\label{fig:mixwincomp} The mean squared estimation error for each
-    parameter in an analysis of two components in mixture. A set of
-    $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
-    maximum bin differences $0 \leq d < \Doffset{}$, with $d$ varied in
-    $\Dstep{}$ bin increments. The signal power ratio
-    between components is indicated with colours and the corresponding ratio in decibels is indicated in the
-    plot legend. The names indicate the windows used to generate the atoms for
-    estimation: \textit{N3} and \textit{N4} are the 3- and 4-cosine-term
-    continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
-is the continuous 5-cosine-term approximation to a digital prolate window as
-described in Sec.~\ref{sec:designexample}.}
-\end{figure*}
-%
-As a design example we show how to create a continuous approximation of a digital
-prolate spheroidal window.
-
-Digital prolate spheroidal windows are a parametric approximation to functions
-whose Fourier transform's energy is maximized in a given bandwidth
-\cite{slepian1978prolate}. These can be tuned to have extremely low sidelobes,
-at the expense of main-lobe width.  Differentiation of these window functions
-may be possible but is not as straightforward as differentiation of the
-sum-of-cosine windows above. Furthermore, the windows do not generally have
-end-points equal to 0. In the following we will demonstrate how to approximate
-a digital prolate spheroidal window with one that is everywhere at least
-once-differentiable.
+\begin{tcolorbox}
+\begin{multicols}{2}
+Using this technique, we designed a continuous approximation to a digital prolate
+spheroidal window of length $N=512$ and $W=0.008$. The coefficients
+are described in Table~\ref{tab:contprolate} and a comparison with other
+windows is shown in Figure~\ref{fig:dpw}.
 
@@
     \caption{The coefficients of the once-differentiable approximation to a digital prolate
-    window designed in Sec.~\ref{sec:designexample}.
+    window.
     \label{tab:contprolate}}
@@
             $b_4$ & $ = $ & 2.071 $\times 10^{-3}$ 
-            %3.128258203861262743 $\times 10^{-1}$ &
-            %4.655346501582137142 $\times 10^{-1}$ &
-            %1.851027605614040672 $\times 10^{-1}$ &
-            %3.446534984178639682 $\times 10^{-2}$ &
-            %2.071419052469766937 $\times 10^{-3}$ \\
         \end{tabular}
@@
 \end{table}%
+\end{multicols}
+\end{tcolorbox}
 
-In \cite{verma1996digital} it was shown how to construct digital prolate
-spheroidal windows under parameters $N$, the window length in samples, and a
-parameter $W$ choosing the (normalized) frequency range in which the proportion
-of the main lobe's energy is to be maximized. We chose $N=512$ based on the
-window length chosen in \cite{betser2009sinusoidal} for ease of comparison. Its
-$W$ parameter's value was chosen by synthesizing windows with $W$ ranging
-between $0.005$ and $0.010$ at a resolution of $0.001$. The window with the
-closest 3 dB bandwidth to the 4-term Nuttall window was obtained with $W=0.008$.
-Its magnitude response is shown in Fig.~\ref{fig:dpw}. We see that this window's
-asymptotic falloff is 6 dB per octave and therefore has a discontinuity
-somewhere in its domain \cite{nuttall1981some}.
+\section{The performance of improved windows on signals with 2 components}
 
-We designed an approximate
-window using Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and
-$N/8$ to find the best approximation to the digital prolate window's main lobe
-using a small number of cosines. The $M$ giving the best approximation was $5$.
-The magnitude response of the approximation is shown in Fig.~\ref{fig:dpw} and
-its coefficients are listed in Tab.~\ref{tab:contprolate}; the temporal shape is
-very close to a digital prolate spheroidal window with $W=0.008$ and is
-therefore omitted for brevity.
+To investigate the performance of the various windows when estimating the
+parameters of components in mixture we synthesized signals using
+Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
+uniform distributions specified in \cite{betser2009sinusoidal} and evaluated
+the parameter estimation accuracy at various differences between local maxima in
+the mixture's power-spectrum. The procedure is
+summarized in Fig.~\ref{fig:2cevalflowchart}.
 
-It is seen that a lower highest sidelobe level than the Nuttall and Prolate
-windows is obtained by slightly sacrificing the narrowness of the main lobe.
-More importantly, in Fig.~\ref{fig:dpw} we observe that the falloff of the
-window is 18 dB per octave because it is once-differentiable at all points in
-its domain.
+$d$ was incremented by $\Delta_{d} = \Dstep{}$ and so
+$\hat{d}$ was not generally integral valued in this case.
 
-\section{The performance of improved windows}
-
-\subsection{Signals with single component}
-
-To compare the average estimation error variance with the
-theoretical minimum given by the Cram\'{e}r-Rao bound we synthesized $K_{1}$ random
-chirps using Eq.~\ref{eq:polyphaseexp}
-with $Q=2$ and parameters chosen from uniform distributions justified in
-\cite{betser2009sinusoidal}. The original Hann window,
-the windows proposed by Nuttall and the new digital prolate based window were
-used to synthesize the atoms as described in Sec.~\ref{sec:designingatoms} and
-their estimation error variance was compared (see
-Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
-with the atoms, the three atoms whose inner products were greatest were used in
-the estimations, i.e., $R=3$ in Eq.~\ref{eq:ddmsyseq}. The windows with the
-lowest sidelobes only give the lowest error variance at very favourable SNRs, at
-real-world SNRs the original Hann window still performs best at estimating the
-parameters of a single component signal.
-
-\begin{figure}[H]
+\begin{figure}
     \centering
@@
 
-\subsection{Signals with 2 components}
-
-To evaluate the performance of the various windows when estimating the
-parameters of components in mixture we synthesized signals using
-Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
-uniform distributions specified in \cite{betser2009sinusoidal}.  We desired to
-see how the accuracy of estimation is influenced by the difference (in bins)
-between the locally maximized atoms and the difference in signal power between
-the two components. To obtain a set of components from which test signals
-exhibiting the desired differences could be constructed, we synthesized a set
-$\mathcal{C}$ of $K_{2}$ components for which the energy is maximized in bin 0.
-Test signals were obtained by choosing a pair of unique components from this set
-and modulating one to give the desired frequency and amplitude difference.  This was carried out as
-follows: the atom $r^{\ast}$ for which the inner product was maximized was
-determined for each unmixed chirp and the chirp was modulated by $\exp(-2\pi
-\frac{r^{\ast} n}{N}j)$ for $0 \leq n < N$ in order to move this maximum
-to $r=0$. Then for each desired difference $d$, with $0 \leq d < D$ (for the
-evaluation $D = \Doffset{}$), two unique
-chirps were selected from $\mathcal{C}$ and one chirp was modulated by
-$\exp(2\pi \frac{n d}{N}j)$ for $0 \leq n < N$ in order to give the
-desired difference between maxima. This component was also scaled by a constant
-to give a desired signal power ratio from set $\mathcal{S}$ with the other component (the power ratios
-$\mathcal{S}$ tested were 0 dB and -30 dB). As we assume perfect peak-atom selection for this
-evaluation no inner-product maximizing $r^{\ast}$ is chosen, rather atoms with
-angular frequencies $\omega=2\pi\frac{\hat{d}}{N}$ for $\hat{d} \in
-\{d-1,d,d+1\}$ in Eq.~\ref{eq:fourieratom} (again, $R=3$) were chosen to carry
-out the estimation. $d$ was incremented by $\Delta_{d} = \Dstep{}$ and so
-$\hat{d}$ was not generally integral valued in this case. The parameters of the
-unmodulated component were estimated using angular frequencies
-$\omega=2\pi\frac{\hat{d}}{N}$ for $\hat{d} \in\{-1,0,1\}$ in
-Eq.~\ref{eq:fourieratom}. The squared
-estimation error for each parameter was summed and divided by $K_{2}(K_{2}-1)$
-(the number of choices of two unique components) to give the averaged squared
-estimation error for each parameter at each difference $d$. The procedure is
-summarized in Fig.~\ref{fig:2cevalflowchart}.
-
-The behaviour of the windows when used to analyse mixtures of non-stationary
-signals is similar to the behaviour of windows used for harmonic analysis in the
-stationary case \cite{harris1978use}; here we obtain further insight into how
-the estimation of each coefficient of the polynomial in
-Eq.~$\ref{eq:polyphaseexp}$ is influenced by main-lobe width and sidelobe
-height and slope. In Fig.~\ref{fig:mixwincomp} we see that there is generally less
-estimation error for components having similar signal power. This is to be
-expected as there will be less masking of the weaker signal in these scenarios.
-The estimation error is large when the atoms containing the most signal energy
-for each component are not greatly separated in frequency.  This is due to the
-convolution of the Fourier transform of the window with the signal, and agrees
-with what was predicted by Eq.~\ref{eq:mixest}: indeed windows with a larger
-main lobe exhibit a larger ``radius'' (bandwidth) in which the error of the
-parameter estimation will be high.  However, for signals where local
-inner-product maxima are from atoms sufficiently separated in frequency, windows
-with lower sidelobes are better at attenuating the other component and for these
-the estimation error is lowest.
-
-\section{Conclusions}
-
-Motivated by the need to analyse mixtures of frequency- and
-am\-pli\-tude-mod\-u\-lat\-ed
-sinusoids (Eq.~\ref{eq:polyphaseexpmix}), we have shown that the DDM can be
-employed under a single-component
-assumption when components have roughly disjoint sets of atoms for which their
-inner products take on large values. This indicates the need for windows whose
-Fourier transform exhibits low sidelobes. We developed windows whose sidelobes
-are minimized while remaining everywhere once-differentiable: a requirement to
-generate valid atoms for the DDM. These windows were shown to only improve parameter
-estimation of $P=1$ component with argument-polynomial of order $Q=2$ in low
-amounts of noise. However, for $P=2$ components of the same order in mixture without
-noise, granted the components
-exhibited reasonable separation in frequency between the atoms for which the
-inner product was maximized, these new windows substantially improved the
-estimation of all but the first argument-polynomial coefficient.
-
-Further work should evaluate these windows on sinusoids of different orders,
-i.e., $Q \gg 1$. Optimal main-lobe widths for windows should be determined
-depending on the separation of local maxima in the power spectrum. It should
-also be determined if these windows improve the modeling of real-world acoustic
-signals.
-
 \section{Acknowledgments}
 This work was partially supported by grant from the Natural Sciences and Engineering Research Council of Canada awarded to Philippe Depalle (RGPIN-262808-2012).
-
-%\newpage
-%\nocite{*}
 \bibliographystyle{IEEEbib}
-\bibliography{paper} % requires file DAFx17_tmpl.bib
-
-%\section{Appendix}
+\bibliography{dafx-poster} % requires file DAFx17_tmpl.bib
+\end{multicols}
 

### 2017-08-28 paper/build_paper.sh

@@ -8,5 +8,5 @@ pdflatex paper.tex
 BIBINPUTS=. bibtex paper.aux
 pdflatex paper.tex
 pdflatex paper.tex
-mv paper.pdf Esterer_Nicholas_dafx_2017.pdf
+mv paper.pdf Esterer_Nicholas_dafx_2017_paper.pdf
 #dvipdf thesis.dvi

### 2017-08-28 poster/sciposter/dafxposter/build_poster.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+export TEXINPUTS=.:../../../paper/:
+pdflatex dafx-poster.tex
+BSTINPUTS=.:../../../paper/: BIBINPUTS=.:../../../paper/: bibtex dafx-poster.aux
+pdflatex dafx-poster.tex
+pdflatex dafx-poster.tex

### 2017-08-28 poster/sciposter/dafxposter/build_poster_reduced.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+export TEXINPUTS=.:../../../paper/:
+pdflatex dafx-poster-reduced.tex
+BSTINPUTS=.:../../../paper/: BIBINPUTS=.:../../../paper/: bibtex dafx-poster-reduced.aux
+pdflatex dafx-poster-reduced.tex
+pdflatex dafx-poster-reduced.tex

### 2017-08-29 poster/sciposter/dafxposter/dafx-poster-reduced.tex
Working on the flow chart

@@
 \usepackage{tikz}
-\usetikzlibrary{shapes.geometric, arrows, positioning, calc}
+\usetikzlibrary{shapes.geometric, arrows.meta, positioning, calc}
 \tikzstyle{startstop} = [rectangle,draw=black,text centered]%, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
@@
 \tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
-\tikzstyle{arrow} = [thick,->,>=stealth]
+\tikzstyle{arrow} = [thick,->,-{Latex}]
 \tikzstyle{noarrow} = [thick,-,>=stealth]
@@
                 single-component signals.};
+                \node (dumstart) [emptybox, right = of start] {};
                 \node (modulate) [process, below = of start] {Modulate so that
@@
                 according to $d$.};
-                \node (addpair) [process, below = of scaleone] {Add each signal
+                \node (dumscaleone) [emptybox, right = of scaleone] {};
+                \node (addpair) [process, right = of dumstart] {Add each signal
                 pair together.};
@@
                 $\Delta_{d}$.};
-                \node (dum2) [emptybox, right = of incd] {};
+                \node (dum2) [emptybox, left = of incd] {};
                 \node (dum3) [emptybox, below = of incd] {};
-                \node (dum3b) [emptybox, left = of incd] {};
+                \node (dum3b) [emptybox, left = of scaleone] {};
                 \node (dum4) [emptybox] at (dum3b |- dum3) {};
@@
                 \draw [arrow] (choosepair) -- (scaleone);
-                \draw [arrow] (scaleone) -- (addpair);
+                \draw [arrow] (scaleone) -- (dumscaleone.west) --
+                (dumstart.west) -- (addpair);
                 \draw [arrow] (addpair) -- (tryestimate1);
@@
 
-                \draw [arrow] (incd) -- (dum2.center) -- (dum2.center) -- 
-                    node [anchor=west,text width=2cm,minimum width=3cm] {If $d <
-                    D$.} (dum1.center) 
-                    -- (dum1.center) -- (choosepair);
+                \draw [arrow] (incd) -- (dum2.east) -- 
+                    (dum1.east) -- (choosepair);
+                \node [emptybox,text width=4cm,minimum width=3cm,left = of dum2]
+                {If $d < D$.};
 
-                \draw [arrow] (incd) -- (dum3.center) -- (dum3.center) --
-                (dum4.center) -- (dum4.center) -- 
-                node [anchor=east,text width=2cm,minimum width=2cm]
+                \draw [arrow] (incd) -- (dum3.center) -- 
+                (dum4.center) -- 
+                node [anchor=east,text width=4cm,minimum width=2cm]
                 {If signal power ratios in $\mathcal{S}$ remaining to be
-                evaluated.} (dum5.center) --
+                evaluated.} 
                  (dum5.center) -- (setd);

### 2017-09-27 set_python_path.sh
Added paper building script, need to test.

@@ -1,0 +1,1 @@
+export PYTHONPATH=../signal_modeling:.

### 2017-09-27 poster/sciposter/dafxposter/dafx-poster-reduced.tex

@@
 \def\papertitle{On the design and use of once-differentiable high dynamic
-resolution atoms for the Distribution Derivative Method}
+resolution atoms for the Distribution Derivative Method%
+}
 \def\paperauthorA{Nicholas Esterer}
@@
 \usepackage{tcolorbox}
+\usepackage{caption}
 %\usepackage{fancybullets}
@@
 %\definecolor{BoxCol}{rgb}{0.9,0.9,0.9}
-% uncomment for grey background to \section boxes 
+% uncomment for grey background to \section* boxes 
 % for use with default option boxedsections
@@
 %\definecolor{BoxCol}{rgb}{0.9,0.9,1}
-% uncomment for light blue background to \section boxes 
+% uncomment for light blue background to \section* boxes 
 % for use with default option boxedsections
@@
 %\definecolor{SectionCol}{rgb}{0,0,0.5}
-% uncomment for dark blue \section text
+% uncomment for dark blue \section* text
 
 % Flowchart drawing stuff
+\newcommand{\myinnercolsep}{1cm}
+\newcommand{\flowfontsize}{\small}
 \usepackage{tikz}
-\usetikzlibrary{shapes.geometric, arrows.meta, positioning, calc}
-\tikzstyle{startstop} = [rectangle,draw=black,text centered]%, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
-\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
+\usetikzlibrary{shapes.geometric, arrows.meta, positioning, calc,
+backgrounds}
 \tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=0cm, text
-centered, draw=black, text width=0.3\columnwidth]
+centered, draw=black,  font=\flowfontsize{}, text width=0.4\columnwidth]
 \tikzstyle{emptybox} = []
-\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
 \tikzstyle{arrow} = [thick,->,-{Latex}]
@@
 % insert correct institute name
-\institute{Sound Processing and Control Laboratory (SPCL) at McGill University}
+\institute{Sound Processing and Control Laboratory (SPCL), McGill University,
+Montreal, Canada}
 
@@
 
+\setlength{\secskip}{1pt}
+
+\ifthenelse{\equal{\orientation}{landscape}}{
+  \setlength{\titleskip}{0.01\textheight}
+}{
+  \setlength{\titleskip}{0.01\textwidth}
+}
+
+\newcommand{\imsize}{\columnwidth}
+\newcommand{\mytcbtitlewrap}[1]{{\parbox[bottom][1.5cm][c]{\linewidth}{#1}}}
+
+% This is a huge hack
+\renewcommand{\rightlogo}[3][0.9]{%
+\ifthenelse{\equal{#2}{}}{%
+ \renewcommand{\printrightlogo}{%
+   \begin{center}
+     \hspace*{0.6\textwidth}
+   \end{center}
+   }
+ }
+ {\renewcommand{\printrightlogo}{%
+      \begin{center}
+      \resizebox{#1\textwidth}{!}{\includegraphics{#2}}
+      \vspace{4.5cm}
+      \resizebox{#1\textwidth}{!}{\includegraphics{#3}}
+    \end{center}
+ }}
+}
+
+\renewcommand{\leftlogo}[2][0.9]{%
+\ifthenelse{\equal{#2}{}}{%
+ \renewcommand{\printleftlogo}{%
+   \begin{center}
+     \hspace*{0.6\textwidth}
+   \end{center}
+   }
+ }
+ {\renewcommand{\printleftlogo}{%
+      \begin{center}
+      \resizebox{#1\textwidth}{!}{\includegraphics{#2}}
+      \vspace{4.5cm}
+    \end{center}
+ }}
+}
+
+\renewcommand{\footnotesize}{\small}
+
+\tcbset{colbacktitle=white,coltitle=black,adjust text=\vline height
+1cm,valign=center,toptitle=2mm,bottomtitle=2mm,fonttitle=\bfseries}
+
+\setmargins[3cm]
 \begin{document}
+
+\leftlogo[1.0]{{DAFx17_logo}.pdf}
+\rightlogo[1.0]{{cirmmt_logo}.pdf}{{nserc_logo}.pdf}
+%\rightlogo[1.0]{{nserc_logo}.pdf}
+\renewcommand{\footlogo}{%
+    \resizebox{\logowidth}{!}{\includegraphics{{nserc_logo}.pdf}\hspace{1cm}\includegraphics{{cirmmt_logo}.pdf}}%
+}
+
 %define conference poster is presented at (appears as footer)
 
-\conference{{\em{\small{The 20$^{\text{\itshape th}}$ International Conference on Digital Audio Effects (DAFx-17), Edinburgh, UK, September 5--9, 2017}}}}
+\conference{{\em{\small{The 20$^{\text{\itshape th}}$ International Conference
+on Digital Audio Effects (DAFx-17), Edinburgh, UK, September 5--9, 2017, \textbf{pp.
+208--214}.}}}}
 
@@
 
-%\renewcommand{\mastercapstartstyle}[1]{\textit{\textbf{#1}}}
+\renewcommand{\mastercapstartstyle}[1]{\small{\textbf{#1}}}
+
+\renewcommand{\mastercapbodystyle}[1]{\small{}#1}
 %\renewcommand{\algcapstartstyle}[1]{\textsc{\textbf{#1}}}
@@
 
+%\newpage
+
+%\newpage
+
 %%% Begin of Multicols-Enviroment
@@
 %%% Abstract
-\begin{abstract}
-    The accuracy of the Distribution Derivative Method (DDM)
-    \cite{betser2009sinusoidal} is evaluated on mixtures of chirp signals. It is
+\begin{tcolorbox}[title=\mytcbtitlewrap{Abstract}]
+\setlength{\columnsep}{\myinnercolsep}
+\begin{multicols}{2}
+    \textit{%
+        The \textbf{accuracy of the Distribution Derivative Method (DDM)
+    \cite{betser2009sinusoidal}} is evaluated on mixtures of \textbf{chirp
+    signals}. It is
     shown that accurate estimation can be obtained when the sets of atoms for
-    which the inner product is large are disjoint.  This amounts to designing
-    atoms with windows whose Fourier transform exhibits low sidelobes but which
-    are once-differentiable in the time-domain. A technique for designing
-    once-differentiable approximations to windows is presented and the accuracy
-    of these windows in estimating the parameters of sinusoidal chirps in
-    mixture is evaluated.
-\end{abstract}
+    which the inner product is large are disjoint.  This amounts to \textbf{designing
+    atoms} with windows whose Fourier transform exhibits \textbf{low side-lobes but which
+    are once-differentiable in the time-domain}. A \textbf{technique for designing
+    once-differentiable approximations} to windows is presented and the \textbf{accuracy
+    of these windows in estimating the parameters} of sinusoidal chirps in
+    mixture \textbf{is evaluated}.}
+\end{multicols}
+\end{tcolorbox}
 
 %%% Introduction
-\section{Introduction}
+    \begin{tcolorbox}[title=\mytcbtitlewrap{Introduction}]
+\setlength{\columnsep}{\myinnercolsep}
+\begin{multicols}{2}
 \label{sec:intro}
+    \begin{itemize}
+        \item{Recently, there has
+            been interest in using \textbf{higher-order phase functions} for the argument of sinusoidal
+    functions \cite{xuepiecewise} as the estimation of
+their parameters has been made possible by a set of \textbf{techniques 
+            using signal derivatives} \cite{hamilton2012unified}. The DDM is one
+            such technique.}
 
-Recently, there has
-been interest in using higher-order phase functions for the argument of sinusoidal
-    functions \cite{xuepiecewise} as the estimation of
-their parameters has been made possible by a set of techniques 
-using signal derivatives \cite{hamilton2012unified}.
+        \item{For comparison with previous research on the DDM, we consider the estimation -- via the DDM -- of the parameters of a
+            \textbf{parabolic phase function} for which the imaginary parts of the parameters
+            represent the \textbf{initial phase, frequency and frequency slope}. The real parts
+    of the parameters represent the \textbf{initial amplitude, amplitude slope and
+            amplitude curvature}.}
 
-For comparison with previous research on the DDM, we consider the estimation -- via the DDM -- of the parameters of a
-    parabolic phase function for which the imaginary parts of the parameters
-    represent the initial phase, frequency and frequency slope. The real parts
-    of the parameters represent the initial amplitude, amplitude slope and
-    amplitude curvature.
+        \vspace{1cm}
 
-The DDM requires a set of atoms that are once-differentiable everywhere in
-    the time-domain from which the parameters are estimated. We
-    show that on a mixture of sinusoids, accurate estimation for each sinusoid
+        \item{The DDM requires a set of atoms that are \textbf{once-differentiable everywhere in
+            the time-domain} from which the parameters are estimated. We
+    show that on a \textbf{mixture of sinusoids, accurate estimation for each
+            sinusoid}
     can be obtained under a single-component
-assumption when components have roughly disjoint sets of atoms for which their
-inner products take on large values.
+            assumption when components have roughly \textbf{disjoint sets of atoms} for which their
+inner products take on large values.}
 
-Encouraging disjointedness amounts to designing atoms whose Fourier
-    transform exhibits low side-lobes under the additional constraint that
-    the atoms be everywhere once-differentiable. We show how to design atoms
-    with this latter property based on the shapes of ideal windows.
+\item{\textbf{Encouraging disjointedness} amounts to designing atoms whose Fourier
+    transform exhibits \textbf{low side-lobes} under the additional constraint that
+            the atoms be \textbf{everywhere once-differentiable}. We show how to \textbf{design atoms
+            with this latter property} based on the shapes of ideal windows.}
+    \end{itemize}
+\end{multicols}
+\end{tcolorbox}
 
-\section{Estimating the \lowercase{$a_{p,q}$} of $P$ components}
-\begin{tcolorbox}
+\addtocounter{footnote}{1}\footnotetext{\label{fn:mathdefs}
+$\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)$,
+$\left\langle x , \psi \right\rangle = 
+\int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt$
+}
+\addtocounter{footnote}{1}\footnotetext{\label{fn:optnote}
+The notation $x^{\ast}$ will mean the value of the argument $x$ maximizing or minimizing some
+function.
+}%
+
+\begin{tcolorbox}[title=\mytcbtitlewrap{Estimating the
+    \lowercase{$a_{p,q}$} of $P$ components}]
+\setlength{\columnsep}{\myinnercolsep}
 \begin{multicols}{2}
@@
 \begin{equation}
+    \label{eq:polyphaseexpmix}
     x(t) = \sum_{p=1}^{P} x_{p}(t) + \eta(t)
@@
 %
-with
-%
-\begin{equation}
-    \label{eq:polyphaseexpmix}
-    x_{p}(t) = \exp(a_{p,0} + \sum_{q=1}^{Q} a_{p,q} t^q)
-\end{equation}
-%
+with $ x_{p}(t) = \exp(a_{p,0} + \sum_{q=1}^{Q} a_{p,q} t^q) $
+
 and $\eta$ Gaussian-distributed white noise.
-    \end{multicols}
-\end{tcolorbox}
 
-\begin{tcolorbox}
-\begin{multicols}{2}
-Applying the DDM to a mixture of $P$ componentes, we obtain%
-\footnote{
-$\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)$
-
-$\left\langle x , \psi \right\rangle = 
-\int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt$
-}
+Applying the DDM to a mixture of $P$ components, we
+    obtain\footnotemark[1]%\ref{fn:mathdefs}]
 %
@@
 %
-From this we see if $\left\langle \mathcal{T}^{q-1} x_{p} , \overline{\psi}_{r}
+When $\left\langle \mathcal{T}^{q-1} x_{p} , \overline{\psi}_{r}
 \right\rangle$ and $\left\langle x_{p}, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
-are small for all but $p = p^{\ast}$ and a subset of $R$ atoms\footnote{%
-The notation $x^{\ast}$ will mean the value of the argument $x$ maximizing or minimizing some
-function.
-}%
-, we can simply estimate the parameters $a_{p^{\ast},q}$ using
-\begin{equation}
+are small for all but $p = p^{\ast}$ and a subset of $R$ atoms, we can simply
+    estimate the parameters $a_{p^{\ast},q}$ using%
+    \footnotemark[2]%[\ref{fn:optnote}]
+\begin{multline}
     \sum_{q=1}^{Q} q a_{{p^{\ast}},q} 
     \left\langle \mathcal{T}^{q-1} x_{p^{\ast}} , \overline{\psi}_{r} \right\rangle
-    = -\left\langle x_{p^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
-\end{equation}
-for $1 \leq r \leq R$.
+    = -\left\langle x_{p^{\ast}}, \frac{d\overline{\psi}_{r}}{dn}
+    \right\rangle\\
+    \text{for } 1 \leq r \leq R\text{.}
+\end{multline}
 \end{multicols}
@@
 
-\begin{tcolorbox}
+\begin{tcolorbox}[title=\mytcbtitlewrap{Designing the $\psi_{r}$}]
+\setlength{\columnsep}{\myinnercolsep}
 \begin{multicols}{2}
-To compute $a_{p^{\ast},0}$ we define
-\begin{equation}
-    \gamma_{p^{\ast}}(t) = \exp \left( \sum_{q=1}^{Q} a_{p^{\ast},q} t^{q} \right)
-\end{equation}
-and estimate $a_0$ as
-\begin{equation}
-    \label{eq:ddmesta0}
-    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
-        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
-\end{equation}
+\label{sec:designingatoms}
+%
+Canonically, the atoms $\psi_{\omega}(t)$ 
+    are the \textbf{products} of the elements of the \textbf{Fourier basis} and a 
+    \textbf{window $w$ that is once differentiable}, i.e.,
+    $\psi_{\omega}(t) = w(t) \exp(-j \omega t)$.
+
+    Defining $N$ \textbf{as the length of the window} in samples, angular frequency at bin $r$ as $\omega_{r} = 2
+\pi \frac{r}{N}$, and $T$ the sample period in seconds, the approximate
+    \textbf{inner product} $\left\langle x , \psi_{\omega}
+    \right\rangle$ equals:
+\begin{multline}
+    \label{eq:approxinnerprod}
+    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi j r \frac{n}{N}) 
+\end{multline}
+i.e., the definition of the DFT of a windowed signal.
+\columnbreak
+
+Therefore \textbf{choosing $\psi$ amounts to
+    designing a Fourier window with minimal side-lobes}, under the \textbf{constraint
+    that the window be differentiable in $t$ and finite}.
 \end{multicols}
@@
 
-\section{Designing the $\psi_{r}$}
-\label{sec:designingatoms}
-\begin{tcolorbox}
-\begin{multicols}{2}
+\begin{tcolorbox}[title=\mytcbtitlewrap{Differentiable approximations to windows}]
 %
-Canonically, the chosen atoms $\psi_{\omega}(t)$ 
-are the products of the elements of the Fourier basis and an appropriately
-chosen window $w$ that is once differentiable and finite, i.e.,
-%
-\begin{equation}
-    \label{eq:fourieratom}
-    \psi_{\omega}(t) = w(t) \exp(-j \omega t)
-\end{equation}
-%
-Defining $N = \frac{L_{t}}{T}$ and angular frequency at bin $r$ as $\omega_{r} = 2
-\pi \frac{r}{N}$, the approximate inner product is then
-%
-\begin{equation}
-    \label{eq:approxinnerprod}
-    \left\langle x , \psi_{\omega} \right\rangle \approx 
-    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi j r \frac{n}{N}) 
-\end{equation}
-%
-i.e., the definition of the DFT of a windowed signal.
-Therefore choosing $\psi$ amounts to a
-Fourier window design problem minimizing its side-lobes, under the constraint
-that the window be differentiable in $t$ and finite.
-\end{multicols}
-\end{tcolorbox}
-
-\section{Differentiable approximations to windows}
-%
-\newcommand{\imsize}{\columnwidth}
 \begin{figure}
@@
 \end{center}
-\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
-spectrum characteristics of the continuous 4-term Nuttall window, the digital
-prolate window with $W=0.008$, and the continuous approximation to the digital
-prolate window.}
+    \caption{\label{fig:dpw} \textbf{Comparing the main-lobe and asymptotic power
+    spectrum} characteristics of the continuous 4-term Nuttall window, the digital
+prolate window with $W=0.008$, and the \textbf{continuous approximation to the digital
+    prolate window}. The falloff of the
+    Nuttall and Prolate Approximation is \textbf{18 dB per octave} because they are both
+    \textbf{once-differentiable with respect to time}.}
 \end{figure}
 %
-
-\begin{tcolorbox}
+\setlength{\columnsep}{\myinnercolsep}
 \begin{multicols}{2}
-A differentiable approximation to a symmetrical window can be designed in a
-straightforward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
-is shown how to design optimal windows of length $N$ samples using a linear
-combination of $M$ harmonically related cosines
+A differentiable approximation to a symmetrical window of length $N$ samples can be designed using a \textbf{linear
+    combination of $M$ harmonically related cosines} \cite{harris1978use} \cite{rabiner1970approach} 
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{R}$ is the \textit{rectangle function}. This function is
-discontinuous
-at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
+where $\mathcal{R}$ is the \textit{rectangle function}.
+
+$\tilde{w}(n)$ is
+not differentiable
+at $n = \frac{\pm N}{2}$, unless
 $\sum_{m=0}^{M-1} b_{m} \cos ( \pm \pi m ) = 0$.
 
-Therefore, we choose the $b_{m}$ so that
-the window $\tilde{w}$'s squared approximation error to $w$ is minimized while having
-$\tilde{w}(\frac{\pm N}{2}) = 0$, i.e. we find the solution $\{ b^{\ast}_{m} \}$ to the
+Therefore, we choose the $b_{m}$ 
+minimizing the window $\tilde{w}$'s approximation error to $w$ while
+    \textbf{maintaining continuity}, finding the solution $\{ b^{\ast}_{m} \}$ to the
 mathematical program
-\begin{equation}
+\begin{equation*}
     \label{eq:searchcontwinprogram}
@@
         - \sum_{m=0}^{M-1} b_{m} \cos(2 \pi m \frac{n}{N}))^{2}
-\end{equation}
+\end{equation*}
 \begin{equation}
@@
 \end{equation}
-which can be solved using constrained least-squares\cite[p.~585]{golub1996matrix}.
-\end{multicols}
-\end{tcolorbox}
 
-\begin{tcolorbox}
-\begin{multicols}{2}
-Using this technique, we designed a continuous approximation to a digital prolate
-spheroidal window of length $N=512$ and $W=0.008$. The coefficients
+    Using this technique, we designed a \textbf{5-term continuous approximation} to a digital \textbf{prolate
+    spheroidal window} of length $N=512$ and design parameter $W=0.008$ \cite{verma1996digital}. The coefficients
 are described in Table~\ref{tab:contprolate} and a comparison with other
@@
 
-\section{The performance of improved windows on signals with 2 components}
-
-To investigate the performance of the various windows when estimating the
-parameters of components in mixture we synthesized signals using
-Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
-uniform distributions specified in \cite{betser2009sinusoidal} and evaluated
-the parameter estimation accuracy at various differences between local maxima in
-the mixture's power-spectrum. The procedure is
-summarized in Fig.~\ref{fig:2cevalflowchart}.
-
-$d$ was incremented by $\Delta_{d} = \Dstep{}$ and so
-$\hat{d}$ was not generally integral valued in this case.
+\begin{tcolorbox}[title=\mytcbtitlewrap{The performance of improved windows on a
+    mixture of 2 sinusoids}]
+%    \setlength{\floatsep}{-20pt}
+    \begin{center}
+\begin{figure}
+\begin{center}
+    {\resizebox{\imsize}{!}{\includegraphics{{comp_offset_chirp_est_err_params}.eps}}}
+\end{center}
+\caption{\label{fig:mixwincomp} The mean squared estimation error for each
+    parameter \textbf{in an analysis of two components in mixture}. A set of
+    \textbf{$K_{2}=\Koffset{}$ chirps} was synthesized and \textbf{each unique
+    pair} used for
+    maximum bin differences $0 \leq d < \Doffset{}$, with $d$ varied in
+    $\Delta_{d} = \Dstep{}$ bin increments. The \textbf{signal power ratio}
+    between components is indicated with \textbf{colours} and the corresponding ratio in decibels is indicated in the
+    plot legend (the power ratios
+    $\mathcal{S}$ tested were \textbf{0 dB and -30 dB}). The names indicate the windows used to generate the atoms for
+    estimation: \textbf{\textit{N3} and \textit{N4} are the 3- and 4-cosine-term
+    continuous Nuttall} windows, \textbf{\textit{H} is the Hann window}, and \textbf{\textit{P5}
+    is the continuous 5-cosine-term approximation to a digital prolate window}.}
+\end{figure}
 
@@
     \centering
-            \begin{tikzpicture}[node distance=0.25cm]
+    \begin{minipage}[l]{0.65\columnwidth}
+            \begin{tikzpicture}[node distance=0.25cm, background rectangle/.style= {draw=white,fill=white}, show background rectangle]
+%                \begin{scope}[shift={(-5,0)}]
                 \node (start) [process] at (0,0) {Synthesize $K_{2}$
@@
                 $\Delta_{d}$.};
-                \node (dum2) [emptybox, left = of incd] {};
+                \node (dum2) [emptybox, left = of incd, font=\flowfontsize{},
+                anchor=east] {If $d < D$.};
                 \node (dum3) [emptybox, below = of incd] {};
@@
                 \node (dum4) [emptybox] at (dum3b |- dum3) {};
+                \node (dum4text) [emptybox, text width=0.3\columnwidth, above right, 
+                font=\flowfontsize{}] at (dum4.center) {If signal power ratios in $\mathcal{S}$ remaining to be
+                evaluated.};
 %                \node let \p{dum3b}=(dum3b), \p{dum3}=(dum3) in (dum4) [emptybox] at (\x{dum3b},\y{dum3}) {};
@@
                 \draw [arrow] (choosepair) -- (scaleone);
-                \draw [arrow] (scaleone) -- (dumscaleone.west) --
-                (dumstart.west) -- (addpair);
+                \draw [arrow] (scaleone) -- (dumscaleone.center) --
+                (dumstart.center) -- (addpair);
                 \draw [arrow] (addpair) -- (tryestimate1);
@@
                     (dum1.east) -- (choosepair);
-                \node [emptybox,text width=4cm,minimum width=3cm,left = of dum2]
-                {If $d < D$.};
+                %\node [emptybox,text width=4cm,minimum width=3cm,left = of dum2,
+                %align = flush right]
+                %{If $d < D$.};
 
@@
                 (dum4.center) -- 
-                node [anchor=east,text width=4cm,minimum width=2cm]
-                {If signal power ratios in $\mathcal{S}$ remaining to be
-                evaluated.} 
                  (dum5.center) -- (setd);
+%            \end{scope}
+    \end{tikzpicture}
+    \end{minipage}
+    \begin{minipage}[r]{0.3\columnwidth}
+        \caption{The \textbf{evaluation procedure for 2-component
+        signals}.\label{fig:2cevalflowchart}
+We synthesized signals using
+Eq.~\ref{eq:polyphaseexpmix} with $P=2$, $Q=2$ and parameters chosen from the
+        \textbf{uniform distributions specified in \cite{betser2009sinusoidal}}.
+        No noise was added to the mixture. We then evaluated
+the parameter estimation accuracy at \textbf{various differences between local maxima in
+        the mixture's power-spectrum}.}
+    \end{minipage}
+\end{figure}
+\end{center}
+\end{tcolorbox}
 
-            \end{tikzpicture}
-    \caption{The evaluation procedure for 2-component
-    signals.\label{fig:2cevalflowchart}}
-\end{figure}
-
-\section{Acknowledgments}
-This work was partially supported by grant from the Natural Sciences and Engineering Research Council of Canada awarded to Philippe Depalle (RGPIN-262808-2012).
 \bibliographystyle{IEEEbib}
-\bibliography{dafx-poster} % requires file DAFx17_tmpl.bib
+%\nocite{*}
+%\bibliography{dafx-poster} % requires file DAFx17_tmpl.bib
+\bibliography{paper}
 \end{multicols}

### 2017-09-27 poster/sciposter/dafxposter/dafx-poster.tex

--- 2017-08-28 paper/paper.tex
@@
 \def\paperauthorB{Philippe Depalle}
+\documentclass[plainsections,landscape]{sciposter}
 
-% Authors' affiliations have to be set below
+\usepackage{epsfig}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{multicol}
+%\usepackage{fancybullets}
+%\usepackage{amsmath,amssymb,amsfonts,amsthm}
+%\usepackage{euscript}
+%\usepackage[latin1]{inputenc}
+%\usepackage[T1]{fontenc}
+%\usepackage{ifpdf}
+%
+%\usepackage[english]{babel}
+%\usepackage{caption}
+%\usepackage{subfig} % or can use subcaption package
+%\usepackage{color}
+%\usepackage{cite}
+%\usepackage{float}
+%
+%\usepackage{hyphenat}
+%\hyphenation{spher-oidal}
+%%\hyphenation{amp-li-tude}
+%%\hyphenation{mod-u-lat-ed}
+%
+%\usepackage{times}
 
-%------------------------------------------------------------------------------------------
-\documentclass[twoside,a4paper]{article}
-\usepackage{dafx_17}
-\usepackage{amsmath,amssymb,amsfonts,amsthm}
-\usepackage{euscript}
-\usepackage[latin1]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{ifpdf}
+\newtheorem{Def}{Definition}
 
-\usepackage[english]{babel}
-\usepackage{caption}
-\usepackage{subfig} % or can use subcaption package
-\usepackage{color}
-\usepackage{cite}
-\usepackage{float}
+%\definecolor{BoxCol}{rgb}{0.9,0.9,0.9}
+% uncomment for grey background to \section boxes 
+% for use with default option boxedsections
 
-\setcounter{page}{1}
-\ninept
+%\definecolor{BoxCol}{rgb}{0.9,0.9,1}
+% uncomment for light blue background to \section boxes 
+% for use with default option boxedsections
 
-\usepackage{hyphenat}
-\hyphenation{spher-oidal}
-%\hyphenation{amp-li-tude}
-%\hyphenation{mod-u-lat-ed}
-
-\usepackage{times}
-% Saves a lot of ouptut space in PDF... after conversion with the distiller
-% Delete if you cannot get PS fonts working on your system.
-
-% pdf-tex settings: detect automatically if run by latex or pdflatex
-\newif\ifpdf
-\ifx\pdfoutput\relax
-\else
-   \ifcase\pdfoutput
-      \pdffalse
-   \else
-      \pdftrue
-\fi
-
-\ifpdf % compiling with pdflatex
-  \usepackage[pdftex,
-    pdftitle={\papertitle},
-    pdfauthor={\paperauthorA, \paperauthorB},
-    colorlinks=false, % links are activated as colror boxes instead of color text
-    bookmarksnumbered, % use section numbers with bookmarks
-    pdfstartview=XYZ % start with zoom=100% instead of full screen; especially useful if working with a big screen :-)
-  ]{hyperref}
-  \pdfcompresslevel=9
-  \usepackage[pdftex]{graphicx}
-  \usepackage[figure,table]{hypcap}
-\else % compiling with latex
-  \usepackage[dvips]{epsfig,graphicx}
-  \usepackage[dvips,
-    colorlinks=false, % no color links
-    bookmarksnumbered, % use section numbers with bookmarks
-    pdfstartview=XYZ % start with zoom=100% instead of full screen
-  ]{hyperref}
-  % hyperrefs are active in the pdf file after conversion
-  \usepackage[figure,table]{hypcap}
-\fi
+%\definecolor{SectionCol}{rgb}{0,0,0.5}
+% uncomment for dark blue \section text
 
@@
 
-\twoaffiliations{
-\paperauthorA \,}
-{\href{https://mt.music.mcgill.ca/spcl}{SPCL\sthanks{Sound Processing and Control Laboratory}} \\ McGill University\\ Montreal, Quebec, Canada\\
-{\tt \href{mailto:nicholas.esterer@mail.mcgill.ca}{nicholas.esterer@mail.mcgill.ca}}
-}
-{\paperauthorB \,}
-{\href{https://mt.music.mcgill.ca/spcl}{SPCL} \\ McGill University\\ Montreal,
-Quebec, Canada\\ {\tt \href{mailto:philippe.depalle@mcgill.ca}{philippe.depalle@mcgill.ca}}
-}
+% Note: only give author names, not institute
+\author{\paperauthorA{} and \paperauthorB{}}
+
+% insert correct institute name
+\institute{Sound Processing and Control Laboratory (SPCL) at McGill University}
+
+\email{nicholas.esterer@mail.mcgill.ca, philippe.depalle@mcgill.ca}  % shows author email address below institute
+
+%\date is unused by the current \maketitle
+
+% The following commands can be used to alter the default logo settings
+%\leftlogo[0.9]{logoWenI}{  % defines logo to left of title (with scale factor)
+%\rightlogo[0.52]{RuGlogo}  % same but on right
+
+% NOTE: This will require presence of files logoWenI.eps and RuGlogo.eps, 
+% or other supported format in the current directory  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Begin of Document
 
@@
 
+%%% Begin of Multicols-Enviroment
+\setlength{\columnseprule}{0pt}
+\begin{multicols}{5}
+
+%%% Abstract
 \begin{abstract}
@@
     once-differentiable approximations to windows is presented and the accuracy
-    of these windows in estimating the parameters of sinusoidal chirps in mixture is
-    evaluated.
+    of these windows in estimating the parameters of sinusoidal chirps in
+    mixture is evaluated.
 \end{abstract}
 
+%%% Introduction
 \section{Introduction}
@@
 Additive synthesis using a sum of sinusoids plus noise is a powerful model for
-representing audio \cite{serra1989system}, allowing for the easy implementation
-of many manipulations such as time-stretching \cite{marchand2004enhanced} and
-timbre-morphing \cite{haken2007beyond}.
-%
-In these papers,
-\cite{serra1989system,marchand2004enhanced,haken2007beyond} the
-phase evolution of the sinusoid is assumed linear over the analysis frame, only
-the phase and frequency of the sinusoids at these analysis points are used to
-fit a plausible phase function after some the analysis points are connected to
-form a partial \cite{mcaulay1986speech}. 
+representing audio \cite{serra1989system}.
 %
 Recently, there has
-been interest in using higher-order phase functions \cite{xuepiecewise} as the estimation of
-their parameters has been made possible by a new set of techniques of only
-moderate computational complexity using signal derivatives \cite{hamilton2012unified}.
-%
-The use
-of higher-order phase models allows for accurate description of highly modulated
-signals, for
-example in the analysis of birdsong \cite{stowell2013improved}.
-%
-The frequency
-modulation information has also been used in the
-regularization of mathematical programs for audio source separation \cite{creager2016musicalsource}.
+been interest in using higher-order phase functions for the sinusoidal
+    functions argument \cite{xuepiecewise} as the estimation of
+their parameters has been a set of techniques 
+using signal derivatives \cite{hamilton2012unified}.
 
-The sinusoidal model approximating signal $s$ typically considered is
-%
-\begin{equation}
-    \label{eq:polyphaseexp}
-    \tilde{s}(t) = \exp(a_0 + \sum_{q=1}^{Q} a_{q} t^q) + \eta(t)
-\end{equation}
-where $\tilde{s}$ is the approximating signal, $t$ the variable of time, the
-$a_{q} \in \mathbb{C}$ coefficients of the argument's polynomial, and $\eta(t)$
-white Gaussian noise.
-%
-Although this technique can be extended to describe a single sinusoid of
-arbitrary complexity simply by increasing $Q$, it remains essential to consider
-signals featuring a sum of $P$ such components, whether they represent the harmonic structure of a musical sound or the union of partials resulting from a mixture of multiple signal sources (e.g., recordings of multiple speakers or performers),  i.e.,
+The extended additive sinusoidal model approximating signal $s$ is 
 %
@@
 %
-As regards the design and evaluation of signal-derivatives analysis techniques,
-previous work has generally assumed signals containing a single component, i.e.,
-$P$ = 1 or assumed the influence of other components to be negligible. Later we
-will refine when this assumption can be made. In \cite{hamilton2012comparisons}
-the authors provide a comprehensive evaluation of various signal-derivatives
-analysis methods applied to a single-component signal. In
-\cite{robel2002estimating} the extent to which two components in mixture can
-corrupt estimations of the frequency slope ($\Im\{a_{0,2}\}$ and
-$\Im\{a_{1,2}\}$) is investigated in the context of the reassignment method, one
-of the signal-derivatives techniques, but the corruption of the other
-parameters is not considered.
+and $\eta$ Gaussian-distributed white noise. In this paper, we revisit the quality of signal-derivatives estimation of
+\textit{all} the $a_{q}$ when analyzing a \textit{mixture} of components. We focus on
+the DDM \cite{betser2009sinusoidal} analysis method.
 
-In this paper, we revisit the quality of signal-derivatives estimation of
-\textit{all} the $a_{q}$ when analyzing a \textit{mixture} of components. We focus on
-the DDM \cite{betser2009sinusoidal} analysis method for its convenience as it
-can simply be considered as an atomic decomposition (see
-Sec.~\ref{sec:estimating_aj}), and does not require computing derivatives
-of the signal to be analysed.
-
-The DDM does, however, require a once-differentiable analysis window. As we are
-interested in windows with lower sidelobes in order to better estimate
-parameters of sinusoidal chirp signals in mixture, we seek windows that
-combine these two properties. For this, a technique to design
-once-differentiable approximations to arbitrary symmetrical windows is proposed
-and presented along with a design example for a high-performance window. Finally
-we evaluate the performance of various once-differentiable windows in estimating
+The DDM requires a once-differentiable analysis window. For this, a technique to design
+once-differentiable approximations to arbitrary symmetrical windows is
+    proposed.
+We evaluate the performance of various once-differentiable windows in estimating
 the parameters $a_{q}$.
-
-\section{Estimating the parameters \lowercase{$a_{q}$}}
-\label{sec:estimating_aj}
-We will now show briefly how the DDM can be used to estimate the $a_{q}$. Based on
-the theory of distributions \cite{schwartz1959theorie}, the DDM
-makes use of ``test
-functions'' or atoms $\psi$. These atoms must be once differentiable with
-respect to time variable $t$ and be non-zero only on a finite interval
-$[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$. First, we define the inner product
+\footnote{
+        $\left\langle x , \psi \right\rangle = 
+    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt$
+}
 %
-\begin{equation}
-    \label{eq:ddm:inner:prod:def}
-    \left\langle x , \psi \right\rangle = 
-    \int_{-\infty}^{\infty}x(t)\overline{\psi}(t)dt
-\end{equation}
-%
-and the operator 
-%
-\begin{equation}
-\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)
-\end{equation}
-%
-Consider the weighted signal
-%
-\begin{equation}
-    f(t) = x(t) \overline{\psi}(t)
-\end{equation}
-%
-differentiating with respect to $t$ we obtain
-%
-\begin{multline}
-    \label{eq:ddm:weighted:sig:derivative}
-    \frac{df}{dt}(t) = 
-    \frac{dx}{dt}(t)\overline{\psi}(t)
-    + x(t)\frac{d\overline{\psi}}{dt}(t) = \\
-    \left( \sum_{q=1}^{Q} q a_{q} t^{q-1} \right) x(t)\overline{\psi}(t)
-    + x(t)\frac{d\overline{\psi}}{dt}(t)
-\end{multline}
-%
-Because $\psi$ is zero outside of the interval $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$, integrating
-$\frac{df}{dt}(t)$ we obtain
-%
-\begin{multline}
-    \int_{-\infty}^{\infty}\frac{df}{dt}(t)dt = \\
-    \sum_{q=1}^{Q} q a_{q} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} t^{q-1} x(t) \overline{\psi}(t) dt
-    + \left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle = 0
-\end{multline}
-%
-or, using the operator $\mathcal{T}^{\alpha}$,
-%
-\begin{equation} 
-    \sum_{q=1}^{Q} q a_{q} 
-    \left\langle \mathcal{T}^{q-1} x , \overline{\psi} \right\rangle
-    = -\left\langle x, \frac{d\overline{\psi}}{dt} \right\rangle
-\end{equation}
-%
-
-Estimating coefficients $a_{q}$, ${1 < q \leq Q}$, simply requires $R$ atoms
-$\psi_{r}$ with $R \geq Q$ to solve the linear system of equations
-\begin{equation}
-    \label{eq:ddmsyseq}
-    \sum_{q=1}^{Q} q a_{q} 
-    \left\langle \mathcal{T}^{q-1} x , \overline{\psi}_{r} \right\rangle
-    = -\left\langle x, \frac{d\overline{\psi}_{r}}{dt} \right\rangle
-\end{equation}
-for $1 \leq r \leq R$.
-
-To estimate $a_0$ we rewrite the signal we are analysing as
-\begin{equation}
-    x(t) = \exp(a_0) \gamma(t) + \epsilon (t)
-\end{equation}
-where $\epsilon (t)$ is the error signal, the part of the signal that is not explained
-by our model, and $\gamma (t)$ is the part of the signal
-whose coefficients have already been estimated, i.e.,
-\begin{equation}
-    \gamma(t) = \exp \left( \sum_{q=1}^{Q} a_{q} t^{q} \right)
-\end{equation}
-Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
-\begin{equation}
-    \left\langle x , \gamma \right\rangle
-    =
-    \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
-        \left\langle \epsilon , \gamma \right\rangle
-\end{equation}
-The inner product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
-principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
-depend on $t$, we have
-\begin{equation}
-    \left\langle x , \gamma \right\rangle
-    =
-    \exp(a_0) \left\langle \gamma , \gamma \right\rangle
-\end{equation}
-so we can estimate $a_0$ as
-\begin{equation}
-    \label{eq:ddmesta0}
-    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
-        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
-\end{equation}
-
-As will be seen in subsequent sections, the DDM typically involves taking the
-discrete Fourier transform (DFT) of the signal windowed by both an everywhere once-differentiable function of
-finite support (e.g., the Hann window) and this function's derivative. A small
-subset of atoms corresponding to the peak bins in the DFT are used in
-Eq.~\ref{eq:ddmsyseq} to solve for the parameters $a_{q}$.
+\footnote{
+$\mathcal{T}^{\alpha} : (\mathcal{T}^{\alpha}x)(t) = t^{\alpha}x(t)$
+}
 
@@
 
-We examine how the mixture model influences the estimation of the $a_{p,q}$ in
-Eq.~\ref{eq:polyphaseexpmix}.
-Consider a mixture of $P$ components.
-If we define the weighted signal sum
-%
-\begin{equation}
-    g(t) = \sum_{p=1}^{P} x_{p}(t) \overline{\psi}(t) = \sum_{p=1}^{P} f_{p}(t)
-\end{equation}
-%
-and substitute $g$ for $f$ in Eq.~\ref{eq:ddm:weighted:sig:derivative} we obtain
+Applying the DDM to a mixture of $P$ componentes, we obtain
 %
@@
     + \left\langle x_{p}, \frac{d\overline{\psi}}{dt} \right\rangle \right)
+    = 0
 \end{multline}
@@
 \end{equation}
-for $1 \leq r \leq R$. To compute $a_{p^{\ast},0}$ we simply use
+for $1 \leq r \leq R$.
+To compute $a_{p^{\ast},0}$ we define
 \begin{equation}
@@
 \end{equation}
-in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.
+and estimate $a_0$ as
+\begin{equation}
+    \label{eq:ddmesta0}
+    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
+        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
+\end{equation}
 
@@
 \label{sec:designingatoms}
-%
-\begin{figure*}[t]
-    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
-\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
-spectrum characteristics of the continuous 4-term Nuttall window, the digital
-prolate window with $W=0.008$, and the continuous approximation to the digital
-prolate window.}
-\end{figure*}
 %
@@
 i.e., the definition of the DFT of a windowed signal%
-\footnote{%
-    Notice however that this is an approximation of the inner product and should
-    not be interpreted as yielding the Fourier series coefficients of a properly
-    sampled signal $x$ periodic in $L_{t}$. This means that other
-    evaluations of the inner product that yield more accurate results are
-    possible. For example, the analytic solution is possible if $x$ is assumed
-    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
-    general analytic).  In this case the samples of $x$ are convolved with the
-    appropriate interpolating sinc functions and the integral of this function's
-    product with $\psi$ is evaluated.
-}. %
 The DFT is readily interpreted as a bank of bandpass filters centred at
-normalized frequencies%
-%\footnote{%
-%In this article as in much of the literature on signal processing the index $r$
-%of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
-%\frac{r}{N}$ will be referred to as its bin number.
-%}
+normalized frequencies
 $\frac{r}{N}$ and with frequency response described by the Fourier transform of
 modulated $w$ \cite{allen1977unified}. Therefore choosing $\psi$ amounts to a
-filter design problem under the constraints that the impulse response of the
-filter be differentiable in $t$ and finite. To minimize the influence of all but
-one component, granted the components's energy concentrations are sufficiently
-separated in frequency, we desire impulse responses whose magnitude response
-gives maximum out-of-band rejection or equivalently, windows whose Fourier
-transform exhibits the lowest sidelobes.
-
-In all the publications reviewed on the DDM for this paper, the window used was
-the Hann window which is once-differentiable everywhere in the time-domain. In
-\cite{robel2002estimating}, a publication on the reassignment method, other
-windows than the Hann are considered but these windows must be
-twice-differentiable.  Nuttall \cite{nuttall1981some} has designed windows with
-lower sidelobes than the canonical Hann window which are everywhere at least
-once-differentiable. It is also possible to design approximations to arbitrary
-symmetrical window functions using harmonically related cosines, as is discussed
-in the following section.
+filter design problem optimizing the amount of out-of-band rejection, under the constraints that the impulse response of the
+filter be differentiable in $t$ and finite.
 
@@
 %
-\begin{figure*}[ht]
-    \centerline{\includegraphics[width=7in]{{ddm_snr_win_comp}.eps}}
-\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
-    phase sinusoids averaged over $K_{1}=\Ksnr{}$ trials using atoms generated from
-    various windows. \textit{C} is the Cram\'{e}r-Rao
-lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
-Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continuous
-5-cosine-term approximation to a digital prolate window as described in
-Sec.~\ref{sec:designexample}.}
-\end{figure*}
+\newcommand{\imsize}{\columnwidth}
+\begin{figure}
+\begin{center}
+    {\resizebox{\imsize}{!}{\includegraphics{{search_dpw_bw_m}.eps}}}
+\end{center}
+\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
+spectrum characteristics of the continuous 4-term Nuttall window, the digital
+prolate window with $W=0.008$, and the continuous approximation to the digital
+prolate window.}
+\end{figure}
 %
+
 A differentiable approximation to a symmetrical window can be designed in a
@@
 
-\section{A continuous window design example}
-\label{sec:designexample}
-%
-\begin{figure*}[ht]
-    \centerline{\includegraphics[width=7in]{{comp_offset_chirp_est_err_params}.eps}}
-\caption{\label{fig:mixwincomp} The mean squared estimation error for each
-    parameter in an analysis of two components in mixture. A set of
-    $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
-    maximum bin differences $0 \leq d < \Doffset{}$, with $d$ varied in
-    $\Dstep{}$ bin increments. The signal power ratio
-    between components is indicated with colours and the corresponding ratio in decibels is indicated in the
-    plot legend. The names indicate the windows used to generate the atoms for
-    estimation: \textit{N3} and \textit{N4} are the 3- and 4-cosine-term
-    continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
-is the continuous 5-cosine-term approximation to a digital prolate window as
-described in Sec.~\ref{sec:designexample}.}
-\end{figure*}
-%
-As a design example we show how to create a continuous approximation of a digital
-prolate spheroidal window.
-
-Digital prolate spheroidal windows are a parametric approximation to functions
-whose Fourier transform's energy is maximized in a given bandwidth
-\cite{slepian1978prolate}. These can be tuned to have extremely low sidelobes,
-at the expense of main-lobe width.  Differentiation of these window functions
-may be possible but is not as straightforward as differentiation of the
-sum-of-cosine windows above. Furthermore, the windows do not generally have
-end-points equal to 0. In the following we will demonstrate how to approximate
-a digital prolate spheroidal window with one that is everywhere at least
-once-differentiable.
+Using this technique, we designed a continuous approximation to a digital prolate
+spheroidal window of length $N=512$ and $W=0.008$. The coefficients
+are described in Table~\ref{tab:contprolate} and a comparison with other
+windows is shown in Figure~\ref{fig:dpw}.
 
@@
 
-In \cite{verma1996digital} it was shown how to construct digital prolate
-spheroidal windows under parameters $N$, the window length in samples, and a
-parameter $W$ choosing the (normalized) frequency range in which the proportion
-of the main lobe's energy is to be maximized. We chose $N=512$ based on the
-window length chosen in \cite{betser2009sinusoidal} for ease of comparison. Its
-$W$ parameter's value was chosen by synthesizing windows with $W$ ranging
-between $0.005$ and $0.010$ at a resolution of $0.001$. The window with the
-closest 3 dB bandwidth to the 4-term Nuttall window was obtained with $W=0.008$.
-Its magnitude response is shown in Fig.~\ref{fig:dpw}. We see that this window's
-asymptotic falloff is 6 dB per octave and therefore has a discontinuity
-somewhere in its domain \cite{nuttall1981some}.
+\section{The performance of improved windows on signals with 2 components}
 
-We designed an approximate
-window using Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and
-$N/8$ to find the best approximation to the digital prolate window's main lobe
-using a small number of cosines. The $M$ giving the best approximation was $5$.
-The magnitude response of the approximation is shown in Fig.~\ref{fig:dpw} and
-its coefficients are listed in Tab.~\ref{tab:contprolate}; the temporal shape is
-very close to a digital prolate spheroidal window with $W=0.008$ and is
-therefore omitted for brevity.
+To investigate the performance of the various windows when estimating the
+parameters of components in mixture we synthesized signals using
+Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
+uniform distributions specified in \cite{betser2009sinusoidal} and evaluated
+the parameter estimation accuracy at various differences between local maxima in
+the mixture's power-spectrum. The procedure is
+summarized in Fig.~\ref{fig:2cevalflowchart}.
 
-It is seen that a lower highest sidelobe level than the Nuttall and Prolate
-windows is obtained by slightly sacrificing the narrowness of the main lobe.
-More importantly, in Fig.~\ref{fig:dpw} we observe that the falloff of the
-window is 18 dB per octave because it is once-differentiable at all points in
-its domain.
+$d$ was incremented by $\Delta_{d} = \Dstep{}$ and so
+$\hat{d}$ was not generally integral valued in this case.
 
-\section{The performance of improved windows}
-
-\subsection{Signals with single component}
-
-To compare the average estimation error variance with the
-theoretical minimum given by the Cram\'{e}r-Rao bound we synthesized $K_{1}$ random
-chirps using Eq.~\ref{eq:polyphaseexp}
-with $Q=2$ and parameters chosen from uniform distributions justified in
-\cite{betser2009sinusoidal}. The original Hann window,
-the windows proposed by Nuttall and the new digital prolate based window were
-used to synthesize the atoms as described in Sec.~\ref{sec:designingatoms} and
-their estimation error variance was compared (see
-Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
-with the atoms, the three atoms whose inner products were greatest were used in
-the estimations, i.e., $R=3$ in Eq.~\ref{eq:ddmsyseq}. The windows with the
-lowest sidelobes only give the lowest error variance at very favourable SNRs, at
-real-world SNRs the original Hann window still performs best at estimating the
-parameters of a single component signal.
-
-\begin{figure}[H]
+\begin{figure}
     \centering

### 2017-09-27 poster/sciposter/dafxposter/references.tex

\documentclass[letterpaper,8pt]{article}
\usepackage[margin=0.5in]{geometry}

\begin{document}
\title{\large\textbf{On the design and use of once-differentiable high dynamic
resolution atoms for the Distribution Derivative Method%
}}
\date{}
\pagestyle{headings}
\markright{On the design and use of once-differentiable high dynamic
resolution atoms for the Distribution Derivative Method%
}
\pagenumbering{gobble}
\bibliographystyle{IEEEbib}
\nocite{*}
%\bibliography{dafx-poster} % requires file DAFx17_tmpl.bib
\bibliography{paper}

\end{document}
